### 2020-08-07 paper.tex
Setting up paper

\documentclass[letterpaper, 10 pt, conference]{IEEEconf}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[style=ieee]{biblatex}
\usepackage{amsmath, amssymb, xcolor}

\newcommand{\todo}[1]{{\color{red}#1}}

\title{\LARGE \bf
A Pipeline to Assemble Near-Accident Footage Datasets
}

\author{
         Ben Upenieks, Chaitanya Varier,\\
         Curtis Duy Kha Phan, Jack David Roberts Williamson,\\
         Nicholas Geofroy, Tony Meng, Vincent-Olivier Roch\\
         University of Waterloo\\
         \\
         {\tt\small ben.upenieks@uwaterloo.ca, cvarier@uwaterloo.ca, cdkphan@uwaterloo.ca, 
          jdrwilliamson@uwaterloo.ca, nicholas.geofroy@uwaterloo.ca, c24meng@uwaterloo.ca, vroch@uwaterloo.ca}
}

\bibliography{sources}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

\todo{Write the abstract}

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}

\todo{Write the introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{CONCLUSIONS}

\todo{Write the conclusions}

A conclusion section is not required. Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion. A conclusion might elaborate on the importance of the work or suggest applications and extensions.

\addtolength{\textheight}{-12cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{APPENDIX}

\todo{Write the appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\nocite{*}
\printbibliography

\end{document}

### 2020-09-14 paper.tex
add sections to paper from meeting with chen

@@
 
-\todo{Write the introduction}
+\todo{Write the introduction} \\
+
+why society needs our tool, what other tools exist and what they are lacking 3/4/5 paragraphs
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{BACKGROUND / PRELIMINARY}
+\todo{write the background / preliminary} \\
+introducing basic ideas to readers. why is the annotation pipeline important (how was the annotation toolbox developed) - use separate subsections
 
-\section{CONCLUSIONS}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{METHODOLOGY}
 
-\todo{Write the conclusions}
+\todo{Write the METHODOLOGY}
+\begin{itemize}
+  \item Major pipeline
+  \item Presenting a graph or figure of the pipeline architecture
+  \begin{itemize}
+    \item pre-processing
+    \item Tracking we can mention how prepare to solve the tracking problem (challenge and future work)
+    \item Blurring (tracking and blurring of vehicle plates and faces)
+  \end{itemize}
+\end{itemize}
+\subsection{Video Preprocessing}
+\subsection{Automatic Annotation}
+\subsection{Object Detection \& Tracking}
+\subsection{Blurring}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{EXPERIMENT}
+- present results of our data, reference the Kitti dataset and how they presented their own data (histogram of object classes, velocity, acceleration, etc)
+- the major contribution we have is the histogram of accident type
+- Histogram of data
+- Usage of our data (applications) - not a major section, just describe potential in preventing/predicting accidents and their importance
+
+\todo{Write the EXPERIMENT SECTION (analyzing data)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{CONCLUSION}
+
+\todo{Write the conclusion}
 A conclusion section is not required.
@@
 A conclusion might elaborate on the importance of the work or suggest applications and extensions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{FUTURE WORK}
+
+\todo{Write the future work ideas}
 

### 2020-09-23 paper.tex
Added introduction, related work and WIP background/preliminary

@@
 
-\todo{Write the introduction} \\
+In the advent of connected vehicles and autonomous transportation, equipping consumer vehicles with the necessary equipment to facilitate high-end automated collision avoidance systems can be prohibitively expensive.
+Technologies such as Radar, LIDAR and high-end cameras that are typically used for collision prediction are likely too expensive for most consumers and might not easily be affixed to their vehicles (maybe not true).
+We note that front-facing dash-cams have become increasingly affordable and prevalent as a means to capture a driver’s perspective leading up to the event of a potential collision.
+We propose that this egocentric dash-cam video stream can be leveraged by computer vision systems to act as an affordable and commonplace sensor for automated collision prediction.
 
-why society needs our tool, what other tools exist and what they are lacking 3/4/5 paragraphs
+In this paper we present a software pipeline to facilitate the collection, processing and annotation of egocentric dash-cam videos from various online video repositories to produce datasets that can be used to train deep dash-cam collision prediction models.
+We aim to generate datasets that are not constrained to any regions or countries but rather provide location-agnostic data that is representative of general, global road and vehicle conditions.
+These datasets will also be collision-oriented.
+Current autonomous vehicle data collection techniques typically require astronomically expensive hardware and equipment and, consequently, are rarely involved in collisions and intentionally not put in high risk environments that may lead to a collision.
+This is the data we hope to capture.
 
@@
 introducing basic ideas to readers. why is the annotation pipeline important (how was the annotation toolbox developed) - use separate subsections
+
+\todo{Work in progress}
+
+Dash-cams are cheap video cameras that can be mounted a car's dashboard or windshield to continuously save a recording of a driver's perspective to an internal memory card.
+Exceptional events recorded by the dashcam such as collisions and crashes are often uploaded and shared to popular social media websites and video repositories such as Reddit, Youtube and Imgur and are typically tagged with a closely related set of key terms.
+
+\todo{Not sure what else to put here}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{RELATED WORK}
+
+Chan et al.
+\cite{chan2016anticipating} approach the same problem of collision prediction via egocentric dash-cam videos.
+They propose a novel Dynamic-Spatial-Attention Recurrent Neural Network that distributes attention to localized and tracked vehicles within the video and models temporal dependencies to predict the earliest frame of a potential impending collision.
+Released with their paper is a dataset of 678 dash-cam videos capturing areas in Taiwan.
+Each video is annotated with vehicle tracking bounding boxes, the vehicles that were involved in the collision and the frame of the collision.
+We hope to allow researchers to expand on this dataset with location-agnostic data and similar annotations.
+
+\subsection{Dash-cams}%
+\label{sub:dash_cams}
 

### 2020-09-23 scripts/make_example.py
Created example histogram

@@ -1,0 +1,9 @@
+import numpy as np
+
+if __name__ == '__main__':
+    N = np.random.normal(size=100)
+    Y, X = np.histogram(N)
+    dtype = [ ('X', np.float64), ('Y', np.float64) ]
+    Z = np.array([ *zip(X, Y) ], dtype=dtype)
+    np.savetxt('example.csv', Z, delimiter=',', fmt=['%f', '%f'], header='X,Y', comments='')
+

### 2020-09-28 paper.tex
Created example histogram
Updates from Overleaf

--- 2020-09-14 paper.tex
@@
          \\
-         {\tt\small ben.upenieks@uwaterloo.ca, cvarier@uwaterloo.ca, cdkphan@uwaterloo.ca,
-          jdrwilliamson@uwaterloo.ca, nicholas.geofroy@uwaterloo.ca, c24meng@uwaterloo.ca, vroch@uwaterloo.ca}
+         {\tt\small ben.upenieks@uwaterloo.ca, cvarier@uwaterloo.ca,
+         \\ \tt\small cdkphan@uwaterloo.ca, jdrwilli@uwaterloo.ca,
+         \\ \tt\small nicholas.geofroy@uwaterloo.ca, c24meng@uwaterloo.ca, vroch@uwaterloo.ca}
 }

### 2020-09-28 paper.tex

--- 2020-09-23 paper.tex
@@
 \usepackage[style=ieee]{biblatex}
-\usepackage{amsmath, amssymb, xcolor}
+\usepackage{amsmath, amssymb, xcolor, tikz, pgfplots}
 
@@
 
+\begin{center}
+\begin{tikzpicture}
+\begin{axis}[
+  title={Example histogram},
+  xlabel={Classes},
+  ylabel={$\textup{Normal}(\mu=0, \sigma=1)$}
+]
+\addplot[fill, ybar] table [x=X, y=Y, col sep=comma] {example.csv};
+\end{axis}
+\end{tikzpicture}
+\end{center}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-09-29 paper.tex
add some minor additions to intro + background

@@
          \\
-         {\tt\small ben.upenieks@uwaterloo.ca, cvarier@uwaterloo.ca,
+         \tt\small ben.upenieks@uwaterloo.ca, cvarier@uwaterloo.ca,
          \\ \tt\small cdkphan@uwaterloo.ca, jdrwilli@uwaterloo.ca,
-         \\ \tt\small nicholas.geofroy@uwaterloo.ca, c24meng@uwaterloo.ca, vroch@uwaterloo.ca}
+         \\ \tt\small nicholas.geofroy@uwaterloo.ca, c24meng@uwaterloo.ca, vroch@uwaterloo.ca
 }
@@
 \bibliography{sources}
-
 \begin{document}
@@
 We note that front-facing dash-cams have become increasingly affordable and prevalent as a means to capture a driver’s perspective leading up to the event of a potential collision.
+This has led to the creation of many online communities to share such videos.
 We propose that this egocentric dash-cam video stream can be leveraged by computer vision systems to act as an affordable and commonplace sensor for automated collision prediction.
@@
 We aim to generate datasets that are not constrained to any regions or countries but rather provide location-agnostic data that is representative of general, global road and vehicle conditions.
-These datasets will also be collision-oriented.
+These datasets will also be collision-oriented as the majority of these videos contain collisions for people's entertainment.
 Current autonomous vehicle data collection techniques typically require astronomically expensive hardware and equipment and, consequently, are rarely involved in collisions and intentionally not put in high risk environments that may lead to a collision.
-This is the data we hope to capture.
+This is the data we hope to capture by taking advantage of existing videos of non-artificial collisions.
 
@@
 Dash-cams are cheap video cameras that can be mounted a car's dashboard or windshield to continuously save a recording of a driver's perspective to an internal memory card.
-Exceptional events recorded by the dashcam such as collisions and crashes are often uploaded and shared to popular social media websites and video repositories such as Reddit, Youtube and Imgur and are typically tagged with a closely related set of key terms.
-
+Exceptional events recorded by the dashcam such as collisions and crashes are often uploaded and shared to popular social media websites and video repositories such as Reddit, Youtube, and Imgur and are typically tagged with a closely related set of key terms.
+The pipeline uses web-scraping techniques to fetch the video data from these websites, along with a set of video metadata, describing the video's contents.
+We use this data, in combination with the manually annotated data in order to create the collision dataset.
 \todo{Not sure what else to put here}

### 2020-10-07 paper.tex
combine intro and background/preliminary sections

@@
 Technologies such as Radar, LIDAR and high-end cameras that are typically used for collision prediction are likely too expensive for most consumers and might not easily be affixed to their vehicles (maybe not true).
-We note that front-facing dash-cams have become increasingly affordable and prevalent as a means to capture a driver’s perspective leading up to the event of a potential collision.
-This has led to the creation of many online communities to share such videos.
+On the other hand dash-cams, cheap video cameras that can be mounted a car's dashboard, have become increasingly affordable and prevalent as a means to capture a driver’s perspective.
+Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that wouldn't be feasible to simulate. 
+This has led to the creation of many online communities to share videos of these rare situations on websites such as Reddit, Youtube, and Imgur.
 We propose that this egocentric dash-cam video stream can be leveraged by computer vision systems to act as an affordable and commonplace sensor for automated collision prediction.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{BACKGROUND / PRELIMINARY}
-\todo{write the background / preliminary} \\
-introducing basic ideas to readers. why is the annotation pipeline important (how was the annotation toolbox developed) - use separate subsections
-
-\todo{Work in progress}
-
-Dash-cams are cheap video cameras that can be mounted a car's dashboard or windshield to continuously save a recording of a driver's perspective to an internal memory card.
-Exceptional events recorded by the dashcam such as collisions and crashes are often uploaded and shared to popular social media websites and video repositories such as Reddit, Youtube, and Imgur and are typically tagged with a closely related set of key terms.
 The pipeline uses web-scraping techniques to fetch the video data from these websites, along with a set of video metadata, describing the video's contents.
 We use this data, in combination with the manually annotated data in order to create the collision dataset.
+This combination allows us to take advantage of the wide variety of videos available on the internet, while still having reliable data that has been curated manually.
 \todo{Not sure what else to put here}

### 2020-10-07 paper.tex
Added by-class histogram

@@
 \usepackage[style=ieee]{biblatex}
-\usepackage{amsmath, amssymb, xcolor, tikz, pgfplots}
+\usepackage{tikz}
+\usetikzlibrary{positioning,fit,arrows.meta,backgrounds}
+\usepackage{amsmath, amssymb, xcolor, tikz, pgfplots, pgfplotstable}
 
@@
 \end{itemize}
+\tikzset{
+    module/.style={%
+        draw, rounded corners,
+        minimum width=#1,
+        minimum height=7mm,
+        font=\sffamily
+        },
+    module/.default=2cm,
+    >=LaTeX
+}
+\begin{tikzpicture}[
+  % This will show the frame around the figure
+  show background rectangle]
+
+  % Place first 6 items
+  \node[module] (crawler) {Web-Scrapers};
+  \node[module, below=of crawler] (downloader) {Downloaders};
+  \node[module, below=of downloader] (splitter) {Video-Splitter};
+  \node[module, below=of splitter] (labeller) {Video-Labelling Tool};
+  \node[module, below=of labeller] (face-blur) {Face Blurring};
+  \node[module, below=of face-blur] (license-blur) {License Plate Blurring};
+  \node[draw,inner xsep=4mm,inner ysep=7mm,fit=(face-blur)(license-blur)](anon){};
+  \node[anchor=north west,inner sep=1pt] at (anon.north west) 
+    {Anonymization};
+  \node[module, below=of anon] (uploader) {Data-Uploader};
+  \draw[->] (crawler)--(downloader);
+  \draw[->] (downloader)--(splitter);
+  \draw[->] (splitter)--(labeller);
+  \draw[->] (labeller)--(face-blur);
+  \draw[->] (face-blur)--(license-blur);
+  \draw[->] (license-blur)--(uploader);
+
+\end{tikzpicture}
 \subsection{Video Preprocessing}
@@
 
+\pgfplotstableread[col sep=comma]{by-classes.csv}\byclass
+
+\begin{center}
+\begin{tikzpicture}
+\begin{axis}[
+  title={Objects by class},
+  xlabel={Class},
+  ylabel={Frequency (\# of bounding boxes)},
+  xtick=data,
+  xticklabels from table={\byclass}{X}
+]
+\addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
+\end{axis}
+\end{tikzpicture}
+\end{center}
+
 \begin{center}

### 2020-10-07 scripts/make_by-classes.py

@@ -1,0 +1,35 @@
+import numpy as np
+import firebase_admin as fb
+from firebase_admin import credentials, db
+from firebase_admin.db import Reference
+from functools import reduce
+
+FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
+
+def histogram_by_class(hist, data):
+    (key, data) = data
+    if data.get('is_cancelled', True):
+        return hist
+    for cls in data.get('bb_fields', {}).get('clss', []):
+        hist[cls] = hist.get(cls, 0) + 1
+    return hist
+
+if __name__ == '__main__':
+    cred = credentials.Certificate(FIREBASE_CRED_FILENAME)
+    print('Created credentials')
+    fb_app = fb.initialize_app(cred, {
+            'databaseURL': 'https://autodash-9dccb.firebaseio.com/',
+            'databaseAuthVariableOverride': {
+                'uid': 'pipeline-worker'
+            }
+        })
+    print('Created app')
+    metadata = db.reference('metadata')
+    print('Retrieved data')
+    data = [ val for val in metadata.get().items() ]
+    hist = reduce(histogram_by_class, data, {})
+    print(hist)
+    dtype = [ ('X', object), ('Y', np.uint32) ]
+    Z = np.array([ *hist.items() ], dtype=dtype)
+    np.savetxt('by-classes.csv', Z, delimiter=',', fmt=['%s', '%d'], header='X,Y', comments='')
+

### 2020-10-14 paper.tex
update metadata section

@@
 \newcommand{\todo}[1]{{\color{red}#1}}
+\usepackage{listings, xcolor}
+
+\colorlet{punct}{red!60!black}
+\definecolor{background}{HTML}{EEEEEE}
+\definecolor{delim}{RGB}{20,105,176}
+\colorlet{numb}{magenta!60!black}
+
+\lstdefinelanguage{json}{
+    basicstyle=\normalfont\ttfamily,
+    numbers=left,
+    numberstyle=\scriptsize,
+    stepnumber=1,
+    numbersep=8pt,
+    showstringspaces=false,
+    breaklines=true,
+    frame=lines,
+    backgroundcolor=\color{background},
+    literate=
+     *{0}{{{\color{numb}0}}}{1}
+      {1}{{{\color{numb}1}}}{1}
+      {2}{{{\color{numb}2}}}{1}
+      {3}{{{\color{numb}3}}}{1}
+      {4}{{{\color{numb}4}}}{1}
+      {5}{{{\color{numb}5}}}{1}
+      {6}{{{\color{numb}6}}}{1}
+      {7}{{{\color{numb}7}}}{1}
+      {8}{{{\color{numb}8}}}{1}
+      {9}{{{\color{numb}9}}}{1}
+      {:}{{{\color{punct}{:}}}}{1}
+      {,}{{{\color{punct}{,}}}}{1}
+      {\{}{{{\color{delim}{\{}}}}{1}
+      {\}}{{{\color{delim}{\}}}}}{1}
+      {[}{{{\color{delim}{[}}}}{1}
+      {]}{{{\color{delim}{]}}}}{1},
+}
 
 \title{\LARGE \bf
-A Pipeline to Assemble Near-Accident Footage Datasets
+A Pipeline to Assemble (Near-)Collision Footage Datasets
 }
@@
 Technologies such as Radar, LIDAR and high-end cameras that are typically used for collision prediction are likely too expensive for most consumers and might not easily be affixed to their vehicles (maybe not true).
-On the other hand dash-cams, cheap video cameras that can be mounted a car's dashboard, have become increasingly affordable and prevalent as a means to capture a driver’s perspective.
+On the other hand dash-cams, cheap video cameras that can be mounted to a car's dashboard, have become increasingly affordable and prevalent as a means to capture a driver’s perspective.
 Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that wouldn't be feasible to simulate. 
@@
 
+The software pipeline is built of multiple executors that each process or handle the data corresponding to a single video before piping the resulting data to the next executor.
+
 \todo{Write the METHODOLOGY}
@@
     \item Tracking we can mention how prepare to solve the tracking problem (challenge and future work)
-    \item Blurring (tracking and blurring of vehicle plates and faces)
+    \item Anonymization (tracking and blurring of vehicle plates and faces)
   \end{itemize}
 \end{itemize}
+
+\begin{figure}[htpb]
+		\centering
     \tikzset{
@@
     \end{tikzpicture}
+		\caption{Architecture of the default pipeline}
+		\label{fig:obj-by-class}
+\end{figure}
+
+\subsection{Video Collection}
+
+The entry into our pipeline is a set of web scraper executors that each target and scrape a specific website or video repository based on a user-defined set of key-terms, and an executor that pulls unlabelled videos from the user's database.
+Videos that are pulled by the scrapers are immediately added to the database with relevant metadata and marked as unlabelled.
+Subsequently, they are loaded into memory and sequentially fed into the pipeline.
+If the pipeline terminates before labelling a video, it remains flagged as unlabelled in the database and the video will be pulled in a subsequent run by the database source executor.
+Crawler state is maintained via database lookup of specified key-value pairs to ensure duplicate data is not pulled.
+No video preprocessing such as resizing, trimming or cropping is automatically performed.
+
+Users may define their own search terms to be used when querying the video repository.
+This value can be set either in the crawler implementation (\todo{or the yaml pipeline configuration file?}).
+By default, our scrapers query using the keywords: (\todo{should probably define default keywords}).
+Currently we support scraping and querying Reddit, YouTube and Imgur.
+Users that want to pull from a video repository that is not currently implemented should create a custom executor and implement the \texttt{iCrawler} interface.
+This new executor should be added as an entry point in a new yaml configuration and should generate and return a \texttt{MetaDataItem} with video source information to be used by a subsequent and corresponding downloader.
+\texttt{MetaDataItem} objects are fed into the \texttt{UniversalDownloader} which aggregates \texttt{iDownloader} implementations and distributes \texttt{MetaDataItem} objects to their corresponding downloader via regex matching of source URL's.
+New downloaders should registered with the \texttt{UniversalDownloader} via the yaml pipeline configuration along with a regex string for url matching.
+\todo{Maybe this should be refactored to just pass iCrawler output directly to its downloader}
+
 \subsection{Video Preprocessing}
+
 \subsection{Automatic Annotation}
 \subsection{Object Detection \& Tracking}
-\subsection{Blurring}
+\todo{Automated object detection not used right now?}
+\subsection{Anonymization}
+An important facet of automobile data aggregation is in eliminating biases and protecting the identities of depicted individuals.
+Consequently, our pipeline contains a post-processing stage in which we apply blurring masks to anonymize any personally identifiable information.
+Specifically, we provide two executors to perform these anonymization tasks: \texttt{FaceBlurrer}, which blurs faces and \texttt{LicensePlateBlurrer} which blurs license plates.
+Both of these executors are powered by pre-trained machine learning models which detect regions containing personally identifiable information.
+Specifically, for  \texttt{FaceBlurrer}, we use a MobileNet Single Shot MultiBox Detector (TODO: cite https://github.com/yeephycho/tensorflow-face-detection) and for \texttt{LicensePlateBlurrer} we use a Convolutional Neural Network (TODO: cite http://sergiomsilva.com/pubs/alpr-unconstrained/).
+
+This software module is encapsulated as a library and can be reused by importing our \texttt{anonymization} package as a dependency.
+The accuracy, amount and type of blurring applied can be tweaked using the API exposed by the \texttt{anonymization} package.
+
+\subsection{Annotation}
+
+In addition to collection and preprocessing, a core component of our pipeline is a GUI tool that facilitates the manual annotation of the dash-cam videos, and quick manual filtering of non-dashcam and irrelevant videos.
+Following Chan et al.\cite{chan2016anticipating}, if a collision occurs we provide tools to annotate the frame the collision occurs, and bounding boxes to localize, identify and track agents both involved and not involved in the collision.
+Object tracking bounding boxes can be linearly interpolated from manual start and end points to improve ease of labelling.
+We also save the video resolution at which the video was annotated to ensure bounding box annotations can always be scaled to fit any variable download resolutions (\todo{Is this a useful feature to have?}).For long-form videos that may contain multiple collision events or irrelevant video segments, such as compilation videos or videos with substantial editing and transitions, we provide a video clipping feature to demarcate the collision events from which we extract and generate distinct data points.
+
+\todo{Talk more about clipping and how we generate distinct data points after clipping}
+
+\subsection{Metadata}
+After all of the previous steps have been completed, the pipeline is able to produce a metadata object.
+There are many fields in the metadata object (as can be seen in Figure \ref{metadata_example}):
+
+\begin{itemize}
+  \item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
+  \item "description" contains a breif description of the video as scraped from the video hosting website
+  \item "download\_src" contains the site that the video was sourced from (e.g. YouTube)
+  \item "tags" is an object that contains custom user-defined tags on videos and additional data that is site specific
+  \item "title" is a string that represents the type of the video
+  \item "url" is the url that the video was fetched from
+  \item "is\_split\_url" is a boolean that represents if all of the frames of the video have bounding boxes in this metadata
+  \item "start\_i" is the start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
+  \item "end\_i" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
+  \item "bb\_fields" contains all bounding-box specific data. Each entry is a list, where the $i_{th}$ index in each contains the data for one bounding-box:
+  \begin{itemize}
+    \item "ids[$i$]" represents what vehicle id the $i_{th}$ bounding box represents. Each vehicle in the video has it's own unique id
+    \item "cls[$i$]" represents the object class of the vehicle
+    \item "frames[$i$]" represents what frame of the video the $i_{th}$ bounding box is for
+    \item "has\_collision[$i$]" represents if the vehicle with id $ids[i]$ is in a collision
+    \item "x1s[$i$], y1s[$i$], x2s[$i$], y2s[$i$]" are the coordinates of the two points $(x_1,y_1)$ \& $(x_2,y_2)$ that make bounding box $i$
+  \end{itemize}
+\end{itemize}`
+
+\begin{figure}
+  \begin{lstlisting}[language=json]
+    {
+      "collision_type":"",
+      "description":"",
+      "download_src":"",
+      "tags": {
+        "reddit_post_info":{
+          "id":"<post_id>"
+          "title":"title"
+        }
+      },
+      "title":"Title of the Video",
+      "url":"http:/www.myvideo.com",
+      "is_split_url": false,
+      "start_i": 0,
+      "end_i": 60,
+      "bb_fields": {
+        "cls": [],
+        "frames": [],
+        "has_collision": [],
+        "ids": [],
+        "x1s": [],
+        "y1s": [],
+        "x2s": [],
+        "y2s": [],
+      }
+    }
+  \end{lstlisting}
+    \caption{Example Metadata Produced by the Pipeline}
+    \label{metadata_example}
+\end{figure}
+
+\begin{figure}[htpb]
+		\centering
+		% TODO: Uncomment this
+    %\includegraphics[width=0.5\textwidth]{images/example_gui_tool.png}
+		\caption{GUI tool to facilitate annotation}
+		\label{fig:example_gui_tool-png}
+\end{figure}
 
@@
 - present results of our data, reference the Kitti dataset and how they presented their own data (histogram of object classes, velocity, acceleration, etc)
+
 - the major contribution we have is the histogram of accident type
+
 - Histogram of data
+
 - Usage of our data (applications) - not a major section, just describe potential in preventing/predicting accidents and their importance
@@
 
+There are many ways that we could improve on our system. This are just a series of ideas that we could think of:
+\begin{enumerate}
+\item Custom interpolation between input frames: One idea would be to make it easier to modify the method of interpolation between frames.
+Currently, linear interpolation is always used.
+Moreover, given a type of interpolation is stored in the metadata, we probably shouldn't store all interpolated frames, rather than just the ones the user has entered.
+While linear interpolation works great for entering a frame every 10 frames, supporting more interpolations could be great for faster data entry, or even for supporting affine transformations on more complex bounds.
+
+\item Polyhedral bounds: It's always possible to represent a 2-dimensional polyhedron with a matrix $A\in\mathbb{R}^{n\times 2}$, and a vector $b\in\mathbb{R}^2$, given that the polyhedron can be represented by the set $\left\{x\mid Ax\leq b\right\}$.
+We could use this idea to store masking bounds that can be used for training Mask-RCNN networks in (near-)collision contexts.
+
+\item Web interface: Having a web-based user interface would be advantageous for this project.
+While currently being used in the context of (near-)collision accident, this software has the potential to become a platform for scraping automation and collaboration.
+Ideally, people without a technical background would be able to contribute to the microtasking involved, and technical contributors would be in charge of creating and managing the automation and general design of the pipeline.
+
+\end{enumerate}
 \todo{Write the future work ideas}
@@
 
-\begin{center}
+\begin{figure}[htpb]
+		\centering
     \begin{tikzpicture}
@@
     \end{tikzpicture}
-\end{center}
+		\caption{Object by classes in our private database}
+		\label{fig:obj-by-class}
+\end{figure}
 

### 2020-10-21 paper.tex
add initial architecture diagram
Added sections on video collection and annotation

--- 2020-10-07 paper.tex
@@
 \end{itemize}
+
+\subsection{Video Collection}
+
+The entry into our pipeline is a set of web scraper executors that each target and scrape a specific website or video repository based on a user-defined set of key-terms, and an executor that pulls unlabelled videos from the user's database.
+Videos that are pulled by the scrapers are immediately added to the database with relevant metadata and marked as unlabelled.
+Subsequently, they are loaded into memory and sequentially fed into the pipeline.
+If the pipeline terminates before labelling a video, it remains flagged as unlabelled in the database and the video will be pulled in a subsequent run by the database source executor.
+Crawler state is maintained via database lookup of specified key-value pairs to ensure duplicate data is not pulled.
+No video preprocessing such as resizing, trimming or cropping is automatically performed.
+
+Users may define their own search terms to be used when querying the video repository.
+This value can be set either in the crawler implementation (\todo{or the yaml pipeline configuration file?}).
+By default, our scrapers query using the keywords: (\todo{should probably define default keywords}).
+Currently we support scraping and querying Reddit, YouTube and Imgur.
+Users that want to pull from a video repository that is not currently implemented should create a custom executor and implement the \texttt{iCrawler} interface.
+This new executor should be added as an entry point in a new yaml configuration and should generate and return a \texttt{MetaDataItem} with video source information to be used by a subsequent and corresponding downloader.
+\texttt{MetaDataItem} objects are fed into the \texttt{UniversalDownloader} which aggregates \texttt{iDownloader} implementations and distributes \texttt{MetaDataItem} objects to their corresponding downloader via regex matching of source URL's.
+New downloaders should registered with the \texttt{UniversalDownloader} via the yaml pipeline configuration along with a regex string for url matching.
+\todo{Maybe this should be refactored to just pass iCrawler output directly to its downloader}
+
 \subsection{Video Preprocessing}
+
 \subsection{Automatic Annotation}
 \subsection{Object Detection \& Tracking}
+\todo{Automated object detection not used right now?}
 \subsection{Blurring}
+\subsection{Annotation}
+
+In addition to collection and preprocessing, a core component of our pipeline is a GUI tool that facilitates the manual annotation of the dash-cam videos, and quick manual filtering of non-dashcam and irrelevant videos.
+Following Chan et al.\cite{chan2016anticipating}, if a collision occurs we provide tools to annotate the frame the collision occurs, and bounding boxes to localize, identify and track agents both involved and not involved in the collision.
+Object tracking bounding boxes can be linearly interpolated from manual start and end points to improve ease of labelling.
+We also save the video resolution at which the video was annotated to ensure bounding box annotations can always be scaled to fit any variable download resolutions (\todo{Is this a useful feature to have?}).For long-form videos that may contain multiple collision events or irrelevant video segments, such as compilation videos or videos with substantial editing and transitions, we provide a video clipping feature to demarcate the collision events from which we extract and generate distinct data points.
+
+\todo{Talk more about clipping and how we generate distinct data points after clipping}
+
+\begin{figure}[htpb]
+		\centering
+		\includegraphics[width=0.5\textwidth]{images/example_metadata.png}
+		\caption{An example of metadata for a labelled video.
+Both automatic metadata about the source of the video and manual annotation of the collision is maintained.
+Each bounding box contains the object classification, a unique identifier and a boolean value representing if the tracked agent is involved in a collision.}
+		\label{fig:images-example_metadata-png}
+\end{figure}
+
+\todo{Use a better image}
+
+\begin{figure}[htpb]
+		\centering
+		\includegraphics[width=0.5\textwidth]{images/example_gui_tool.png}
+		\caption{GUI tool to facilitate annotation}
+		\label{fig:example_gui_tool-png}
+\end{figure}
 
@@
 
-\begin{center}
-\begin{tikzpicture}
-\begin{axis}[
-  title={Example histogram},
-  xlabel={Classes},
-  ylabel={$\textup{Normal}(\mu=0, \sigma=1)$}
-]
-\addplot[fill, ybar] table [x=X, y=Y, col sep=comma] {example.csv};
-\end{axis}
-\end{tikzpicture}
-\end{center}
+%\begin{center}
+%\begin{tikzpicture}
+%\begin{axis}[
+%  title={Example histogram},
+%  xlabel={Classes},
+%  ylabel={$\textup{Normal}(\mu=0, \sigma=1)$}
+%]
+%\addplot[fill, ybar] table [x=X, y=Y, col sep=comma] {example.csv};
+%\end{axis}
+%\end{tikzpicture}
+%\end{center}
 

### 2020-10-22 paper.tex

@@
 \end{itemize}
+
+\tikzset{
+    module/.style={%
+        draw, rounded corners,
+        minimum width=#1,
+        minimum height=7mm,
+        font=\sffamily
+        },
+    module/.default=2cm,
+    >=LaTeX
+}
+\begin{tikzpicture}[
+  % This will show the frame around the figure
+  show background rectangle]
+
+  % Place first 6 items
+  \node[module] (crawler) {Web-Scrapers};
+  \node[module, below=of crawler] (downloader) {Downloaders};
+  \node[module, below=of downloader] (splitter) {Video-Splitter};
+  \node[module, below=of splitter] (labeller) {Video-Labelling Tool};
+  \node[module, below=of labeller] (face-blur) {Face Blurring};
+  \node[module, below=of face-blur] (license-blur) {License Plate Blurring};
+  \node[draw,inner xsep=4mm,inner ysep=7mm,fit=(face-blur)(license-blur)](anon){};
+  \node[anchor=north west,inner sep=1pt] at (anon.north west) 
+    {Anonymization};
+  \node[module, below=of anon] (uploader) {Data-Uploader};
+  \draw[->] (crawler)--(downloader);
+  \draw[->] (downloader)--(splitter);
+  \draw[->] (splitter)--(labeller);
+  \draw[->] (labeller)--(face-blur);
+  \draw[->] (face-blur)--(license-blur);
+  \draw[->] (license-blur)--(uploader);
+
+\end{tikzpicture}
 
@@
 %\end{center}
+\pgfplotstableread[col sep=comma]{by-classes.csv}\byclass
+
+\begin{center}
+\begin{tikzpicture}
+\begin{axis}[
+  title={Objects by class},
+  xlabel={Class},
+  ylabel={Frequency (\# of bounding boxes)},
+  xtick=data,
+  xticklabels from table={\byclass}{X}
+]
+\addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
+\end{axis}
+\end{tikzpicture}
+\end{center}
+
+\begin{center}
+\begin{tikzpicture}
+\begin{axis}[
+  title={Example histogram},
+  xlabel={Classes},
+  ylabel={$\textup{Normal}(\mu=0, \sigma=1)$}
+]
+\addplot[fill, ybar] table [x=X, y=Y, col sep=comma] {example.csv};
+\end{axis}
+\end{tikzpicture}
+\end{center}
 

### 2020-10-28 paper.tex
Fixing paper build
Added some ideas in the Future work section

@@
 \title{\LARGE \bf
-A Pipeline to Assemble Near-Accident Footage Datasets
+A Pipeline to Assemble (Near-)Collision Footage Datasets
 }
@@
 
+\begin{figure}[htpb]
+		\centering
     \tikzset{
@@
     \end{tikzpicture}
+		\caption{Architecture of the default pipeline}
+		\label{fig:obj-by-class}
+\end{figure}
 
@@
 		\centering
-		\includegraphics[width=0.5\textwidth]{images/example_metadata.png}
+		% TODO: Uncomment this
+    %\includegraphics[width=0.5\textwidth]{images/example_metadata.png}
 		\caption{An example of metadata for a labelled video.
@@
 		\centering
-		\includegraphics[width=0.5\textwidth]{images/example_gui_tool.png}
+		% TODO: Uncomment this
+    %\includegraphics[width=0.5\textwidth]{images/example_gui_tool.png}
 		\caption{GUI tool to facilitate annotation}
@@
 
-%\begin{center}
-%\begin{tikzpicture}
-%\begin{axis}[
-%  title={Example histogram},
-%  xlabel={Classes},
-%  ylabel={$\textup{Normal}(\mu=0, \sigma=1)$}
-%]
-%\addplot[fill, ybar] table [x=X, y=Y, col sep=comma] {example.csv};
-%\end{axis}
-%\end{tikzpicture}
-%\end{center}
 \pgfplotstableread[col sep=comma]{by-classes.csv}\byclass
 
-\begin{center}
+\begin{figure}[htpb]
+		\centering
     \begin{tikzpicture}

### 2020-10-29 paper.tex
added section on anonymization

@@
 
-Chan et al.
-\cite{chan2016anticipating} approach the same problem of collision prediction via egocentric dash-cam videos.
+Chan et al.   \cite{chan2016anticipating}
+approach the same problem of collision prediction via egocentric dash-cam videos.
 They propose a novel Dynamic-Spatial-Attention Recurrent Neural Network that distributes attention to localized and tracked vehicles within the video and models temporal dependencies to predict the earliest frame of a potential impending collision.
@@
     \item Tracking we can mention how prepare to solve the tracking problem (challenge and future work)
-    \item Blurring (tracking and blurring of vehicle plates and faces)
+    \item Anonymization (tracking and blurring of vehicle plates and faces)
   \end{itemize}
@@
 \todo{Automated object detection not used right now?}
-\subsection{Blurring}
+\subsection{Anonymization}
+An important facet of automobile data aggregation is in eliminating biases and protecting the identities of depicted individuals.
+Consequently, our pipeline contains a post-processing stage in which we apply blurring masks to anonymize any personally identifiable information.
+Specifically, we provide two executors to perform these anonymization tasks: \textttt{FaceBlurrer}, which blurs faces and \texttt{LicensePlateBlurrer} which blurs license plates.
+Both of these executors are powered by pre-trained machine learning models which detect regions containing personally identifiable information.
+Specifically, for  \textttt{FaceBlurrer}, we use a MobileNet Single Shot MultiBox Detector (TODO: cite https://github.com/yeephycho/tensorflow-face-detection) and for \texttt{LicensePlateBlurrer} we use a Convolutional Neural Network (TODO: cite http://sergiomsilva.com/pubs/alpr-unconstrained/).
+
+This software module is encapsulated as a library and can be reused easily by importing our \texttt{anonymization} package as a dependency.
+The accuracy, amount and type of blurring applied can be tweaked using the API exposed by the \texttt{anonymization} package.
+
 \subsection{Annotation}

### 2020-11-01 paper.tex
cleanup
Updates from Overleaf

--- 2020-10-22 paper.tex
@@
 \usepackage[style=ieee]{biblatex}
-\usepackage{tikz}
-\usetikzlibrary{positioning,fit,arrows.meta,backgrounds}
-\usepackage{amsmath, amssymb, xcolor, tikz, pgfplots, pgfplotstable}
+\usepackage{amsmath, amssymb, xcolor, tikz, pgfplots}
 
@@
 Technologies such as Radar, LIDAR and high-end cameras that are typically used for collision prediction are likely too expensive for most consumers and might not easily be affixed to their vehicles (maybe not true).
-On the other hand dash-cams, cheap video cameras that can be mounted to a car's dashboard, have become increasingly affordable and prevalent as a means to capture a driver’s perspective.
+On the other hand dash-cams, cheap video cameras that can be mounted a car's dashboard, have become increasingly affordable and prevalent as a means to capture a driver’s perspective.
 Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that wouldn't be feasible to simulate. 
@@
 
+The software pipeline is built of multiple executors that each process or handle the data corresponding to a single video before piping the resulting data to the next
+
 \todo{Write the METHODOLOGY}
@@
 \end{itemize}
-
-\tikzset{
-    module/.style={%
-        draw, rounded corners,
-        minimum width=#1,
-        minimum height=7mm,
-        font=\sffamily
-        },
-    module/.default=2cm,
-    >=LaTeX
-}
-\begin{tikzpicture}[
-  % This will show the frame around the figure
-  show background rectangle]
-
-  % Place first 6 items
-  \node[module] (crawler) {Web-Scrapers};
-  \node[module, below=of crawler] (downloader) {Downloaders};
-  \node[module, below=of downloader] (splitter) {Video-Splitter};
-  \node[module, below=of splitter] (labeller) {Video-Labelling Tool};
-  \node[module, below=of labeller] (face-blur) {Face Blurring};
-  \node[module, below=of face-blur] (license-blur) {License Plate Blurring};
-  \node[draw,inner xsep=4mm,inner ysep=7mm,fit=(face-blur)(license-blur)](anon){};
-  \node[anchor=north west,inner sep=1pt] at (anon.north west) 
-    {Anonymization};
-  \node[module, below=of anon] (uploader) {Data-Uploader};
-  \draw[->] (crawler)--(downloader);
-  \draw[->] (downloader)--(splitter);
-  \draw[->] (splitter)--(labeller);
-  \draw[->] (labeller)--(face-blur);
-  \draw[->] (face-blur)--(license-blur);
-  \draw[->] (license-blur)--(uploader);
-
-\end{tikzpicture}
-
 \subsection{Video Collection}
-
-The entry into our pipeline is a set of web scraper executors that each target and scrape a specific website or video repository based on a user-defined set of key-terms, and an executor that pulls unlabelled videos from the user's database.
-Videos that are pulled by the scrapers are immediately added to the database with relevant metadata and marked as unlabelled.
-Subsequently, they are loaded into memory and sequentially fed into the pipeline.
-If the pipeline terminates before labelling a video, it remains flagged as unlabelled in the database and the video will be pulled in a subsequent run by the database source executor.
-Crawler state is maintained via database lookup of specified key-value pairs to ensure duplicate data is not pulled.
-No video preprocessing such as resizing, trimming or cropping is automatically performed.
-
-Users may define their own search terms to be used when querying the video repository.
-This value can be set either in the crawler implementation (\todo{or the yaml pipeline configuration file?}).
-By default, our scrapers query using the keywords: (\todo{should probably define default keywords}).
-Currently we support scraping and querying Reddit, YouTube and Imgur.
-Users that want to pull from a video repository that is not currently implemented should create a custom executor and implement the \texttt{iCrawler} interface.
-This new executor should be added as an entry point in a new yaml configuration and should generate and return a \texttt{MetaDataItem} with video source information to be used by a subsequent and corresponding downloader.
-\texttt{MetaDataItem} objects are fed into the \texttt{UniversalDownloader} which aggregates \texttt{iDownloader} implementations and distributes \texttt{MetaDataItem} objects to their corresponding downloader via regex matching of source URL's.
-New downloaders should registered with the \texttt{UniversalDownloader} via the yaml pipeline configuration along with a regex string for url matching.
-\todo{Maybe this should be refactored to just pass iCrawler output directly to its downloader}
-
 \subsection{Video Preprocessing}
-
 \subsection{Automatic Annotation}
 \subsection{Object Detection \& Tracking}
-\todo{Automated object detection not used right now?}
 \subsection{Blurring}
-\subsection{Annotation}
-
-In addition to collection and preprocessing, a core component of our pipeline is a GUI tool that facilitates the manual annotation of the dash-cam videos, and quick manual filtering of non-dashcam and irrelevant videos.
-Following Chan et al.\cite{chan2016anticipating}, if a collision occurs we provide tools to annotate the frame the collision occurs, and bounding boxes to localize, identify and track agents both involved and not involved in the collision.
-Object tracking bounding boxes can be linearly interpolated from manual start and end points to improve ease of labelling.
-We also save the video resolution at which the video was annotated to ensure bounding box annotations can always be scaled to fit any variable download resolutions (\todo{Is this a useful feature to have?}).For long-form videos that may contain multiple collision events or irrelevant video segments, such as compilation videos or videos with substantial editing and transitions, we provide a video clipping feature to demarcate the collision events from which we extract and generate distinct data points.
-
-\todo{Talk more about clipping and how we generate distinct data points after clipping}
-
-\begin{figure}[htpb]
-		\centering
-		\includegraphics[width=0.5\textwidth]{images/example_metadata.png}
-		\caption{An example of metadata for a labelled video.
-Both automatic metadata about the source of the video and manual annotation of the collision is maintained.
-Each bounding box contains the object classification, a unique identifier and a boolean value representing if the tracked agent is involved in a collision.}
-		\label{fig:images-example_metadata-png}
-\end{figure}
-
-\todo{Use a better image}
-
-\begin{figure}[htpb]
-		\centering
-		\includegraphics[width=0.5\textwidth]{images/example_gui_tool.png}
-		\caption{GUI tool to facilitate annotation}
-		\label{fig:example_gui_tool-png}
-\end{figure}
 
@@
 
-%\begin{center}
-%\begin{tikzpicture}
-%\begin{axis}[
-%  title={Example histogram},
-%  xlabel={Classes},
-%  ylabel={$\textup{Normal}(\mu=0, \sigma=1)$}
-%]
-%\addplot[fill, ybar] table [x=X, y=Y, col sep=comma] {example.csv};
-%\end{axis}
-%\end{tikzpicture}
-%\end{center}
-\pgfplotstableread[col sep=comma]{by-classes.csv}\byclass
-
-\begin{center}
-\begin{tikzpicture}
-\begin{axis}[
-  title={Objects by class},
-  xlabel={Class},
-  ylabel={Frequency (\# of bounding boxes)},
-  xtick=data,
-  xticklabels from table={\byclass}{X}
-]
-\addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
-\end{axis}
-\end{tikzpicture}
-\end{center}
-
 \begin{center}

### 2020-11-01 paper.tex
Updates from Overleaf

--- 2020-10-29 paper.tex
@@
 
-Chan et al.   \cite{chan2016anticipating}
-approach the same problem of collision prediction via egocentric dash-cam videos.
+Chan et al.
+\cite{chan2016anticipating} approach the same problem of collision prediction via egocentric dash-cam videos.
 They propose a novel Dynamic-Spatial-Attention Recurrent Neural Network that distributes attention to localized and tracked vehicles within the video and models temporal dependencies to predict the earliest frame of a potential impending collision.
@@
 \section{METHODOLOGY}
+
+The software pipeline is built of multiple executors that each process or handle the data corresponding to a single video before piping the resulting data to the next
 
@@
 
-This software module is encapsulated as a library and can be reused easily by importing our \texttt{anonymization} package as a dependency.
+This software module is encapsulated as a library and can be reused by importing our \texttt{anonymization} package as a dependency.
 The accuracy, amount and type of blurring applied can be tweaked using the API exposed by the \texttt{anonymization} package.

### 2020-11-01 paper.tex
Fixing the build errors and adding CSVs to support overleaf build

@@
 Consequently, our pipeline contains a post-processing stage in which we apply blurring masks to anonymize any personally identifiable information.
-Specifically, we provide two executors to perform these anonymization tasks: \textttt{FaceBlurrer}, which blurs faces and \texttt{LicensePlateBlurrer} which blurs license plates.
+Specifically, we provide two executors to perform these anonymization tasks: \texttt{FaceBlurrer}, which blurs faces and \texttt{LicensePlateBlurrer} which blurs license plates.
 Both of these executors are powered by pre-trained machine learning models which detect regions containing personally identifiable information.
-Specifically, for  \textttt{FaceBlurrer}, we use a MobileNet Single Shot MultiBox Detector (TODO: cite https://github.com/yeephycho/tensorflow-face-detection) and for \texttt{LicensePlateBlurrer} we use a Convolutional Neural Network (TODO: cite http://sergiomsilva.com/pubs/alpr-unconstrained/).
+Specifically, for  \texttt{FaceBlurrer}, we use a MobileNet Single Shot MultiBox Detector (TODO: cite https://github.com/yeephycho/tensorflow-face-detection) and for \texttt{LicensePlateBlurrer} we use a Convolutional Neural Network (TODO: cite http://sergiomsilva.com/pubs/alpr-unconstrained/).
 

### 2020-11-01 paper.tex
Updates from Overleaf

--- 2020-11-01 paper.tex
@@
 
-The software pipeline is built of multiple executors that each process or handle the data corresponding to a single video before piping the resulting data to the next
+The software pipeline is built of multiple executors that each process or handle the data corresponding to a single video before piping the resulting data to the next executor.
 

### 2020-11-11 paper.tex
Adding 2 histograms

--- 2020-11-01 paper.tex
@@
 \pgfplotstableread[col sep=comma]{by-classes.csv}\byclass
+\pgfplotstableread[col sep=comma]{by-actors.csv}\byactors
+\pgfplotstableread[col sep=comma]{by-duration.csv}\byduration
 
@@
 		\label{fig:obj-by-class}
+\end{figure}
+
+\begin{figure}[htpb]
+		\centering
+    \begin{tikzpicture}
+    \begin{axis}[
+      title={Videos by actors},
+      xlabel={Number of actors},
+      ylabel={Frequency (\# of videos)},
+      xtick=data,
+      xticklabels from table={\byactors}{X}
+    ]
+    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
+    \end{axis}
+    \end{tikzpicture}
+		\caption{Videos by number of actors}
+		\label{fig:vids-by-actors}
+\end{figure}
+
+\begin{figure}[htpb]
+		\centering
+    \begin{tikzpicture}
+    \begin{axis}[
+      title={Videos by duration},
+      xlabel={Duration (in frames)},
+      ylabel={Frequency (\# of videos)},
+      xtick=data,
+      xticklabels from table={\byduration}{X}
+    ]
+    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byduration;
+    \end{axis}
+    \end{tikzpicture}
+		\caption{Videos by duration}
+		\label{fig:vids-by-duration}
 \end{figure}

### 2020-11-11 scripts/make_by-actors.py

@@ -1,0 +1,43 @@
+import numpy as np
+import firebase_admin as fb
+from firebase_admin import credentials, db
+from firebase_admin.db import Reference
+from functools import reduce
+
+FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
+
+def histogram_by_duration(hist, data):
+    (key, data) = data
+    if data.get('is_cancelled', True):
+        return hist
+    """
+    Uncomment this code if you want to ignore unlabelled & uncancelled data
+    if 'bb_fields' not in data or 'ids' not in data['bb_fields']:
+       return
+    """
+    num_actors = max(data.get('bb_fields', {}).get('ids', [float('-inf')]))
+    hist[num_actors] = hist.get(num_actors, 0) + 1
+    return hist
+
+if __name__ == '__main__':
+    cred = credentials.Certificate(FIREBASE_CRED_FILENAME)
+    print('Created credentials')
+    fb_app = fb.initialize_app(cred, {
+            'databaseURL': 'https://autodash-9dccb.firebaseio.com/',
+            'databaseAuthVariableOverride': {
+                'uid': 'pipeline-worker'
+            }
+        })
+    print('Created app')
+    metadata = db.reference('metadata')
+    print('Retrieved data')
+    data = [ val for val in metadata.get().items() ]
+    hist = reduce(histogram_by_duration, data, {})
+    if float('-inf') in hist:
+        hist['Unknown'] = hist[float('-inf')]
+        del hist[float('-inf')]
+    print(hist)
+    dtype = [ ('X', object), ('Y', np.uint32) ]
+    Z = np.array([ *hist.items() ], dtype=dtype)
+    np.savetxt('by-actors.csv', Z, delimiter=',', fmt=['%s', '%d'], header='X,Y', comments='')
+

### 2020-11-11 scripts/make_by-duration.py

@@ -1,0 +1,38 @@
+import numpy as np
+import firebase_admin as fb
+from firebase_admin import credentials, db
+from firebase_admin.db import Reference
+from functools import reduce
+
+FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
+
+def histogram_by_duration(hist, data):
+    (key, data) = data
+    if data.get('is_cancelled', True):
+        return hist
+    num_frames = data.get('end_i', float('inf')) - data.get('start_i', float('-inf'))
+    hist[num_frames] = hist.get(num_frames, 0) + 1
+    return hist
+
+if __name__ == '__main__':
+    cred = credentials.Certificate(FIREBASE_CRED_FILENAME)
+    print('Created credentials')
+    fb_app = fb.initialize_app(cred, {
+            'databaseURL': 'https://autodash-9dccb.firebaseio.com/',
+            'databaseAuthVariableOverride': {
+                'uid': 'pipeline-worker'
+            }
+        })
+    print('Created app')
+    metadata = db.reference('metadata')
+    print('Retrieved data')
+    data = [ val for val in metadata.get().items() ]
+    hist = reduce(histogram_by_duration, data, {})
+    if float('inf') in hist:
+        hist['Unknown'] = hist[float('inf')]
+        del hist[float('inf')]
+    print(hist)
+    dtype = [ ('X', object), ('Y', np.uint32) ]
+    Z = np.array([ *hist.items() ], dtype=dtype)
+    np.savetxt('by-duration.csv', Z, delimiter=',', fmt=['%s', '%d'], header='X,Y', comments='')
+

### 2020-11-11 paper.tex

@@
 \newcommand{\todo}[1]{{\color{red}#1}}
+\usepackage{listings, xcolor}
+
+\colorlet{punct}{red!60!black}
+\definecolor{background}{HTML}{EEEEEE}
+\definecolor{delim}{RGB}{20,105,176}
+\colorlet{numb}{magenta!60!black}
+
+\lstdefinelanguage{json}{
+    basicstyle=\normalfont\ttfamily,
+    numbers=left,
+    numberstyle=\scriptsize,
+    stepnumber=1,
+    numbersep=8pt,
+    showstringspaces=false,
+    breaklines=true,
+    frame=lines,
+    backgroundcolor=\color{background},
+    literate=
+     *{0}{{{\color{numb}0}}}{1}
+      {1}{{{\color{numb}1}}}{1}
+      {2}{{{\color{numb}2}}}{1}
+      {3}{{{\color{numb}3}}}{1}
+      {4}{{{\color{numb}4}}}{1}
+      {5}{{{\color{numb}5}}}{1}
+      {6}{{{\color{numb}6}}}{1}
+      {7}{{{\color{numb}7}}}{1}
+      {8}{{{\color{numb}8}}}{1}
+      {9}{{{\color{numb}9}}}{1}
+      {:}{{{\color{punct}{:}}}}{1}
+      {,}{{{\color{punct}{,}}}}{1}
+      {\{}{{{\color{delim}{\{}}}}{1}
+      {\}}{{{\color{delim}{\}}}}}{1}
+      {[}{{{\color{delim}{[}}}}{1}
+      {]}{{{\color{delim}{]}}}}{1},
+}
 
@@
 
-\begin{figure}[htpb]
-		\centering
-		% TODO: Uncomment this
-    %\includegraphics[width=0.5\textwidth]{images/example_metadata.png}
-		\caption{An example of metadata for a labelled video.
-Both automatic metadata about the source of the video and manual annotation of the collision is maintained.
-Each bounding box contains the object classification, a unique identifier and a boolean value representing if the tracked agent is involved in a collision.}
-		\label{fig:images-example_metadata-png}
+\subsection{Metadata}
+After all of the previous steps have been completed, the pipeline is able to produce a metadata object.
+There are many fields in the metadata object (as can be seen in Figure \ref{metadata_example}):
+
+\begin{itemize}
+  \item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
+  \item "description" contains a breif description of the video as scraped from the video hosting website
+  \item "download\_src" contains the site that the video was sourced from (e.g. YouTube)
+  \item "tags" is an object that contains custom user-defined tags on videos and additional data that is site specific
+  \item "title" is a string that represents the type of the video
+  \item "url" is the url that the video was fetched from
+  \item "is\_split\_url" is a boolean that represents if all of the frames of the video have bounding boxes in this metadata
+  \item "start\_i" is the start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
+  \item "end\_i" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
+  \item "bb\_fields" contains all bounding-box specific data. Each entry is a list, where the $i_{th}$ index in each contains the data for one bounding-box:
+  \begin{itemize}
+    \item "ids[$i$]" represents what vehicle id the $i_{th}$ bounding box represents. Each vehicle in the video has it's own unique id
+    \item "cls[$i$]" represents the object class of the vehicle
+    \item "frames[$i$]" represents what frame of the video the $i_{th}$ bounding box is for
+    \item "has\_collision[$i$]" represents if the vehicle with id $ids[i]$ is in a collision
+    \item "x1s[$i$], y1s[$i$], x2s[$i$], y2s[$i$]" are the coordinates of the two points $(x_1,y_1)$ \& $(x_2,y_2)$ that make bounding box $i$
+  \end{itemize}
+\end{itemize}`
+
+\begin{figure}
+  \begin{lstlisting}[language=json]
+    {
+      "collision_type":"",
+      "description":"",
+      "download_src":"",
+      "tags": {
+        "reddit_post_info":{
+          "id":"<post_id>"
+          "title":"title"
+        }
+      },
+      "title":"Title of the Video",
+      "url":"http:/www.myvideo.com",
+      "is_split_url": false,
+      "start_i": 0,
+      "end_i": 60,
+      "bb_fields": {
+        "cls": [],
+        "frames": [],
+        "has_collision": [],
+        "ids": [],
+        "x1s": [],
+        "y1s": [],
+        "x2s": [],
+        "y2s": [],
+      }
+    }
+  \end{lstlisting}
+    \caption{Example Metadata Produced by the Pipeline}
+    \label{metadata_example}
 \end{figure}
-
-\todo{Use a better image}
 

### 2020-11-12 scripts/make_by-actors.py
Fixing some issues with new histograms

@@ -10,11 +10,8 @@ def histogram_by_duration(hist, data):
     (key, data) = data
     if data.get('is_cancelled', True):
         return hist
-    """
-    Uncomment this code if you want to ignore unlabelled & uncancelled data
     if 'bb_fields' not in data or 'ids' not in data['bb_fields']:
-       return
-    """
+       return hist
     num_actors = max(data.get('bb_fields', {}).get('ids', [float('-inf')]))
     hist[num_actors] = hist.get(num_actors, 0) + 1
     return hist
@@ -39,5 +36,6 @@ if __name__ == '__main__':
     print(hist)
     dtype = [ ('X', object), ('Y', np.uint32) ]
     Z = np.array([ *hist.items() ], dtype=dtype)
+    Z = np.sort(Z, axis=0)
     np.savetxt('by-actors.csv', Z, delimiter=',', fmt=['%s', '%d'], header='X,Y', comments='')
 

### 2020-11-12 scripts/make_by-duration.py

@@ -10,8 +10,9 @@ def histogram_by_duration(hist, data):
     (key, data) = data
     if data.get('is_cancelled', True):
         return hist
-    num_frames = data.get('end_i', float('inf')) - data.get('start_i', float('-inf'))
-    hist[num_frames] = hist.get(num_frames, 0) + 1
+    if 'end_i' not in data or 'start_i' not in data:
+        return hist
+    hist.append(data.get('end_i', float('inf')) - data.get('start_i', float('-inf')))
     return hist
 
 if __name__ == '__main__':
@@ -27,12 +28,14 @@ if __name__ == '__main__':
     metadata = db.reference('metadata')
     print('Retrieved data')
     data = [ val for val in metadata.get().items() ]
-    hist = reduce(histogram_by_duration, data, {})
+    hist = reduce(histogram_by_duration, data, [])
+    hist, bins = np.histogram(hist, bins=10)
+    """
     if float('inf') in hist:
         hist['Unknown'] = hist[float('inf')]
         del hist[float('inf')]
-    print(hist)
-    dtype = [ ('X', object), ('Y', np.uint32) ]
-    Z = np.array([ *hist.items() ], dtype=dtype)
+    """
+    dtype = [ ('X', np.uint32), ('Y', np.uint32) ]
+    Z = np.array([ *zip(bins, hist) ], dtype=dtype)
     np.savetxt('by-duration.csv', Z, delimiter=',', fmt=['%s', '%d'], header='X,Y', comments='')
 

### 2020-12-03 paper.tex
+ Manual review of paper + adding pie charts to paper + adding new agents histogram + added abstract + Removed anonymization

@@
 
-\todo{Write the abstract}
+The international movement towards developing autonomous vehicle technologies has raised concerns in all spheres of civilization: from legal perspectives to ethical dilemmas; from control theory to safety engineering; from cybersecurity to realtime computing.
+Over the
+last decade, some emphasis has been made on the need for these vehicles to reduce road collisions and reckless driving.
+However, research into collision avoidance have been slowed down by the lack of egocentric footage dataset.
+Currently, these types of datasets are most effectively created through computer generated scenarios because of the dangerous and costly nature of road collisions.
+We provide a pipeline to assemble datasets of real events that have been published online to complement alredy existing methods.
+Our aggregated dataset includes egocentric vehicle footage from all over the world: varying visibilities, varying weather conditions, and varying settings.
 
@@
 In the advent of connected vehicles and autonomous transportation, equipping consumer vehicles with the necessary equipment to facilitate high-end automated collision avoidance systems can be prohibitively expensive.
-Technologies such as Radar, LIDAR and high-end cameras that are typically used for collision prediction are likely too expensive for most consumers and might not easily be affixed to their vehicles (maybe not true).
+Technologies such as Radar, LIDAR and high-end cameras that are typically used for collision prediction are likely too expensive for most consumers.
 On the other hand dash-cams, cheap video cameras that can be mounted to a car's dashboard, have become increasingly affordable and prevalent as a means to capture a driver’s perspective.
@@
 This combination allows us to take advantage of the wide variety of videos available on the internet, while still having reliable data that has been curated manually.
-\todo{Not sure what else to put here}
 
@@
 
-\subsection{Dash-cams}%
-\label{sub:dash_cams}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The software pipeline is built of multiple executors that each process or handle the data corresponding to a single video before piping the resulting data to the next executor.
-
-\todo{Write the METHODOLOGY}
-\begin{itemize}
-  \item Major pipeline
-  \item Presenting a graph or figure of the pipeline architecture
-  \begin{itemize}
-    \item pre-processing
-    \item Tracking we can mention how prepare to solve the tracking problem (challenge and future work)
-    \item Anonymization (tracking and blurring of vehicle plates and faces)
-  \end{itemize}
-\end{itemize}
 
@@
       \node[module, below=of splitter] (labeller) {Video-Labelling Tool};
-      \node[module, below=of labeller] (face-blur) {Face Blurring};
-      \node[module, below=of face-blur] (license-blur) {License Plate Blurring};
-      \node[draw,inner xsep=4mm,inner ysep=7mm,fit=(face-blur)(license-blur)](anon){};
-      \node[anchor=north west,inner sep=1pt] at (anon.north west) 
-        {Anonymization};
-      \node[module, below=of anon] (uploader) {Data-Uploader};
+      \node[module, below=of labeller] (uploader) {Data-Uploader};
       \draw[->] (crawler)--(downloader);
@@
       \draw[->] (splitter)--(labeller);
-      \draw[->] (labeller)--(face-blur);
-      \draw[->] (face-blur)--(license-blur);
-      \draw[->] (license-blur)--(uploader);
+      \draw[->] (labeller)--(uploader);
 
@@
 Users may define their own search terms to be used when querying the video repository.
-This value can be set either in the crawler implementation (\todo{or the yaml pipeline configuration file?}).
-By default, our scrapers query using the keywords: (\todo{should probably define default keywords}).
+This value can be set in the yaml pipeline configuration file.
+By default, our scrapers query using the keywords: \texttt{Car crash dashcam}.
 Currently we support scraping and querying Reddit, YouTube and Imgur.
@@
 
-\subsection{Video Preprocessing}
-
-\subsection{Automatic Annotation}
-\subsection{Object Detection \& Tracking}
-\todo{Automated object detection not used right now?}
-\subsection{Anonymization}
-An important facet of automobile data aggregation is in eliminating biases and protecting the identities of depicted individuals.
+% HAS BEEN REMOVED BECAUSE NOT FUNCTIONAL
+%\subsection{Video Preprocessing}
+%\subsection{Automatic Annotation}
+%\subsection{Object Detection \& Tracking}
+%\todo{Automated object detection not used right now?}
+%\subsection{Anonymization}
+%An important facet of automobile data aggregation is in eliminating biases and protecting the identities of depicted individuals.
 Consequently, our pipeline contains a post-processing stage in which we apply blurring masks to anonymize any personally identifiable information.
@@
 Specifically, for  \texttt{FaceBlurrer}, we use a MobileNet Single Shot MultiBox Detector (TODO: cite https://github.com/yeephycho/tensorflow-face-detection) and for \texttt{LicensePlateBlurrer} we use a Convolutional Neural Network (TODO: cite http://sergiomsilva.com/pubs/alpr-unconstrained/).
-
-This software module is encapsulated as a library and can be reused by importing our \texttt{anonymization} package as a dependency.
+%
+%This software module is encapsulated as a library and can be reused by importing our \texttt{anonymization} package as a dependency.
 The accuracy, amount and type of blurring applied can be tweaked using the API exposed by the \texttt{anonymization} package.
@@
 Object tracking bounding boxes can be linearly interpolated from manual start and end points to improve ease of labelling.
-We also save the video resolution at which the video was annotated to ensure bounding box annotations can always be scaled to fit any variable download resolutions (\todo{Is this a useful feature to have?}).For long-form videos that may contain multiple collision events or irrelevant video segments, such as compilation videos or videos with substantial editing and transitions, we provide a video clipping feature to demarcate the collision events from which we extract and generate distinct data points.
+\todo{We don't do this???
+We also save the video resolution at which the video was annotated to ensure bounding box annotations can always be scaled to fit any variable download resolutions}.
+For long-form videos that may contain multiple collision events or irrelevant video segments, such as compilation videos or videos with substantial editing and transitions, we provide a video clipping feature to demarcate the collision events from which we extract and generate distinct data points.
+Each video segment will eventually become a metadata item.
 
-\todo{Talk more about clipping and how we generate distinct data points after clipping}
+Once clipping is complete, each video must be manually labelled.
+Each object within a video segment must be bounded at every frame.
+To fasten this process, we provide an interpolation feature which will fill gaps between two entered bounding boxes.
 
@@
 \section{EXPERIMENT}
-- present results of our data, reference the Kitti dataset and how they presented their own data (histogram of object classes, velocity, acceleration, etc)
 
-- the major contribution we have is the histogram of accident type
-
-- Histogram of data
-
-- Usage of our data (applications) - not a major section, just describe potential in preventing/predicting accidents and their importance
-
-\todo{Write the EXPERIMENT SECTION (analyzing data)}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{CONCLUSION}
-
-\todo{Write the conclusion}
-A conclusion section is not required.
-Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion.
-A conclusion might elaborate on the importance of the work or suggest applications and extensions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{FUTURE WORK}
-
-There are many ways that we could improve on our system. This are just a series of ideas that we could think of:
-\begin{enumerate}
-\item Custom interpolation between input frames: One idea would be to make it easier to modify the method of interpolation between frames.
-Currently, linear interpolation is always used.
-Moreover, given a type of interpolation is stored in the metadata, we probably shouldn't store all interpolated frames, rather than just the ones the user has entered.
-While linear interpolation works great for entering a frame every 10 frames, supporting more interpolations could be great for faster data entry, or even for supporting affine transformations on more complex bounds.
-
-\item Polyhedral bounds: It's always possible to represent a 2-dimensional polyhedron with a matrix $A\in\mathbb{R}^{n\times 2}$, and a vector $b\in\mathbb{R}^2$, given that the polyhedron can be represented by the set $\left\{x\mid Ax\leq b\right\}$.
-We could use this idea to store masking bounds that can be used for training Mask-RCNN networks in (near-)collision contexts.
-
-\item Web interface: Having a web-based user interface would be advantageous for this project.
-While currently being used in the context of (near-)collision accident, this software has the potential to become a platform for scraping automation and collaboration.
-Ideally, people without a technical background would be able to contribute to the microtasking involved, and technical contributors would be in charge of creating and managing the automation and general design of the pipeline.
-
-\end{enumerate}
-\todo{Write the future work ideas}
-
-\addtolength{\textheight}{-12cm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{APPENDIX}
-
-\todo{Write the appendix}
+\todo{We are currently still assembling our dataset.
+At the time of this writing, we only have 67 positive videos labelled.
+By using many heuristics like splitting video segments into 5s snippets, we can duplicate our dataset
+by introducing negatives from positive labelled videos.
+However, we must be concious to preserve a near 1:1 positives to negatives ratio in our testing set.
+Because of our low turnout, some of the results described below are likely inaccurate and subject to change.
+}
 
@@
 \pgfplotstableread[col sep=comma]{by-actors.csv}\byactors
+\pgfplotstableread[col sep=comma]{by-agents.csv}\byagents
 \pgfplotstableread[col sep=comma]{by-duration.csv}\byduration
+
+We have aggregated some statistics about our dataset to help clients understand various distributions in the data.
+While these distributions may be representative of online collision footage, they are not necessarily of real world collisions.
 
@@
       title={Objects by class},
-      xlabel={Class},
-      ylabel={Frequency (\# of bounding boxes)},
+      ylabel={Frequency (\# of objects)},
       xtick=data,
-      xticklabels from table={\byclass}{X}
+      xticklabels from table={\byclass}{X},
+      xticklabel style={rotate=90}
     ]
@@
     \begin{axis}[
+      title={Videos by agents},
+      xlabel={Number of agents},
+      ylabel={Frequency (\# of videos)},
+      xtick=data,
+      xticklabels from table={\byagents}{X}
+    ]
+    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byagents;
+    \end{axis}
+    \end{tikzpicture}
+		\caption{Videos by number of agents}
+		\label{fig:vids-by-agents}
+\end{figure}
+
+\begin{figure}[htpb]
+		\centering
+    \begin{tikzpicture}
+    \begin{axis}[
       title={Videos by duration},
@@
 
-\begin{center}
-\begin{tikzpicture}
-\begin{axis}[
-  title={Example histogram},
-  xlabel={Classes},
-  ylabel={$\textup{Normal}(\mu=0, \sigma=1)$}
-]
-\addplot[fill, ybar] table [x=X, y=Y, col sep=comma] {example.csv};
-\end{axis}
-\end{tikzpicture}
-\end{center}
+\begin{figure}[htpb]
+		\centering
+    \includegraphics[width=3in]{by-collision.png}
+		\caption{Videos by collision}
+		\label{fig:vids-by-collision}
+\end{figure}
+
+\begin{figure}[htpb]
+		\centering
+    \includegraphics[width=3in]{by-camera.png}
+		\caption{Videos by camera}
+		\label{fig:vids-by-camera}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{CONCLUSION}
+
+%\todo{Write the conclusion}
+%A conclusion section is not required.
+Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion.
+A conclusion might elaborate on the importance of the work or suggest applications and extensions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{FUTURE WORK}
+
+There are many ways that we could improve on our system. This are just a series of ideas that we could think of:
+\begin{enumerate}
+\item Custom interpolation between input frames: One idea would be to make it easier to modify the method of interpolation between frames.
+Currently, linear interpolation is always used.
+Moreover, given a type of interpolation is stored in the metadata, we probably shouldn't store all interpolated frames, rather than just the ones the user has entered.
+While linear interpolation works great for entering a frame every 10 frames, supporting more interpolations could be great for faster data entry, or even for supporting affine transformations on more complex bounds.
+
+\item Polyhedral bounds: It's always possible to represent a 2-dimensional polyhedron with a matrix $A\in\mathbb{R}^{n\times 2}$, and a vector $b\in\mathbb{R}^2$, given that the polyhedron can be represented by the set $\left\{x\mid Ax\leq b\right\}$.
+We could use this idea to store masking bounds that can be used for training Mask-RCNN networks in (near-)collision contexts.
+This however would be
+
+\item Web interface: Having a web-based user interface would be advantageous for this project.
+While currently being used in the context of (near-)collision accident, this software has the potential to become a platform for scraping automation and collaboration.
+Ideally, people without a technical background would be able to contribute to the microtasking involved, and technical contributors would be in charge of creating and managing the automation and general design of the pipeline.
+
+\end{enumerate}
+
+\addtolength{\textheight}{-12cm}
 

### 2020-12-03 scripts/count_bbs.py

@@ -6,15 +6,13 @@ from functools import reduce
 
 FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
 
-def histogram_by_duration(hist, data):
+def count_bbs(count, data):
     (key, data) = data
     if data.get('is_cancelled', True):
-        return hist
-    if 'bb_fields' not in data or 'ids' not in data['bb_fields']:
-       return hist
-    num_actors = len(set(data.get('bb_fields', {}).get('ids', [])))
-    hist[num_actors] = hist.get(num_actors, 0) + 1
-    return hist
+        return count
+    if 'bb_fields' not in data:
+       return count
+    return count + 1
 
 if __name__ == '__main__':
     cred = credentials.Certificate(FIREBASE_CRED_FILENAME)
@@ -29,10 +27,6 @@ if __name__ == '__main__':
     metadata = db.reference('metadata')
     print('Retrieved data')
     data = [ val for val in metadata.get().items() ]
-    hist = reduce(histogram_by_duration, data, {})
-    print(hist)
-    dtype = [ ('X', object), ('Y', np.uint32) ]
-    Z = np.array([ *hist.items() ], dtype=dtype)
-    Z = np.sort(Z, axis=0)
-    np.savetxt('by-actors.csv', Z, delimiter=',', fmt=['%s', '%d'], header='X,Y', comments='')
+    count = reduce(count_bbs, data, 0)
+    print(count)
 

### 2020-12-03 scripts/make_by-agents.py

@@ -12,8 +12,15 @@ def histogram_by_duration(hist, data):
         return hist
     if 'bb_fields' not in data or 'ids' not in data['bb_fields']:
        return hist
-    num_actors = len(set(data.get('bb_fields', {}).get('ids', [])))
-    hist[num_actors] = hist.get(num_actors, 0) + 1
+    num_agents = 0
+    viewed_ids = set()
+    ids = data.get('bb_fields', {}).get('ids')
+    collisions = data.get('bb_fields', {}).get('has_collision')
+    for id, has_collision in zip(ids, collisions):
+        if has_collision and id not in viewed_ids:
+            viewed_ids.add(id)
+            num_agents += 1
+    hist[num_agents] = hist.get(num_agents, 0) + 1
     return hist
 
 if __name__ == '__main__':
@@ -34,5 +41,4 @@ if __name__ == '__main__':
     dtype = [ ('X', object), ('Y', np.uint32) ]
     Z = np.array([ *hist.items() ], dtype=dtype)
     Z = np.sort(Z, axis=0)
-    np.savetxt('by-actors.csv', Z, delimiter=',', fmt=['%s', '%d'], header='X,Y', comments='')
-
+    np.savetxt('by-agents.csv', Z, delimiter=',', fmt=['%s', '%d'], header='X,Y', comments='')

### 2020-12-03 scripts/make_by-camera.py

@@ -3,17 +3,22 @@ import firebase_admin as fb
 from firebase_admin import credentials, db
 from firebase_admin.db import Reference
 from functools import reduce
+from matplotlib import pyplot as plt
 
 FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
 
-def histogram_by_duration(hist, data):
+def pie_by_camera(hist, data):
     (key, data) = data
-    if data.get('is_cancelled', True):
+    if not data.get('enum_tags'):
         return hist
-    if 'bb_fields' not in data or 'ids' not in data['bb_fields']:
-       return hist
-    num_actors = len(set(data.get('bb_fields', {}).get('ids', [])))
-    hist[num_actors] = hist.get(num_actors, 0) + 1
+    enum_tags = data['enum_tags']
+    if 'StationaryCamera' in enum_tags:
+        hist.update({ 'StationaryCamera': hist.get('StationaryCamera', 0) + 1 })
+    elif 'ManHeldCamera' in enum_tags:
+        hist.update({ 'ManHeldCamera': hist.get('ManHeldCamera', 0) + 1 })
+    else:
+        hist.update({ 'DashCamera': hist.get('DashCamera', 0) + 1 })
+
     return hist
 
 if __name__ == '__main__':
@@ -29,10 +34,7 @@ if __name__ == '__main__':
     metadata = db.reference('metadata')
     print('Retrieved data')
     data = [ val for val in metadata.get().items() ]
-    hist = reduce(histogram_by_duration, data, {})
-    print(hist)
-    dtype = [ ('X', object), ('Y', np.uint32) ]
-    Z = np.array([ *hist.items() ], dtype=dtype)
-    Z = np.sort(Z, axis=0)
-    np.savetxt('by-actors.csv', Z, delimiter=',', fmt=['%s', '%d'], header='X,Y', comments='')
-
+    pie = reduce(pie_by_camera, data, {})
+    fig, ax = plt.subplots()
+    ax.pie(pie.values(), labels=pie.keys(), autopct='%1.1f%%')
+    fig.savefig('by-camera.png')

### 2020-12-03 scripts/make_by-classes.py

@@ -10,8 +10,13 @@ def histogram_by_class(hist, data):
     (key, data) = data
     if data.get('is_cancelled', True):
         return hist
-    for cls in data.get('bb_fields', {}).get('clss', []):
-        hist[cls] = hist.get(cls, 0) + 1
+    viewed_ids = set()
+    clss = data.get('bb_fields', {}).get('clss', [])
+    ids = data.get('bb_fields', {}).get('ids', [])
+    for cls, id in zip(clss, ids):
+        if id not in viewed_ids:
+            viewed_ids.add(id)
+            hist[cls] = hist.get(cls, 0) + 1
     return hist
 
 if __name__ == '__main__':

### 2020-12-03 scripts/make_by-collision.py

@@ -3,17 +3,22 @@ import firebase_admin as fb
 from firebase_admin import credentials, db
 from firebase_admin.db import Reference
 from functools import reduce
+from matplotlib import pyplot as plt
 
 FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
 
-def histogram_by_duration(hist, data):
+def pie_by_collision(hist, data):
     (key, data) = data
-    if data.get('is_cancelled', True):
+    if not data.get('enum_tags'):
         return hist
-    if 'bb_fields' not in data or 'ids' not in data['bb_fields']:
-       return hist
-    num_actors = len(set(data.get('bb_fields', {}).get('ids', [])))
-    hist[num_actors] = hist.get(num_actors, 0) + 1
+    enum_tags = data['enum_tags']
+    if 'MultiCollision' in enum_tags:
+        hist.update({ 'MultiCollision': hist.get('MultiCollision', 0) + 1 })
+    elif 'NoCollision' in enum_tags:
+        hist.update({ 'NoCollision': hist.get('NoCollision', 0) + 1 })
+    else:
+        hist.update({ 'SimpleCollision': hist.get('SimpleCollision', 0) + 1 })
+
     return hist
 
 if __name__ == '__main__':
@@ -29,10 +34,7 @@ if __name__ == '__main__':
     metadata = db.reference('metadata')
     print('Retrieved data')
     data = [ val for val in metadata.get().items() ]
-    hist = reduce(histogram_by_duration, data, {})
-    print(hist)
-    dtype = [ ('X', object), ('Y', np.uint32) ]
-    Z = np.array([ *hist.items() ], dtype=dtype)
-    Z = np.sort(Z, axis=0)
-    np.savetxt('by-actors.csv', Z, delimiter=',', fmt=['%s', '%d'], header='X,Y', comments='')
-
+    pie = reduce(pie_by_collision, data, {})
+    fig, ax = plt.subplots()
+    ax.pie(pie.values(), labels=pie.keys(), autopct='%1.1f%%')
+    fig.savefig('by-collision.png')

### 2020-12-03 scripts/make_by-duration.py

@@ -10,6 +10,8 @@ def histogram_by_duration(hist, data):
     (key, data) = data
     if data.get('is_cancelled', True):
         return hist
+    if 'bb_fields' not in data:
+        return hist
     if 'end_i' not in data or 'start_i' not in data:
         return hist
     hist.append(data.get('end_i', float('inf')) - data.get('start_i', float('-inf')))

### 2020-12-03 paper.tex
Meeting changes

@@
 Currently, these types of datasets are most effectively created through computer generated scenarios because of the dangerous and costly nature of road collisions.
-We provide a pipeline to assemble datasets of real events that have been published online to complement alredy existing methods.
+We provide a pipeline to assemble datasets of real events that have been published online to complement already existing methods.
 Our aggregated dataset includes egocentric vehicle footage from all over the world: varying visibilities, varying weather conditions, and varying settings.
@@
 We aim to generate datasets that are not constrained to any regions or countries but rather provide location-agnostic data that is representative of general, global road and vehicle conditions.
-These datasets will also be collision-oriented as the majority of these videos contain collisions for people's entertainment.
+These datasets will also be collision-oriented as the majority of these videos contain collisions for people's viewing.
 Current autonomous vehicle data collection techniques typically require astronomically expensive hardware and equipment and, consequently, are rarely involved in collisions and intentionally not put in high risk environments that may lead to a collision.
@@
 This combination allows us to take advantage of the wide variety of videos available on the internet, while still having reliable data that has been curated manually.
+As part of this data, we identify participants and bystanders, both known as agents.
+Participants are objects that are involved in a collision identified in the metadata, while bystanders are objects that are not.
 
@@
 
-The entry into our pipeline is a set of web scraper executors that each target and scrape a specific website or video repository based on a user-defined set of key-terms, and an executor that pulls unlabelled videos from the user's database.
+The entry into our pipeline is a set of web scraper executors that each target and scrape a specific website or video repository based on a user-defined set of key-terms, and a \textit{database source executor} that pulls unlabelled videos from the user's database.
 Videos that are pulled by the scrapers are immediately added to the database with relevant metadata and marked as unlabelled.
 Subsequently, they are loaded into memory and sequentially fed into the pipeline.
-If the pipeline terminates before labelling a video, it remains flagged as unlabelled in the database and the video will be pulled in a subsequent run by the database source executor.
+If the pipeline terminates before labelling a video, it remains flagged as unlabelled in the database and the video will be pulled in a subsequent run by the \textit{database source executor}.
 Crawler state is maintained via database lookup of specified key-value pairs to ensure duplicate data is not pulled.
@@
 Users may define their own search terms to be used when querying the video repository.
-This value can be set in the yaml pipeline configuration file.
+This value can be set in a YAML pipeline configuration file.
 By default, our scrapers query using the keywords: \texttt{Car crash dashcam}.
-Currently we support scraping and querying Reddit, YouTube and Imgur.
+Currently we support querying Reddit and YouTube, downloading from YouTube and Imgur.
 Users that want to pull from a video repository that is not currently implemented should create a custom executor and implement the \texttt{iCrawler} interface.
-This new executor should be added as an entry point in a new yaml configuration and should generate and return a \texttt{MetaDataItem} with video source information to be used by a subsequent and corresponding downloader.
-\texttt{MetaDataItem} objects are fed into the \texttt{UniversalDownloader} which aggregates \texttt{iDownloader} implementations and distributes \texttt{MetaDataItem} objects to their corresponding downloader via regex matching of source URL's.
-New downloaders should registered with the \texttt{UniversalDownloader} via the yaml pipeline configuration along with a regex string for url matching.
-\todo{Maybe this should be refactored to just pass iCrawler output directly to its downloader}
+This new executor should be added as an entry point in a new YAML configuration and should generate and return a \texttt{MetaDataItem} with video source information to be used by a subsequent and corresponding downloader.
+\texttt{MetaDataItem} objects are fed into the \texttt{UniversalDownloader} which aggregates \texttt{iDownloader} implementations and distributes \texttt{MetaDataItem} objects to their corresponding downloader via regular expressions matching of source URL's.
+New downloaders should be registered with the \texttt{UniversalDownloader} via a YAML pipeline configuration along with a regular expression string for URL matching.
 
@@
 In addition to collection and preprocessing, a core component of our pipeline is a GUI tool that facilitates the manual annotation of the dash-cam videos, and quick manual filtering of non-dashcam and irrelevant videos.
-Following Chan et al.\cite{chan2016anticipating}, if a collision occurs we provide tools to annotate the frame the collision occurs, and bounding boxes to localize, identify and track agents both involved and not involved in the collision.
+Following Chan et al.\cite{chan2016anticipating}, if a collision occurs we provide tools to annotate the frame the collision occurs, and bounding boxes to localize, identify and track agents in the video segment.
 Object tracking bounding boxes can be linearly interpolated from manual start and end points to improve ease of labelling.
-\todo{We don't do this???
-We also save the video resolution at which the video was annotated to ensure bounding box annotations can always be scaled to fit any variable download resolutions}.
+We don't do this???
+We also save the video resolution at which the video was annotated to ensure bounding box annotations can always be scaled to fit any variable download resolutions.
 For long-form videos that may contain multiple collision events or irrelevant video segments, such as compilation videos or videos with substantial editing and transitions, we provide a video clipping feature to demarcate the collision events from which we extract and generate distinct data points.
@@
 
-Once clipping is complete, each video must be manually labelled.
-Each object within a video segment must be bounded at every frame.
-To fasten this process, we provide an interpolation feature which will fill gaps between two entered bounding boxes.
-
 \subsection{Metadata}
-After all of the previous steps have been completed, the pipeline is able to produce a metadata object.
+After all of the previous steps have been completed, the pipeline is able to produce a complete metadata object.
 There are many fields in the metadata object (as can be seen in Figure \ref{metadata_example}):
@@
 \begin{itemize}
-  \item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
-  \item "description" contains a breif description of the video as scraped from the video hosting website
-  \item "download\_src" contains the site that the video was sourced from (e.g. YouTube)
-  \item "tags" is an object that contains custom user-defined tags on videos and additional data that is site specific
-  \item "title" is a string that represents the type of the video
-  \item "url" is the url that the video was fetched from
-  \item "is\_split\_url" is a boolean that represents if all of the frames of the video have bounding boxes in this metadata
-  \item "start\_i" is the start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
-  \item "end\_i" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
-  \item "bb\_fields" contains all bounding-box specific data. Each entry is a list, where the $i_{th}$ index in each contains the data for one bounding-box:
+  %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
+  \item "\texttt{description}" contains a description of the video as scraped from the video hosting website
+  \item "\texttt{state}" is a string that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
+  \item "\texttt{download\_src}" contains the site that the video was sourced from (e.g. YouTube)
+  \item "\texttt{tags}" is an object that contains custom user-defined tags on videos and additional data that is site specific
+  \item "\texttt{title}" is a string that represents the type of the video
+  \item "\texttt{url}" is the url that the video was fetched from
+  \item "\texttt{is\_split\_url}" is a boolean that represents if all of the frames of the video have bounding boxes in this metadata
+  \item "\texttt{enum\_tags}" is a list of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
+  \item "\texttt{start\_i}" is the start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
+  \item "\texttt{end\_i}" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
+  \item "\texttt{collision\_locations}" a list of frames indicating the collisions
+  \item "\texttt{bb\_fields}" contains all bounding-box specific data. Each entry is a list, where the $i_{th}$ index in each contains the data for one bounding-box:
   \begin{itemize}
-    \item "ids[$i$]" represents what vehicle id the $i_{th}$ bounding box represents. Each vehicle in the video has it's own unique id
-    \item "cls[$i$]" represents the object class of the vehicle
-    \item "frames[$i$]" represents what frame of the video the $i_{th}$ bounding box is for
-    \item "has\_collision[$i$]" represents if the vehicle with id $ids[i]$ is in a collision
-    \item "x1s[$i$], y1s[$i$], x2s[$i$], y2s[$i$]" are the coordinates of the two points $(x_1,y_1)$ \& $(x_2,y_2)$ that make bounding box $i$
+    \item "\texttt{ids[i]}" represents what vehicle id the $i_{th}$ bounding box represents. Each vehicle in the video has it's own unique id
+    \item "\texttt{class[i]}" represents the object class of the vehicle
+    \item "\texttt{frames[i]}" represents what frame of the video the $i_{th}$ bounding box is for
+    \item "\texttt{has\_collision[i]}" represents if the vehicle with id \texttt{ids[i]} is in a collision
+    \item "\texttt{x1s[i], y1s[i], x2s[i], y2s[i]}" are the coordinates of the two points $(x_1,y_1)$ \& $(x_2,y_2)$ that make bounding box i
   \end{itemize}
@@
       "is_split_url": false,
+      "enum_tags": ["CollisionWithRecordingVehicle"],
       "start_i": 0,
       "end_i": 60,
+      "collision_locations": [],
       "bb_fields": {
-        "cls": [],
+        "clss": [],
         "frames": [],
@@
 		\centering
-		% TODO: Uncomment this
-    %\includegraphics[width=0.5\textwidth]{images/example_gui_tool.png}
+    \includegraphics[width=0.5\textwidth]{example_gui_tool.png}
 		\caption{GUI tool to facilitate annotation}
@@
 by introducing negatives from positive labelled videos.
-However, we must be concious to preserve a near 1:1 positives to negatives ratio in our testing set.
+However, we must be conscious to preserve a near 1:1 positives to negatives ratio in our testing set.
 Because of our low turnout, some of the results described below are likely inaccurate and subject to change.
@@
     \end{tikzpicture}
-		\caption{Object by classes in our private database}
+		\caption{Object by classes in our database}
 		\label{fig:obj-by-class}
@@
 %\section{CONCLUSION}
-
+% REMOVED BECAUSE WE DON'T HAVE ANY RESULTS
 %\todo{Write the conclusion}
@@
 We could use this idea to store masking bounds that can be used for training Mask-RCNN networks in (near-)collision contexts.
-This however would be
+
+\item Automated labelling: It would make labelling much faster if we had a (semi-)automated process of detecting objects and tracking them over frames.
+There are models for object detection that behaves reasonably well that we could use, but they would still need to be augmented by a review process.
+For object tracking, there are simple heuristic algorithms that could be used.
 

### 2020-12-03 scripts/make_by-agents.py

@@ -20,6 +20,8 @@ def histogram_by_duration(hist, data):
         if has_collision and id not in viewed_ids:
             viewed_ids.add(id)
             num_agents += 1
+    if 'CollisionWithRecordingVehicle' in data.get('enum_tags', []):
+        num_agents += 1
     hist[num_agents] = hist.get(num_agents, 0) + 1
     return hist
 

### 2020-12-03 paper.tex
Replacing actor with participant

@@
     \begin{axis}[
-      title={Videos by actors},
-      xlabel={Number of actors},
+      title={Videos by participant},
+      xlabel={Number of participants},
       ylabel={Frequency (\# of videos)},

### 2021-03-24 paper.tex
Fixing figure title actor
Few fixes from peer activity.

@@
 By default, our scrapers query using the keywords: \texttt{Car crash dashcam}.
-Currently we support querying Reddit and YouTube, downloading from YouTube and Imgur.
+Currently we support crawling Reddit and YouTube to locate videos that are of interest, and downloading videos hosted on YouTube and Imgur.
 Users that want to pull from a video repository that is not currently implemented should create a custom executor and implement the \texttt{iCrawler} interface.
@@
       "title":"Title of the Video",
-      "url":"http:/www.myvideo.com",
+      "url":"http://www.myvideo.com",
       "is_split_url": false,
@@
     \end{tikzpicture}
-		\caption{Videos by number of actors}
-		\label{fig:vids-by-actors}
+		\caption{Videos by number of participants}
+		\label{fig:vids-by-participant}
 \end{figure}

### 2021-03-27 paper.tex
Added experiments. changed some wording

@@
 
-The international movement towards developing autonomous vehicle technologies has raised concerns in all spheres of civilization: from legal perspectives to ethical dilemmas; from control theory to safety engineering; from cybersecurity to realtime computing.
+The international movement towards developing autonomous vehicle technologies has raised concerns in all spheres of society: from legal perspectives to ethical dilemmas; from control theory to safety engineering; from cybersecurity to realtime computing.
 Over the
@@
 \cite{chan2016anticipating} approach the same problem of collision prediction via egocentric dash-cam videos.
-They propose a novel Dynamic-Spatial-Attention Recurrent Neural Network that distributes attention to localized and tracked vehicles within the video and models temporal dependencies to predict the earliest frame of a potential impending collision.
+They propose a novel Dynamic-Spatial-Attention Recurrent Neural Network (DSARNN) that distributes attention to localized and detected vehicles within the video and models temporal dependencies to predict the earliest frame of a potential impending collision.
 Released with their paper is a dataset of 678 dash-cam videos capturing areas in Taiwan.
@@
 Object tracking bounding boxes can be linearly interpolated from manual start and end points to improve ease of labelling.
-We don't do this???
 We also save the video resolution at which the video was annotated to ensure bounding box annotations can always be scaled to fit any variable download resolutions.
@@
 
-\todo{We are currently still assembling our dataset.
-At the time of this writing, we only have 67 positive videos labelled.
-By using many heuristics like splitting video segments into 5s snippets, we can duplicate our dataset
-by introducing negatives from positive labelled videos.
-However, we must be conscious to preserve a near 1:1 positives to negatives ratio in our testing set.
-Because of our low turnout, some of the results described below are likely inaccurate and subject to change.
-}
+In order to evaluate the importance of acquiring data from multiple geographical locations and under varying driving conditions around the world, we have manually collected a dataset of 223 video clips on which we will test the existing collision anticipation model, DSARNN.
+This dataset is comprised of 97 positive and 126 negative videos.
+Most of these videos represent road scenes from North America, Europe and Russia which have noticeably different characteristics than those in Taiwan.
+To prepare our data we follow the steps outlined by Chan et.
+al \cite{chan2016anticipating}.
+Namely, we trim videos such that they are 5 seconds long sampled at 20fps.
+We trim such that the collision occurs at frame 90, i.e.
+the first 90 frames are used for collision prediction.
+This trimming and sampling functionality is provided within a configuration of our pipeline.
+In our experiments we use the DSARNN model to be trained on features produced by a running a VGG \cite{simonyan2015deep} on each full frame and the cropped objects within the frame and concatenating the output.
+This is denoted VGG+RNN+F+D-con.
+in the original publication.
+We note that this data includes manually annotated bounding boxes, so there will be no error imposed by using automated vehicle detection and localization models.
+
+In our first experiment we merge our dataset with the dataset provided by Chan et.
+al.
+We augment their train set with 77 positives and 106 negatives, and their test set with 20 positives and 20 negatives.
+We use the same training procedure as Chan et.
+al, namely we train for 40 epochs with a learning rate of $10^{-4}$.
+Although our data contribution here is relatively small, we observe a mean time-to-accident of 2.198 at 80\% recall which is very similar to the existing results from Chan et.
+al, however we observe an average precision of 66.22\% which is appreciably lower than the 73.53\% average precision reported by Chan et.
+al.
+
+In our second experiment we use the provided pre-trained DSARNN model and test the performance on our entire dataset of 223 videos.
+We see very poor prediction performance at an average precision of 34.29\%, and in Figure \ref{fig:pr_curve} we observe poor precision at all recall values.
+
+\begin{figure}[htpb]
+		\centering
+		\includegraphics[width=0.4\textwidth]{prcurve.png}
+		\caption{}
+		\label{fig:pr_curve}
+\end{figure}
+
+These experiments seem to support the notion that in order for a collision prediction model to be generally effective in practice, it must be trained on collisions and complex roads scenes from varying regions and road conditions around the world, which is what we hope to achieve with this data collection pipeline.
 
@@
 We have aggregated some statistics about our dataset to help clients understand various distributions in the data.
-While these distributions may be representative of online collision footage, they are not necessarily of real world collisions.
+While these distributions may be representative of online collision footage, they are not necessarily representative of real world collisions.
 

### 2021-03-27 paper.tex
fixed vgg source

@@
 This trimming and sampling functionality is provided within a configuration of our pipeline.
-In our experiments we use the DSARNN model to be trained on features produced by a running a VGG \cite{simonyan2015deep} on each full frame and the cropped objects within the frame and concatenating the output.
+In our experiments we use the DSARNN model to be trained on features produced by a running a VGG \cite{DBLP:journals/corr/SimonyanZ14a} on each full frame and the cropped objects within the frame and concatenating the output.
 This is denoted VGG+RNN+F+D-con.

### 2021-03-27 paper.tex
added batch size
changed wording

@@
 al \cite{chan2016anticipating}.
-Namely, we trim videos such that they are 5 seconds long sampled at 20fps.
-We trim such that the collision occurs at frame 90, i.e.
-the first 90 frames are used for collision prediction.
+Namely, we trim videos such that they are 5 seconds long sampled at 20fps and the collision occurs at frame 90.
 This trimming and sampling functionality is provided within a configuration of our pipeline.
@@
 We use the same training procedure as Chan et.
-al, namely we train for 40 epochs with a learning rate of $10^{-4}$.
+al, namely we train for 40 epochs with a learning rate of $10^{-4}$ and a batch size of 10.
 Although our data contribution here is relatively small, we observe a mean time-to-accident of 2.198 at 80\% recall which is very similar to the existing results from Chan et.

### 2021-03-28 paper.tex
Updated split_url definition
rewording future work

@@
   \item "\texttt{url}" is the url that the video was fetched from
-  \item "\texttt{is\_split\_url}" is a boolean that represents if all of the frames of the video have bounding boxes in this metadata
+  \item "\texttt{is\_split\_url}" is a boolean that is true if all of the frames of the video are covered in this metadata item and false if no
   \item "\texttt{enum\_tags}" is a list of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
@@
 
-There are many ways that we could improve on our system. This are just a series of ideas that we could think of:
+There are many ways that we could improve our system, such as the following:
 \begin{enumerate}

### 2021-03-28 paper.tex
grammatical changes + rewording in experiments section

@@
 
-The international movement towards developing autonomous vehicle technologies has raised concerns in all spheres of society: from legal perspectives to ethical dilemmas; from control theory to safety engineering; from cybersecurity to realtime computing.
+The international movement towards developing autonomous vehicle technologies has raised concerns in many spheres of society: from legal perspectives to ethical dilemmas; from control theory to safety engineering; from cybersecurity to realtime computing.
 Over the
 last decade, some emphasis has been made on the need for these vehicles to reduce road collisions and reckless driving.
-However, research into collision avoidance have been slowed down by the lack of egocentric footage dataset.
-Currently, these types of datasets are most effectively created through computer generated scenarios because of the dangerous and costly nature of road collisions.
+However, research into collision avoidance has been slowed down by the lack of egocentric footage datasets.
+Currently, this types of data is most effectively created through computer generated scenarios due to the dangerous and costly nature of road collisions.
 We provide a pipeline to assemble datasets of real events that have been published online to complement already existing methods.
@@
 al \cite{chan2016anticipating}.
-Namely, we trim videos such that they are 5 seconds long sampled at 20fps and the collision occurs at frame 90.
-This trimming and sampling functionality is provided within a configuration of our pipeline.
-In our experiments we use the DSARNN model to be trained on features produced by a running a VGG \cite{DBLP:journals/corr/SimonyanZ14a} on each full frame and the cropped objects within the frame and concatenating the output.
+Namely, we trim videos such that they are 5 seconds long, sampled at 20 FPS, and the collision occurs at frame 90.
+This trimming and sampling functionality is provided within a configuration of our pipeline, \texttt{smallcorgi\_exporter.yml}.
+In our experiments we train the DSARNN model on features produced by running a pre-trained VGG on each full frame and the cropped objects within the frame \cite{DBLP:journals/corr/SimonyanZ14a}.
 This is denoted VGG+RNN+F+D-con.
@@
 al.
-We augment their train set with 77 positives and 106 negatives, and their test set with 20 positives and 20 negatives.
+We augment their training set with 77 positives and 106 negatives, and their testing set with 20 positives and 20 negatives.
 We use the same training procedure as Chan et.
 al, namely we train for 40 epochs with a learning rate of $10^{-4}$ and a batch size of 10.
-Although our data contribution here is relatively small, we observe a mean time-to-accident of 2.198 at 80\% recall which is very similar to the existing results from Chan et.
-al, however we observe an average precision of 66.22\% which is appreciably lower than the 73.53\% average precision reported by Chan et.
+Although our data contribution here is relatively small, we observe a mean time-to-accident of 2.198s at 80\% recall which is very similar to the existing results from Chan et.
 al.
+However, we observe an average precision of 66.22\% which is appreciably lower than the 73.53\% average precision reported by Chan et.
+al.
+\cite{chan2016anticipating}
 

### 2021-03-28 paper.tex
reword title, add todo regarding AUC in figure

@@
 \title{\LARGE \bf
-A Pipeline to Assemble (Near-)Collision Footage Datasets
+A Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets
 }
@@
 Namely, we trim videos such that they are 5 seconds long, sampled at 20 FPS, and the collision occurs at frame 90.
-This trimming and sampling functionality is provided within a configuration of our pipeline, \texttt{smallcorgi\_exporter.yml}.
+This trimming and sampling functionality is provided within the pipeline configuration \texttt{smallcorgi\_exporter.yml}.
 In our experiments we train the DSARNN model on features produced by running a pre-trained VGG on each full frame and the cropped objects within the frame \cite{DBLP:journals/corr/SimonyanZ14a}.
@@
 		\includegraphics[width=0.4\textwidth]{prcurve.png}
-		\caption{}
+		\caption{\todo{Write caption, fix label (I don't think the term AUC is correct here since this value is actually the average precision from the training code)}}
 		\label{fig:pr_curve}

### 2021-03-28 paper.tex
revive anonymization

@@
 
-% HAS BEEN REMOVED BECAUSE NOT FUNCTIONAL
+%HAS BEEN REMOVED BECAUSE NOT FUNCTIONAL
 %\subsection{Video Preprocessing}
@@
 %\todo{Automated object detection not used right now?}
-%\subsection{Anonymization}
-%An important facet of automobile data aggregation is in eliminating biases and protecting the identities of depicted individuals.
+\subsection{Anonymization}
+An important facet of automobile data aggregation is in eliminating biases and protecting the identities of depicted individuals.
 Consequently, our pipeline contains a post-processing stage in which we apply blurring masks to anonymize any personally identifiable information.
-Specifically, we provide two executors to perform these anonymization tasks: \texttt{FaceBlurrer}, which blurs faces and \texttt{LicensePlateBlurrer} which blurs license plates.
-Both of these executors are powered by pre-trained machine learning models which detect regions containing personally identifiable information.
-Specifically, for  \texttt{FaceBlurrer}, we use a MobileNet Single Shot MultiBox Detector (TODO: cite https://github.com/yeephycho/tensorflow-face-detection) and for \texttt{LicensePlateBlurrer} we use a Convolutional Neural Network (TODO: cite http://sergiomsilva.com/pubs/alpr-unconstrained/).
-%
-%This software module is encapsulated as a library and can be reused by importing our \texttt{anonymization} package as a dependency.
+Specifically, we provide the executor \texttt{FaceBlurrer}, which blurs faces.
+This executor first uses a MobileNet Single Shot MultiBox Detector \cite{yixuan_h_y_hu_2021_4642275} trained on the WIDERFACE dataset \cite{yang2016wider} to obtain the bounding boxes of all visibly identifiable individuals' faces at each frame of a given video and then applies a blurring mask over each bounding box.
+
+This software module is encapsulated as a library and can be reused by importing our \texttt{anonymization} package.
 The accuracy, amount and type of blurring applied can be tweaked using the API exposed by the \texttt{anonymization} package.

### 2021-03-28 paper.tex
some more grammatical fixes

@@
 However, research into collision avoidance has been slowed down by the lack of egocentric footage datasets.
-Currently, this types of data is most effectively created through computer generated scenarios due to the dangerous and costly nature of road collisions.
+Currently, this type of data is most effectively created through computer generated scenarios due to the dangerous and costly nature of road collisions.
 We provide a pipeline to assemble datasets of real events that have been published online to complement already existing methods.
-Our aggregated dataset includes egocentric vehicle footage from all over the world: varying visibilities, varying weather conditions, and varying settings.
+Futher, we present an aggregated dataset that we have produced using our pipeline which includes egocentric vehicle footage from all over the world subject to varying visibilities, varying weather conditions, and varying settings.
 
@@
 Technologies such as Radar, LIDAR and high-end cameras that are typically used for collision prediction are likely too expensive for most consumers.
-On the other hand dash-cams, cheap video cameras that can be mounted to a car's dashboard, have become increasingly affordable and prevalent as a means to capture a driver’s perspective.
+On the other hand, dash-cams, which are cheap video cameras that can be mounted to a car's dashboard, have become increasingly affordable and prevalent as a means to capture a driver’s perspective.
 Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that wouldn't be feasible to simulate. 
-This has led to the creation of many online communities to share videos of these rare situations on websites such as Reddit, Youtube, and Imgur.
+This has led to the creation of many online communities to share videos of these rare situations on websites such as Reddit, YouTube, and Imgur.
 We propose that this egocentric dash-cam video stream can be leveraged by computer vision systems to act as an affordable and commonplace sensor for automated collision prediction.
@@
 \item Automated labelling: It would make labelling much faster if we had a (semi-)automated process of detecting objects and tracking them over frames.
-There are models for object detection that behaves reasonably well that we could use, but they would still need to be augmented by a review process.
+There are models for object detection that behave reasonably well which we could use, but they would still need to be augmented by a review process.
 For object tracking, there are simple heuristic algorithms that could be used.

### 2021-03-28 scripts/count_bbs.py
new count script

@@ -3,6 +3,7 @@ import firebase_admin as fb
 from firebase_admin import credentials, db
 from firebase_admin.db import Reference
 from functools import reduce
+from pprint import pprint
 
 FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
 
@@ -10,9 +11,26 @@ def count_bbs(count, data):
     (key, data) = data
     if data.get('is_cancelled', True):
         return count
-    if 'bb_fields' not in data:
-       return count
-    return count + 1
+    if 'bb_fields' in data and len(data['bb_fields']) > 0:
+        count.update({ 'total': count.get('total', 0) + 1 })
+        if 'collision_locations' in data['bb_fields'] and len(data['bb_fields']['collision_locations']) > 0:
+            count.update({ 'collision': count.get('collision', 0) + 1 })
+            if (data.get('url'), data.get('start_i')) in count.get('seen', set()):
+                count['duplicated'].add((data.get('url'), data.get('start_i')))
+            count['seen'].add((data['url'], data.get('start_i')))
+        if 'accident_locations' in data['bb_fields'] and len(data['bb_fields']['accident_locations']) > 0:
+            count.update({ 'nested_accident': count.get('nested_accident', 0) + 1 })
+            if (data.get('url'), data.get('start_i')) in count.get('seen', set()):
+                count['duplicated'].add((data.get('url'), data.get('start_i')))
+            count['seen'].add((data.get('url'), data.get('start_i')))
+    if 'accident_locations' in data and len(data['accident_locations']) > 0:
+        count.update({ 'accident': count.get('accident', 0) + 1 })
+        if (data.get('url'), data.get('start_i')) in count.get('seen', set()):
+            count['duplicated'].add((data.get('url'), data.get('start_i')))
+        count['seen'].add((data['url'], data.get('start_i')))
+    if not data.get('url'):
+        count.update({ 'no_url': count.get('no_url', set()) + data.id })
+    return count
 
 if __name__ == '__main__':
     cred = credentials.Certificate(FIREBASE_CRED_FILENAME)
@@ -27,6 +45,7 @@ if __name__ == '__main__':
     metadata = db.reference('metadata')
     print('Retrieved data')
     data = [ val for val in metadata.get().items() ]
-    count = reduce(count_bbs, data, 0)
-    print(count)
+    count = reduce(count_bbs, data, { 'seen':set(), 'duplicated': set() })
+    del count['seen']
+    pprint(count)
 

### 2021-03-28 paper.tex
update metadata section and add sources

@@
 
-The international movement towards developing autonomous vehicle technologies has raised concerns in many spheres of society: from legal perspectives to ethical dilemmas; from control theory to safety engineering; from cybersecurity to realtime computing.
+The international movement towards developing autonomous vehicle technologies has raised concerns in many spheres of society: from legal perspectives \cite{Pattinson2020} to ethical dilemmas; from control theory to safety engineering; from cybersecurity to realtime computing.
 Over the
@@
   \item "\texttt{end\_i}" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
-  \item "\texttt{collision\_locations}" a list of frames indicating the collisions
-  \item "\texttt{bb\_fields}" contains all bounding-box specific data. Each entry is a list, where the $i_{th}$ index in each contains the data for one bounding-box:
+  \item "\texttt{bb\_fields}" contains all bounding-box specific data.
   \begin{itemize}
-    \item "\texttt{ids[i]}" represents what vehicle id the $i_{th}$ bounding box represents. Each vehicle in the video has it's own unique id
-    \item "\texttt{class[i]}" represents the object class of the vehicle
-    \item "\texttt{frames[i]}" represents what frame of the video the $i_{th}$ bounding box is for
-    \item "\texttt{has\_collision[i]}" represents if the vehicle with id \texttt{ids[i]} is in a collision
-    \item "\texttt{x1s[i], y1s[i], x2s[i], y2s[i]}" are the coordinates of the two points $(x_1,y_1)$ \& $(x_2,y_2)$ that make bounding box i
+    \item "\texttt{collision\_locations}" a list of frame numbers indicating the collision start frames
+    \item "\texttt{resolution}" A list with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
+    \item "\texttt{objects}" Is a list of all of the bounding boxes for each object in the video.
+An object being either a vehicle or pedestrian.
+Within each object, there is metadata specific to that object.
+    \begin{itemize}
+      \item "\texttt{id}" Is a  unique numerical identifier that represents this object
+      \item "\texttt{bboxes}" Is a list of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
+      \item "\texttt{class}" Represents the class of the object, and will be one of "car", "truck", "motorcycle", "van", "pedestrian", "bus"
+      \item "\texttt{has\_collision}" Is a boolean that is true if the object is in a collision, false otherwise
+    \end{itemize}
   \end{itemize}
@@
 {
-      "collision_type":"",
   "description":"",
-      "download_src":"",
+  "download_src":"YouTube",
   "tags": {
@@
   "is_split_url": false,
-      "enum_tags": ["CollisionWithRecordingVehicle"],
+  "enum_tags": ["NoCollision"],
   "start_i": 0,
   "end_i": 60,
+  "bb_fields": {
     "collision_locations": [],
-      "bb_fields": {
-        "clss": [],
-        "frames": [],
-        "has_collision": [],
-        "ids": [],
-        "x1s": [],
-        "y1s": [],
-        "x2s": [],
-        "y2s": [],
+    "objects": [
+      {
+        "bboxes": [
+          [0, 1096, 377, 1279, 634]
+        ],
+        "class": "car",
+        "has_collision": false,
+        "id": "1"
+      }
+    ],
+    "resolution": [1280, 720]
   }

### 2021-03-28 paper.tex
reword the intro to focus less on cost of sensors

@@
 
-In the advent of connected vehicles and autonomous transportation, equipping consumer vehicles with the necessary equipment to facilitate high-end automated collision avoidance systems can be prohibitively expensive.
-Technologies such as Radar, LIDAR and high-end cameras that are typically used for collision prediction are likely too expensive for most consumers.
-On the other hand, dash-cams, which are cheap video cameras that can be mounted to a car's dashboard, have become increasingly affordable and prevalent as a means to capture a driver’s perspective.
+In the advent of connected vehicles and autonomous transportation, it has become commonplace to equip vehicles with the necessary equipment to facilitate high-end automated collision avoidance systems.
+Using these vehicles to simulate collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.
+However, we can collect collision data naturally in real driving scenarios through the use of dash-cams - cheap video cameras that can be mounted to a car's dashboard.
 Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that wouldn't be feasible to simulate. 

### 2021-03-29 paper.tex
citation on computer generated data

@@
 However, research into collision avoidance has been slowed down by the lack of egocentric footage datasets.
-Currently, this type of data is most effectively created through computer generated scenarios due to the dangerous and costly nature of road collisions.
+Currently, this type of data is created through computer generated scenarios \cite{Kim_Lee_Hwang_Suh_2019} due to the dangerous and costly nature of road collisions.
 We provide a pipeline to assemble datasets of real events that have been published online to complement already existing methods.
@@
   \end{itemize}
-\end{itemize}`
+\end{itemize}
 

### 2021-03-29 paper.tex
consistent dashcam and accident verbage

@@
 Using these vehicles to simulate collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.
-However, we can collect collision data naturally in real driving scenarios through the use of dash-cams - cheap video cameras that can be mounted to a car's dashboard.
-Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that wouldn't be feasible to simulate. 
+However, we can collect collision data naturally in real driving scenarios through the use of dashcams - cheap video cameras that can be mounted to a car's dashboard.
+Typically used for insurance purposes, dashcams have the added benefit of recording a wide variety of collisions that wouldn't be feasible to simulate. 
 This has led to the creation of many online communities to share videos of these rare situations on websites such as Reddit, YouTube, and Imgur.
-We propose that this egocentric dash-cam video stream can be leveraged by computer vision systems to act as an affordable and commonplace sensor for automated collision prediction.
+We propose that this egocentric dashcam video stream can be leveraged by computer vision systems to act as an affordable and commonplace sensor for automated collision prediction.
 
-In this paper we present a software pipeline to facilitate the collection, processing and annotation of egocentric dash-cam videos from various online video repositories to produce datasets that can be used to train deep dash-cam collision prediction models.
+In this paper we present a software pipeline to facilitate the collection, processing and annotation of egocentric dashcam videos from various online video repositories to produce datasets that can be used to train deep dashcam collision prediction models.
 We aim to generate datasets that are not constrained to any regions or countries but rather provide location-agnostic data that is representative of general, global road and vehicle conditions.
@@
 Chan et al.
-\cite{chan2016anticipating} approach the same problem of collision prediction via egocentric dash-cam videos.
+\cite{chan2016anticipating} approach the same problem of collision prediction via egocentric dashcam videos.
 They propose a novel Dynamic-Spatial-Attention Recurrent Neural Network (DSARNN) that distributes attention to localized and detected vehicles within the video and models temporal dependencies to predict the earliest frame of a potential impending collision.
-Released with their paper is a dataset of 678 dash-cam videos capturing areas in Taiwan.
+Released with their paper is a dataset of 678 dashcam videos capturing areas in Taiwan.
 Each video is annotated with vehicle tracking bounding boxes, the vehicles that were involved in the collision and the frame of the collision.
@@
 
-In addition to collection and preprocessing, a core component of our pipeline is a GUI tool that facilitates the manual annotation of the dash-cam videos, and quick manual filtering of non-dashcam and irrelevant videos.
+In addition to collection and preprocessing, a core component of our pipeline is a GUI tool that facilitates the manual annotation of the dashcam videos, and quick manual filtering of non-dashcam and irrelevant videos.
 Following Chan et al.\cite{chan2016anticipating}, if a collision occurs we provide tools to annotate the frame the collision occurs, and bounding boxes to localize, identify and track agents in the video segment.
@@
 al, namely we train for 40 epochs with a learning rate of $10^{-4}$ and a batch size of 10.
-Although our data contribution here is relatively small, we observe a mean time-to-accident of 2.198s at 80\% recall which is very similar to the existing results from Chan et.
+Although our data contribution here is relatively small, we observe a mean time-to-collision of 2.198s at 80\% recall which is very similar to the existing results from Chan et.
 al.
@@
 \item Web interface: Having a web-based user interface would be advantageous for this project.
-While currently being used in the context of (near-)collision accident, this software has the potential to become a platform for scraping automation and collaboration.
+While currently being used in the context of (near-)collision, this software has the potential to become a platform for scraping automation and collaboration.
 Ideally, people without a technical background would be able to contribute to the microtasking involved, and technical contributors would be in charge of creating and managing the automation and general design of the pipeline.

### 2021-03-29 paper.tex
remove partial list of classes
consistent wording of metadata

@@
   \item "\texttt{end\_i}" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
-  \item "\texttt{bb\_fields}" contains all bounding-box specific data.
+  \item "\texttt{bb\_fields}" contains all bounding-box specific data
   \begin{itemize}
-    \item "\texttt{collision\_locations}" a list of frame numbers indicating the collision start frames
-    \item "\texttt{resolution}" A list with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
-    \item "\texttt{objects}" Is a list of all of the bounding boxes for each object in the video.
+    \item "\texttt{collision\_locations}" is a list of frame numbers indicating the collision start frames
+    \item "\texttt{resolution}" is a list with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
+    \item "\texttt{objects}" is a list of all of the bounding boxes for each object in the video.
 An object being either a vehicle or pedestrian.
@@
     \begin{itemize}
-      \item "\texttt{id}" Is a  unique numerical identifier that represents this object
-      \item "\texttt{bboxes}" Is a list of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
-      \item "\texttt{class}" Represents the class of the object, and will be one of "car", "truck", "motorcycle", "van", "pedestrian", "bus"
-      \item "\texttt{has\_collision}" Is a boolean that is true if the object is in a collision, false otherwise
+      \item "\texttt{id}" is a  unique numerical identifier that represents this object
+      \item "\texttt{bboxes}" is a list of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
+      \item "\texttt{class}" represents the class of the object, such as "car", "pedestrian"
+      \item "\texttt{has\_collision}" is a boolean that is true if the object is in a collision, false otherwise
     \end{itemize}

### 2021-03-29 paper.tex
add source for lidar

@@
 
-In the advent of connected vehicles and autonomous transportation, it has become commonplace to equip vehicles with the necessary equipment to facilitate high-end automated collision avoidance systems.
+In the advent of connected vehicles and autonomous transportation, it has become commonplace to equip vehicles with the necessary equipment to facilitate high-end automated collision avoidance systems \cite{Perumal2020LidarBI}.
 Using these vehicles to simulate collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.

### 2021-03-29 paper.tex
Minor changes. With mmerge. Again

@@
          Curtis Duy Kha Phan, Jack David Roberts Williamson,\\
-         Nicholas Geofroy, Tony Meng, Vincent-Olivier Roch\\
+         Nicholas Geofroy, Chengzhong Meng, Vincent-Olivier Roch\\
          University of Waterloo\\
@@
 As part of this data, we identify participants and bystanders, both known as agents.
-Participants are objects that are involved in a collision identified in the metadata, while bystanders are objects that are not.
+Participants are objects that are involved in a collision identified in the metadata, while bystanders are uninvolved objects.
 
@@
   %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
-  \item "\texttt{description}" contains a description of the video as scraped from the video hosting website
-  \item "\texttt{state}" is a string that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
-  \item "\texttt{download\_src}" contains the site that the video was sourced from (e.g. YouTube)
-  \item "\texttt{tags}" is an object that contains custom user-defined tags on videos and additional data that is site specific
-  \item "\texttt{title}" is a string that represents the type of the video
-  \item "\texttt{url}" is the url that the video was fetched from
-  \item "\texttt{is\_split\_url}" is a boolean that is true if all of the frames of the video are covered in this metadata item and false if no
-  \item "\texttt{enum\_tags}" is a list of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
-  \item "\texttt{start\_i}" is the start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
-  \item "\texttt{end\_i}" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
-  \item "\texttt{bb\_fields}" contains all bounding-box specific data
+  \item "\texttt{description}": Description of the video as scraped from the video hosting website
+  \item "\texttt{state}": String that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
+  \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
+  \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site specific
+  \item "\texttt{title}": String that represents the type of the video
+  \item "\texttt{url}": Url that the video was fetched from
+  \item "\texttt{is\_split\_url}": Boolean that is true if all of the frames of the video are covered in this metadata item and false if no
+  \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
+  \item "\texttt{start\_i}": The start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
+  \item "\texttt{end\_i}": The end frame of the video the bounding boxes are created for (if is\_split\_url is true)
+  \item "\texttt{bb\_fields}": All bounding-box specific data
   \begin{itemize}
-    \item "\texttt{collision\_locations}" is a list of frame numbers indicating the collision start frames
-    \item "\texttt{resolution}" is a list with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
-    \item "\texttt{objects}" is a list of all of the bounding boxes for each object in the video.
+    \item "\texttt{collision\_locations}": List of frame numbers indicating the collision start frames
+    \item "\texttt{resolution}": List with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
+    \item "\texttt{objects}": List of all of the bounding boxes for each object in the video.
 An object being either a vehicle or pedestrian.
@@
     \begin{itemize}
-      \item "\texttt{id}" is a  unique numerical identifier that represents this object
-      \item "\texttt{bboxes}" is a list of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
-      \item "\texttt{class}" represents the class of the object, such as "car", "pedestrian"
-      \item "\texttt{has\_collision}" is a boolean that is true if the object is in a collision, false otherwise
+      \item "\texttt{id}": Unique numerical identifier that represents this object
+      \item "\texttt{bboxes}": List of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
+      \item "\texttt{class}": The class of the object, such as "car", "pedestrian"
+      \item "\texttt{has\_collision}": Boolean that is true if the object is in a collision, false otherwise
     \end{itemize}

### 2021-03-29 paper.tex
Updates from Overleaf

--- 2021-03-29 paper.tex
@@
 However, research into collision avoidance has been slowed down by the lack of egocentric footage datasets.
-Currently, this type of data is created through computer generated scenarios \cite{Kim_Lee_Hwang_Suh_2019} due to the dangerous and costly nature of road collisions.
+Currently, this type of data is most effectively created through computer generated scenarios due to the dangerous and costly nature of road collisions.
 We provide a pipeline to assemble datasets of real events that have been published online to complement already existing methods.
@@
 Using these vehicles to simulate collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.
-However, we can collect collision data naturally in real driving scenarios through the use of dashcams - cheap video cameras that can be mounted to a car's dashboard.
-Typically used for insurance purposes, dashcams have the added benefit of recording a wide variety of collisions that wouldn't be feasible to simulate. 
+However, we can collect collision data naturally in real driving scenarios through the use of dash-cams - cheap video cameras that can be mounted to a car's dashboard.
+Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that wouldn't be feasible to simulate. 
 This has led to the creation of many online communities to share videos of these rare situations on websites such as Reddit, YouTube, and Imgur.
-We propose that this egocentric dashcam video stream can be leveraged by computer vision systems to act as an affordable and commonplace sensor for automated collision prediction.
+We propose that this egocentric dash-cam video stream can be leveraged by computer vision systems to act as an affordable and commonplace sensor for automated collision prediction.
 
-In this paper we present a software pipeline to facilitate the collection, processing and annotation of egocentric dashcam videos from various online video repositories to produce datasets that can be used to train deep dashcam collision prediction models.
+In this paper we present a software pipeline to facilitate the collection, processing and annotation of egocentric dash-cam videos from various online video repositories to produce datasets that can be used to train deep dash-cam collision prediction models.
 We aim to generate datasets that are not constrained to any regions or countries but rather provide location-agnostic data that is representative of general, global road and vehicle conditions.
@@
 Chan et al.
-\cite{chan2016anticipating} approach the same problem of collision prediction via egocentric dashcam videos.
+\cite{chan2016anticipating} approach the same problem of collision prediction via egocentric dash-cam videos.
 They propose a novel Dynamic-Spatial-Attention Recurrent Neural Network (DSARNN) that distributes attention to localized and detected vehicles within the video and models temporal dependencies to predict the earliest frame of a potential impending collision.
-Released with their paper is a dataset of 678 dashcam videos capturing areas in Taiwan.
+Released with their paper is a dataset of 678 dash-cam videos capturing areas in Taiwan.
 Each video is annotated with vehicle tracking bounding boxes, the vehicles that were involved in the collision and the frame of the collision.
@@
 
-In addition to collection and preprocessing, a core component of our pipeline is a GUI tool that facilitates the manual annotation of the dashcam videos, and quick manual filtering of non-dashcam and irrelevant videos.
+In addition to collection and preprocessing, a core component of our pipeline is a GUI tool that facilitates the manual annotation of the dash-cam videos, and quick manual filtering of non-dashcam and irrelevant videos.
 Following Chan et al.\cite{chan2016anticipating}, if a collision occurs we provide tools to annotate the frame the collision occurs, and bounding boxes to localize, identify and track agents in the video segment.
@@
   \item "\texttt{end\_i}" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
-  \item "\texttt{bb\_fields}" contains all bounding-box specific data
+  \item "\texttt{bb\_fields}" contains all bounding-box specific data.
   \begin{itemize}
-    \item "\texttt{collision\_locations}" is a list of frame numbers indicating the collision start frames
-    \item "\texttt{resolution}" is a list with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
-    \item "\texttt{objects}" is a list of all of the bounding boxes for each object in the video.
+    \item "\texttt{collision\_locations}" a list of frame numbers indicating the collision start frames
+    \item "\texttt{resolution}" A list with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
+    \item "\texttt{objects}" Is a list of all of the bounding boxes for each object in the video.
 An object being either a vehicle or pedestrian.
@@
     \begin{itemize}
-      \item "\texttt{id}" is a  unique numerical identifier that represents this object
-      \item "\texttt{bboxes}" is a list of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
-      \item "\texttt{class}" represents the class of the object, such as "car", "pedestrian"
-      \item "\texttt{has\_collision}" is a boolean that is true if the object is in a collision, false otherwise
+      \item "\texttt{id}" Is a  unique numerical identifier that represents this object
+      \item "\texttt{bboxes}" Is a list of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
+      \item "\texttt{class}" Represents the class of the object, and will be one of "car", "truck", "motorcycle", "van", "pedestrian", "bus"
+      \item "\texttt{has\_collision}" Is a boolean that is true if the object is in a collision, false otherwise
     \end{itemize}
@@
 al, namely we train for 40 epochs with a learning rate of $10^{-4}$ and a batch size of 10.
-Although our data contribution here is relatively small, we observe a mean time-to-collision of 2.198s at 80\% recall which is very similar to the existing results from Chan et.
+Although our data contribution here is relatively small, we observe a mean time-to-accident of 2.198s at 80\% recall which is very similar to the existing results from Chan et.
 al.
@@
 \begin{enumerate}
-\item Custom interpolation between input frames: One idea would be to make it easier to modify the method of interpolation between frames.
-Currently, linear interpolation is always used.
+\item Labelling precision improvements: The current video-labelling process in the pipeline, manual bounding box drawing with linear interpolation between input frames, is prone to inserting mistaken bounding boxes that don't exactly match to the location of an object on certain frames.
+Automated labelling and custom interpolation would speed up the process of labelling and minimize the cases of misplaced bounding boxes.
+Labelling would be much faster if we had a (semi-)automated process of detecting objects and tracking them over frames.
+There are models for object detection that behave reasonably well which we could use, but they would still need to be augmented by a review process.
+For object tracking, there are simple heuristic algorithms that could be used.
+Being able to modify the method of interpolation between frames beyond the default linear interpolation would allow for more bounding box precision between large input frame windows.
 Moreover, given a type of interpolation is stored in the metadata, we probably shouldn't store all interpolated frames, rather than just the ones the user has entered.
@@
 
-\item Polyhedral bounds: It's always possible to represent a 2-dimensional polyhedron with a matrix $A\in\mathbb{R}^{n\times 2}$, and a vector $b\in\mathbb{R}^2$, given that the polyhedron can be represented by the set $\left\{x\mid Ax\leq b\right\}$.
-We could use this idea to store masking bounds that can be used for training Mask-RCNN networks in (near-)collision contexts.
-
-\item Automated labelling: It would make labelling much faster if we had a (semi-)automated process of detecting objects and tracking them over frames.
-There are models for object detection that behave reasonably well which we could use, but they would still need to be augmented by a review process.
-For object tracking, there are simple heuristic algorithms that could be used.
-
-\item Web interface: Having a web-based user interface would be advantageous for this project.
-While currently being used in the context of (near-)collision, this software has the potential to become a platform for scraping automation and collaboration.
-Ideally, people without a technical background would be able to contribute to the microtasking involved, and technical contributors would be in charge of creating and managing the automation and general design of the pipeline.
+\item Complete Location-Varied Dataset: Our next step is to enlarge our existing dataset of car collisions from regions all over the world, which would then use solely to form a training set and testing set for our next experiment.
+We could then compare the results of this experiment with location-varied data to the results from the dataset collected in Taiwan by Chan et.
+al.
 

### 2021-03-29 paper.tex
Revised abstract and changed wording in intro

@@
 
-The international movement towards developing autonomous vehicle technologies has raised concerns in many spheres of society: from legal perspectives \cite{Pattinson2020} to ethical dilemmas; from control theory to safety engineering; from cybersecurity to realtime computing.
-Over the
-last decade, some emphasis has been made on the need for these vehicles to reduce road collisions and reckless driving.
-However, research into collision avoidance has been slowed down by the lack of egocentric footage datasets.
-Currently, this type of data is most effectively created through computer generated scenarios due to the dangerous and costly nature of road collisions.
-We provide a pipeline to assemble datasets of real events that have been published online to complement already existing methods.
-Futher, we present an aggregated dataset that we have produced using our pipeline which includes egocentric vehicle footage from all over the world subject to varying visibilities, varying weather conditions, and varying settings.
+Over the last decade, emphasis has been made on the need for autonomous vehicles to reduce road collisions and reckless driving.
+However, research into collision prediction has been slowed by the lack of egocentric collision-oriented datasets.
+Currently, this type of data is often created through computer generated scenarios due to the dangerous and costly nature of road collisions and data collection equipment.
+We provide a pipeline to assemble datasets of real vehicle collision events that have been published online to various video repositories.
+We specifically focus on collecting collisions recorded from front-mounted dashcam video cameras and demonstrate the importance of learning from complex road scenes and conditions globally rather than in one region.
+Further, we present a small prototype dataset that we have produced using our pipeline which includes egocentric dashcam vehicle footage from all over the world subject to varying visibilities, varying weather conditions, and varying settings.
 
@@
 
-In the advent of connected vehicles and autonomous transportation, it has become commonplace to equip vehicles with the necessary equipment to facilitate high-end automated collision avoidance systems.
-Using these vehicles to simulate collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.
-However, we can collect collision data naturally in real driving scenarios through the use of dash-cams - cheap video cameras that can be mounted to a car's dashboard.
-Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that wouldn't be feasible to simulate. 
+In the advent of connected vehicles and autonomous transportation, it has become commonplace to equip vehicles with high-end equipment to facilitate automated collision avoidance systems.
+Using these vehicles to record collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.
+However, we can collect collision data naturally in real driving scenarios through dash-cams -- cheap video cameras that can be mounted to a car's dashboard.
+Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that might not be effectively simulated. 
 This has led to the creation of many online communities to share videos of these rare situations on websites such as Reddit, YouTube, and Imgur.
@@
 \begin{enumerate}
-\item Labelling precision improvements: The current video-labelling process in the pipeline, manual bounding box drawing with linear interpolation between input frames, is prone to inserting mistaken bounding boxes that don't exactly match to the location of an object on certain frames.
-Automated labelling and custom interpolation would speed up the process of labelling and minimize the cases of misplaced bounding boxes.
-Labelling would be much faster if we had a (semi-)automated process of detecting objects and tracking them over frames.
-There are models for object detection that behave reasonably well which we could use, but they would still need to be augmented by a review process.
-For object tracking, there are simple heuristic algorithms that could be used.
-Being able to modify the method of interpolation between frames beyond the default linear interpolation would allow for more bounding box precision between large input frame windows.
+\item Custom interpolation between input frames: One idea would be to make it easier to modify the method of interpolation between frames.
+Currently, linear interpolation is always used.
 Moreover, given a type of interpolation is stored in the metadata, we probably shouldn't store all interpolated frames, rather than just the ones the user has entered.
@@
 
-\item Complete Location-Varied Dataset: Our next step is to enlarge our existing dataset of car collisions from regions all over the world, which would then use solely to form a training set and testing set for our next experiment.
-We could then compare the results of this experiment with location-varied data to the results from the dataset collected in Taiwan by Chan et.
-al.
+\item Polyhedral bounds: It's always possible to represent a 2-dimensional polyhedron with a matrix $A\in\mathbb{R}^{n\times 2}$, and a vector $b\in\mathbb{R}^2$, given that the polyhedron can be represented by the set $\left\{x\mid Ax\leq b\right\}$.
+We could use this idea to store masking bounds that can be used for training Mask-RCNN networks in (near-)collision contexts.
+
+\item Automated labelling: It would make labelling much faster if we had a (semi-)automated process of detecting objects and tracking them over frames.
+There are models for object detection that behave reasonably well which we could use, but they would still need to be augmented by a review process.
+For object tracking, there are simple heuristic algorithms that could be used.
+
+\item Web interface: Having a web-based user interface would be advantageous for this project.
+While currently being used in the context of (near-)collision accident, this software has the potential to become a platform for scraping automation and collaboration.
+Ideally, people without a technical background would be able to contribute to the microtasking involved, and technical contributors would be in charge of creating and managing the automation and general design of the pipeline.
 

### 2021-03-29 paper.tex
merged

@@
 
-The international movement towards developing autonomous vehicle technologies has raised concerns in many spheres of society: from legal perspectives \cite{Pattinson2020} to ethical dilemmas; from control theory to safety engineering; from cybersecurity to realtime computing.
-Over the
-last decade, some emphasis has been made on the need for these vehicles to reduce road collisions and reckless driving.
-However, research into collision avoidance has been slowed down by the lack of egocentric footage datasets.
-Currently, this type of data is created through computer generated scenarios \cite{Kim_Lee_Hwang_Suh_2019} due to the dangerous and costly nature of road collisions.
-We provide a pipeline to assemble datasets of real events that have been published online to complement already existing methods.
-Futher, we present an aggregated dataset that we have produced using our pipeline which includes egocentric vehicle footage from all over the world subject to varying visibilities, varying weather conditions, and varying settings.
+Over the last decade, emphasis has been made on the need for autonomous vehicles to reduce road collisions and reckless driving.
+However, research into collision prediction has been slowed by the lack of egocentric collision-oriented datasets.
+Currently, this type of data is often created through computer generated scenarios due to the dangerous and costly nature of road collisions and data collection equipment.
+We provide a pipeline to assemble datasets of real vehicle collision events that have been published online to various video repositories.
+We specifically focus on collecting collisions recorded from front-mounted dashcam video cameras and demonstrate the importance of learning from complex road scenes and conditions globally rather than in one region.
+Further, we present a small prototype dataset that we have produced using our pipeline which includes egocentric dashcam vehicle footage from all over the world subject to varying visibilities, varying weather conditions, and varying settings.
 
@@
 
-In the advent of connected vehicles and autonomous transportation, it has become commonplace to equip vehicles with the necessary equipment to facilitate high-end automated collision avoidance systems \cite{Perumal2020LidarBI}.
-Using these vehicles to simulate collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.
-However, we can collect collision data naturally in real driving scenarios through the use of dashcams - cheap video cameras that can be mounted to a car's dashboard.
-Typically used for insurance purposes, dashcams have the added benefit of recording a wide variety of collisions that wouldn't be feasible to simulate. 
+In the advent of connected vehicles and autonomous transportation, it has become commonplace to equip vehicles with high-end equipment to facilitate automated collision avoidance systems.
+Using these vehicles to record collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.
+However, we can collect collision data naturally in real driving scenarios through dash-cams -- cheap video cameras that can be mounted to a car's dashboard.
+Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that might not be effectively simulated. 
 This has led to the creation of many online communities to share videos of these rare situations on websites such as Reddit, YouTube, and Imgur.
@@
 
-\item Complete Location-Varied Dataset: Our next step is to enlarge our existing dataset of car collisions from regions all over the world, which would then use solely to form a training set and testing set for our next experiment.
-We could then compare the results of this experiment with location-varied data to the results from the dataset collected in Taiwan by Chan et.
-al.
+\item Polyhedral bounds: It's always possible to represent a 2-dimensional polyhedron with a matrix $A\in\mathbb{R}^{n\times 2}$, and a vector $b\in\mathbb{R}^2$, given that the polyhedron can be represented by the set $\left\{x\mid Ax\leq b\right\}$.
+We could use this idea to store masking bounds that can be used for training Mask-RCNN networks in (near-)collision contexts.
+
+\item Automated labelling: It would make labelling much faster if we had a (semi-)automated process of detecting objects and tracking them over frames.
+There are models for object detection that behave reasonably well which we could use, but they would still need to be augmented by a review process.
+For object tracking, there are simple heuristic algorithms that could be used.
+
+\item Web interface: Having a web-based user interface would be advantageous for this project.
+While currently being used in the context of (near-)collision, this software has the potential to become a platform for scraping automation and collaboration.
+Ideally, people without a technical background would be able to contribute to the microtasking involved, and technical contributors would be in charge of creating and managing the automation and general design of the pipeline.
 

### 2021-03-29 paper.tex
minor wording

@@
 However, we can collect collision data naturally in real driving scenarios through dash-cams -- cheap video cameras that can be mounted to a car's dashboard.
-Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that might not be effectively simulated. 
+Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of real collisions that might not be effectively simulated. 
 This has led to the creation of many online communities to share videos of these rare situations on websites such as Reddit, YouTube, and Imgur.

### 2021-03-29 paper.tex
added abstract citation and removed dashcam hyphen

--- 2021-03-29 paper.tex
@@
 However, research into collision prediction has been slowed by the lack of egocentric collision-oriented datasets.
-Currently, this type of data is often created through computer generated scenarios due to the dangerous and costly nature of road collisions and data collection equipment.
+Currently, this type of data is often created through computer generated scenarios \cite{Kim_Lee_Hwang_Suh_2019} due to the dangerous and costly nature of road collisions and data collection equipment.
 We provide a pipeline to assemble datasets of real vehicle collision events that have been published online to various video repositories.
@@
 Using these vehicles to record collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.
-However, we can collect collision data naturally in real driving scenarios through dash-cams -- cheap video cameras that can be mounted to a car's dashboard.
-Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that might not be effectively simulated. 
+However, we can collect collision data naturally in real driving scenarios through dashcams -- cheap video cameras that can be mounted to a car's dashboard.
+Typically used for insurance purposes, dashcams have the added benefit of recording a wide variety of real collisions that might not be effectively simulated. 
 This has led to the creation of many online communities to share videos of these rare situations on websites such as Reddit, YouTube, and Imgur.

### 2021-03-29 paper.tex
update anonymization

--- 2021-03-29 paper.tex
@@
          Curtis Duy Kha Phan, Jack David Roberts Williamson,\\
-         Nicholas Geofroy, Chengzhong Meng, Vincent-Olivier Roch\\
+         Nicholas Geofroy, Tony Meng, Vincent-Olivier Roch\\
          University of Waterloo\\
@@
 
-Over the last decade, emphasis has been made on the need for autonomous vehicles to reduce road collisions and reckless driving.
-However, research into collision prediction has been slowed by the lack of egocentric collision-oriented datasets.
-Currently, this type of data is often created through computer generated scenarios due to the dangerous and costly nature of road collisions and data collection equipment.
-We provide a pipeline to assemble datasets of real vehicle collision events that have been published online to various video repositories.
-We specifically focus on collecting collisions recorded from front-mounted dashcam video cameras and demonstrate the importance of learning from complex road scenes and conditions globally rather than in one region.
-Further, we present a small prototype dataset that we have produced using our pipeline which includes egocentric dashcam vehicle footage from all over the world subject to varying visibilities, varying weather conditions, and varying settings.
+The international movement towards developing autonomous vehicle technologies has raised concerns in many spheres of society: from legal perspectives \cite{Pattinson2020} to ethical dilemmas; from control theory to safety engineering; from cybersecurity to realtime computing.
+Over the
+last decade, some emphasis has been made on the need for these vehicles to reduce road collisions and reckless driving.
+However, research into collision avoidance has been slowed down by the lack of egocentric footage datasets.
+Currently, this type of data is most effectively created through computer generated scenarios due to the dangerous and costly nature of road collisions.
+We provide a pipeline to assemble datasets of real events that have been published online to complement already existing methods.
+Futher, we present an aggregated dataset that we have produced using our pipeline which includes egocentric vehicle footage from all over the world subject to varying visibilities, varying weather conditions, and varying settings.
 
@@
 
-In the advent of connected vehicles and autonomous transportation, it has become commonplace to equip vehicles with high-end equipment to facilitate automated collision avoidance systems.
-Using these vehicles to record collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.
-However, we can collect collision data naturally in real driving scenarios through dash-cams -- cheap video cameras that can be mounted to a car's dashboard.
-Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that might not be effectively simulated. 
+In the advent of connected vehicles and autonomous transportation, it has become commonplace to equip vehicles with the necessary equipment to facilitate high-end automated collision avoidance systems.
+Using these vehicles to simulate collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.
+However, we can collect collision data naturally in real driving scenarios through the use of dash-cams - cheap video cameras that can be mounted to a car's dashboard.
+Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that wouldn't be feasible to simulate. 
 This has led to the creation of many online communities to share videos of these rare situations on websites such as Reddit, YouTube, and Imgur.
-We propose that this egocentric dashcam video stream can be leveraged by computer vision systems to act as an affordable and commonplace sensor for automated collision prediction.
+We propose that this egocentric dash-cam video stream can be leveraged by computer vision systems to act as an affordable and commonplace sensor for automated collision prediction.
 
-In this paper we present a software pipeline to facilitate the collection, processing and annotation of egocentric dashcam videos from various online video repositories to produce datasets that can be used to train deep dashcam collision prediction models.
+In this paper we present a software pipeline to facilitate the collection, processing and annotation of egocentric dash-cam videos from various online video repositories to produce datasets that can be used to train deep dash-cam collision prediction models.
 We aim to generate datasets that are not constrained to any regions or countries but rather provide location-agnostic data that is representative of general, global road and vehicle conditions.
@@
 As part of this data, we identify participants and bystanders, both known as agents.
-Participants are objects that are involved in a collision identified in the metadata, while bystanders are uninvolved objects.
+Participants are objects that are involved in a collision identified in the metadata, while bystanders are objects that are not.
 
@@
 This executor first uses a MobileNet Single Shot MultiBox Detector \cite{yixuan_h_y_hu_2021_4642275} trained on the WIDERFACE dataset \cite{yang2016wider} to obtain the bounding boxes of all visibly identifiable individuals' faces at each frame of a given video and then applies a blurring mask over each bounding box.
+We have chosen to use a MobileNet SSD for this task because it achieves a good balance between accuracy and performance, while requiring relatively little memory \cite{yixuan_h_y_hu_2021_4642275}.
 
@@
   %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
-  \item "\texttt{description}": Description of the video as scraped from the video hosting website
-  \item "\texttt{state}": String that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
-  \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
-  \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site specific
-  \item "\texttt{title}": String that represents the type of the video
-  \item "\texttt{url}": Url that the video was fetched from
-  \item "\texttt{is\_split\_url}": Boolean that is true if all of the frames of the video are covered in this metadata item and false if no
-  \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
-  \item "\texttt{start\_i}": The start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
-  \item "\texttt{end\_i}": The end frame of the video the bounding boxes are created for (if is\_split\_url is true)
-  \item "\texttt{bb\_fields}": All bounding-box specific data
+  \item "\texttt{description}" contains a description of the video as scraped from the video hosting website
+  \item "\texttt{state}" is a string that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
+  \item "\texttt{download\_src}" contains the site that the video was sourced from (e.g. YouTube)
+  \item "\texttt{tags}" is an object that contains custom user-defined tags on videos and additional data that is site specific
+  \item "\texttt{title}" is a string that represents the type of the video
+  \item "\texttt{url}" is the url that the video was fetched from
+  \item "\texttt{is\_split\_url}" is a boolean that is true if all of the frames of the video are covered in this metadata item and false if no
+  \item "\texttt{enum\_tags}" is a list of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
+  \item "\texttt{start\_i}" is the start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
+  \item "\texttt{end\_i}" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
+  \item "\texttt{bb\_fields}" contains all bounding-box specific data.
   \begin{itemize}
-    \item "\texttt{collision\_locations}": List of frame numbers indicating the collision start frames
-    \item "\texttt{resolution}": List with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
-    \item "\texttt{objects}": List of all of the bounding boxes for each object in the video.
+    \item "\texttt{collision\_locations}" a list of frame numbers indicating the collision start frames
+    \item "\texttt{resolution}" A list with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
+    \item "\texttt{objects}" Is a list of all of the bounding boxes for each object in the video.
 An object being either a vehicle or pedestrian.
@@
     \begin{itemize}
-      \item "\texttt{id}": Unique numerical identifier that represents this object
-      \item "\texttt{bboxes}": List of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
-      \item "\texttt{class}": The class of the object, such as "car", "pedestrian"
-      \item "\texttt{has\_collision}": Boolean that is true if the object is in a collision, false otherwise
+      \item "\texttt{id}" Is a  unique numerical identifier that represents this object
+      \item "\texttt{bboxes}" Is a list of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
+      \item "\texttt{class}" Represents the class of the object, and will be one of "car", "truck", "motorcycle", "van", "pedestrian", "bus"
+      \item "\texttt{has\_collision}" Is a boolean that is true if the object is in a collision, false otherwise
     \end{itemize}
   \end{itemize}
-\end{itemize}
+\end{itemize}`
 
@@
 \item Web interface: Having a web-based user interface would be advantageous for this project.
-While currently being used in the context of (near-)collision, this software has the potential to become a platform for scraping automation and collaboration.
+While currently being used in the context of (near-)collision accident, this software has the potential to become a platform for scraping automation and collaboration.
 Ideally, people without a technical background would be able to contribute to the microtasking involved, and technical contributors would be in charge of creating and managing the automation and general design of the pipeline.

### 2021-03-29 paper.tex

--- 2021-03-29 paper.tex
@@
 
-Over the last decade, emphasis has been made on the need for autonomous vehicles to reduce road collisions and reckless driving.
-However, research into collision prediction has been slowed by the lack of egocentric collision-oriented datasets.
-Currently, this type of data is often created through computer generated scenarios due to the dangerous and costly nature of road collisions and data collection equipment.
-We provide a pipeline to assemble datasets of real vehicle collision events that have been published online to various video repositories.
-We specifically focus on collecting collisions recorded from front-mounted dashcam video cameras and demonstrate the importance of learning from complex road scenes and conditions globally rather than in one region.
-Further, we present a small prototype dataset that we have produced using our pipeline which includes egocentric dashcam vehicle footage from all over the world subject to varying visibilities, varying weather conditions, and varying settings.
+The international movement towards developing autonomous vehicle technologies has raised concerns in many spheres of society: from legal perspectives \cite{Pattinson2020} to ethical dilemmas; from control theory to safety engineering; from cybersecurity to realtime computing.
+Over the
+last decade, some emphasis has been made on the need for these vehicles to reduce road collisions and reckless driving.
+However, research into collision avoidance has been slowed down by the lack of egocentric footage datasets.
+Currently, this type of data is created through computer generated scenarios \cite{Kim_Lee_Hwang_Suh_2019} due to the dangerous and costly nature of road collisions.
+We provide a pipeline to assemble datasets of real events that have been published online to complement already existing methods.
+Futher, we present an aggregated dataset that we have produced using our pipeline which includes egocentric vehicle footage from all over the world subject to varying visibilities, varying weather conditions, and varying settings.
 
@@
 
-In the advent of connected vehicles and autonomous transportation, it has become commonplace to equip vehicles with high-end equipment to facilitate automated collision avoidance systems.
-Using these vehicles to record collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.
-However, we can collect collision data naturally in real driving scenarios through dash-cams -- cheap video cameras that can be mounted to a car's dashboard.
-Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of real collisions that might not be effectively simulated. 
+In the advent of connected vehicles and autonomous transportation, it has become commonplace to equip vehicles with the necessary equipment to facilitate high-end automated collision avoidance systems \cite{Perumal2020LidarBI}.
+Using these vehicles to simulate collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.
+However, we can collect collision data naturally in real driving scenarios through the use of dashcams - cheap video cameras that can be mounted to a car's dashboard.
+Typically used for insurance purposes, dashcams have the added benefit of recording a wide variety of collisions that wouldn't be feasible to simulate. 
 This has led to the creation of many online communities to share videos of these rare situations on websites such as Reddit, YouTube, and Imgur.

### 2021-03-29 scripts/make_by-actors.py
Fixing by actor

@@ -10,9 +10,9 @@ def histogram_by_duration(hist, data):
     (key, data) = data
     if data.get('is_cancelled', True):
         return hist
-    if 'bb_fields' not in data or 'ids' not in data['bb_fields']:
+    if 'bb_fields' not in data:
        return hist
-    num_actors = len(set(data.get('bb_fields', {}).get('ids', [])))
+    num_actors = len(set([ obj.get('id') for obj in data['bb_fields'].get('objects', []) ]))
     hist[num_actors] = hist.get(num_actors, 0) + 1
     return hist
 

### 2021-03-29 scripts/make_by-agents.py
Fixed by agent script

@@ -10,15 +10,13 @@ def histogram_by_duration(hist, data):
     (key, data) = data
     if data.get('is_cancelled', True):
         return hist
-    if 'bb_fields' not in data or 'ids' not in data['bb_fields']:
+    if 'bb_fields' not in data:
        return hist
     num_agents = 0
     viewed_ids = set()
-    ids = data.get('bb_fields', {}).get('ids')
-    collisions = data.get('bb_fields', {}).get('has_collision')
-    for id, has_collision in zip(ids, collisions):
-        if has_collision and id not in viewed_ids:
-            viewed_ids.add(id)
+    for obj in data['bb_fields'].get('objects', []):
+        if obj['has_collision'] and obj['id'] not in viewed_ids:
+            viewed_ids.add(obj['id'])
             num_agents += 1
     if 'CollisionWithRecordingVehicle' in data.get('enum_tags', []):
         num_agents += 1

### 2021-03-29 scripts/make_by-classes.py
Fixed by class script

@@ -10,13 +10,13 @@ def histogram_by_class(hist, data):
     (key, data) = data
     if data.get('is_cancelled', True):
         return hist
+    if 'bb_fields' not in data:
+        return hist
     viewed_ids = set()
-    clss = data.get('bb_fields', {}).get('clss', [])
-    ids = data.get('bb_fields', {}).get('ids', [])
-    for cls, id in zip(clss, ids):
-        if id not in viewed_ids:
-            viewed_ids.add(id)
-            hist[cls] = hist.get(cls, 0) + 1
+    for obj in data['bb_fields'].get('objects', []):
+        if obj['id'] not in viewed_ids:
+            viewed_ids.add(obj['id'])
+            hist[obj['class']] = hist.get(obj['class'], 0) + 1
     return hist
 
 if __name__ == '__main__':

### 2021-03-29 scripts/make_by-duration.py
Fixed by duration script

@@ -31,6 +31,7 @@ if __name__ == '__main__':
     print('Retrieved data')
     data = [ val for val in metadata.get().items() ]
     hist = reduce(histogram_by_duration, data, [])
+    print(hist)
     hist, bins = np.histogram(hist, bins=10)
     """
     if float('inf') in hist:

### 2021-03-29 paper.tex
Addressed comments in pr #10

--- 2021-03-29 paper.tex
@@
 We specifically focus on collecting collisions recorded from front-mounted dashcam video cameras and demonstrate the importance of learning from complex road scenes and conditions globally rather than in one region.
-Further, we present a small prototype dataset that we have produced using our pipeline which includes egocentric dashcam vehicle footage from all over the world subject to varying visibilities, varying weather conditions, and varying settings.
+Further, we present a small prototype dataset that we have produced using our pipeline which includes egocentric dashcam vehicle footage from all over the world, subject to varying visibilities, varying weather conditions, and varying settings.
 
@@
 
-In the advent of connected vehicles and autonomous transportation, it has become commonplace to equip vehicles with high-end equipment to facilitate automated collision avoidance systems.
+In the advent of connected vehicles and autonomous transportation, it has become commonplace to equip vehicles with high-end equipment to facilitate automated collision avoidance systems \cite{Perumal2020LidarBI}.
 Using these vehicles to record collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.

### 2021-03-29 paper.tex
Updated all graphs

--- 2021-03-29 paper.tex
@@
 \usepackage{listings, xcolor}
+
+\pgfplotsset{compat=1.3}
 
@@
 
-Over the last decade, emphasis has been made on the need for autonomous vehicles to reduce road collisions and reckless driving.
-However, research into collision prediction has been slowed by the lack of egocentric collision-oriented datasets.
-Currently, this type of data is often created through computer generated scenarios \cite{Kim_Lee_Hwang_Suh_2019} due to the dangerous and costly nature of road collisions and data collection equipment.
-We provide a pipeline to assemble datasets of real vehicle collision events that have been published online to various video repositories.
-We specifically focus on collecting collisions recorded from front-mounted dashcam video cameras and demonstrate the importance of learning from complex road scenes and conditions globally rather than in one region.
-Further, we present a small prototype dataset that we have produced using our pipeline which includes egocentric dashcam vehicle footage from all over the world, subject to varying visibilities, varying weather conditions, and varying settings.
+The international movement towards developing autonomous vehicle technologies has raised concerns in many spheres of society: from legal perspectives to ethical dilemmas; from control theory to safety engineering; from cybersecurity to realtime computing.
+Over the
+last decade, some emphasis has been made on the need for these vehicles to reduce road collisions and reckless driving.
+However, research into collision avoidance has been slowed down by the lack of egocentric footage datasets.
+Currently, this type of data is most effectively created through computer generated scenarios due to the dangerous and costly nature of road collisions.
+We provide a pipeline to assemble datasets of real events that have been published online to complement already existing methods.
+Futher, we present an aggregated dataset that we have produced using our pipeline which includes egocentric vehicle footage from all over the world subject to varying visibilities, varying weather conditions, and varying settings.
 
@@
 
-In the advent of connected vehicles and autonomous transportation, it has become commonplace to equip vehicles with high-end equipment to facilitate automated collision avoidance systems \cite{Perumal2020LidarBI}.
-Using these vehicles to record collision situations has a two-fold cost: both the car and expensive data-gathering equipment are put at risk.
-However, we can collect collision data naturally in real driving scenarios through dashcams -- cheap video cameras that can be mounted to a car's dashboard.
-Typically used for insurance purposes, dashcams have the added benefit of recording a wide variety of real collisions that might not be effectively simulated. 
+In the advent of connected vehicles and autonomous transportation, equipping consumer vehicles with the necessary equipment to facilitate high-end automated collision avoidance systems can be prohibitively expensive.
+Technologies such as Radar, LIDAR and high-end cameras that are typically used for collision prediction are likely too expensive for most consumers.
+On the other hand, dash-cams, which are cheap video cameras that can be mounted to a car's dashboard, have become increasingly affordable and prevalent as a means to capture a driver’s perspective.
+Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that wouldn't be feasible to simulate. 
 This has led to the creation of many online communities to share videos of these rare situations on websites such as Reddit, YouTube, and Imgur.
-We propose that this egocentric dashcam video stream can be leveraged by computer vision systems to act as an affordable and commonplace sensor for automated collision prediction.
+We propose that this egocentric dash-cam video stream can be leveraged by computer vision systems to act as an affordable and commonplace sensor for automated collision prediction.
 
-In this paper we present a software pipeline to facilitate the collection, processing and annotation of egocentric dashcam videos from various online video repositories to produce datasets that can be used to train deep dashcam collision prediction models.
+In this paper we present a software pipeline to facilitate the collection, processing and annotation of egocentric dash-cam videos from various online video repositories to produce datasets that can be used to train deep dash-cam collision prediction models.
 We aim to generate datasets that are not constrained to any regions or countries but rather provide location-agnostic data that is representative of general, global road and vehicle conditions.
@@
   %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
-  \item "\texttt{description}": Description of the video as scraped from the video hosting website
-  \item "\texttt{state}": String that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
-  \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
-  \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site specific
-  \item "\texttt{title}": String that represents the type of the video
-  \item "\texttt{url}": Url that the video was fetched from
-  \item "\texttt{is\_split\_url}": Boolean that is true if all of the frames of the video are covered in this metadata item and false if no
-  \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
-  \item "\texttt{start\_i}": The start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
-  \item "\texttt{end\_i}": The end frame of the video the bounding boxes are created for (if is\_split\_url is true)
-  \item "\texttt{bb\_fields}": All bounding-box specific data
+  \item "\texttt{description}" contains a description of the video as scraped from the video hosting website
+  \item "\texttt{state}" is a string that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
+  \item "\texttt{download\_src}" contains the site that the video was sourced from (e.g. YouTube)
+  \item "\texttt{tags}" is an object that contains custom user-defined tags on videos and additional data that is site specific
+  \item "\texttt{title}" is a string that represents the type of the video
+  \item "\texttt{url}" is the url that the video was fetched from
+  \item "\texttt{is\_split\_url}" is a boolean that is true if all of the frames of the video are covered in this metadata item and false if no
+  \item "\texttt{enum\_tags}" is a list of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
+  \item "\texttt{start\_i}" is the start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
+  \item "\texttt{end\_i}" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
+  \item "\texttt{collision\_locations}" a list of frames indicating the collisions
+  \item "\texttt{bb\_fields}" contains all bounding-box specific data. Each entry is a list, where the $i_{th}$ index in each contains the data for one bounding-box:
   \begin{itemize}
-    \item "\texttt{collision\_locations}": List of frame numbers indicating the collision start frames
-    \item "\texttt{resolution}": List with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
-    \item "\texttt{objects}": List of all of the bounding boxes for each object in the video.
-An object being either a vehicle or pedestrian.
-Within each object, there is metadata specific to that object.
-    \begin{itemize}
-      \item "\texttt{id}": Unique numerical identifier that represents this object
-      \item "\texttt{bboxes}": List of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
-      \item "\texttt{class}": The class of the object, such as "car", "pedestrian"
-      \item "\texttt{has\_collision}": Boolean that is true if the object is in a collision, false otherwise
+    \item "\texttt{ids[i]}" represents what vehicle id the $i_{th}$ bounding box represents. Each vehicle in the video has it's own unique id
+    \item "\texttt{class[i]}" represents the object class of the vehicle
+    \item "\texttt{frames[i]}" represents what frame of the video the $i_{th}$ bounding box is for
+    \item "\texttt{has\_collision[i]}" represents if the vehicle with id \texttt{ids[i]} is in a collision
+    \item "\texttt{x1s[i], y1s[i], x2s[i], y2s[i]}" are the coordinates of the two points $(x_1,y_1)$ \& $(x_2,y_2)$ that make bounding box i
   \end{itemize}
-  \end{itemize}
-\end{itemize}
+\end{itemize}`
 
@@
     {
+      "collision_type":"",
       "description":"",
-  "download_src":"YouTube",
+      "download_src":"",
       "tags": {
@@
       "is_split_url": false,
-  "enum_tags": ["NoCollision"],
+      "enum_tags": ["CollisionWithRecordingVehicle"],
       "start_i": 0,
       "end_i": 60,
+      "collision_locations": [],
       "bb_fields": {
-    "collision_locations": [],
-    "objects": [
-      {
-        "bboxes": [
-          [0, 1096, 377, 1279, 634]
-        ],
-        "class": "car",
-        "has_collision": false,
-        "id": "1"
-      }
-    ],
-    "resolution": [1280, 720]
+        "clss": [],
+        "frames": [],
+        "has_collision": [],
+        "ids": [],
+        "x1s": [],
+        "y1s": [],
+        "x2s": [],
+        "y2s": [],
       }
@@
       xtick=data,
-      xticklabels from table={\byactors}{X}
+      xticklabels from table={\byactors}{X},
+      xticklabel style={rotate=90}
     ]
@@
       xtick=data,
-      xticklabels from table={\byduration}{X}
+      xticklabels from table={\byduration}{X},
+      xticklabel style={rotate=90}
     ]

### 2021-03-29 scripts/make_by-actors.py

@@ -30,9 +30,8 @@ if __name__ == '__main__':
     print('Retrieved data')
     data = [ val for val in metadata.get().items() ]
     hist = reduce(histogram_by_duration, data, {})
-    print(hist)
-    dtype = [ ('X', object), ('Y', np.uint32) ]
-    Z = np.array([ *hist.items() ], dtype=dtype)
-    Z = np.sort(Z, axis=0)
+    hist, bins = np.histogram([ *hist.keys() ], weights=[ *hist.values() ])
+    dtype = [ ('X', np.uint32), ('Y', np.uint32) ]
+    Z = np.array([ *zip(bins, hist) ], dtype=dtype)
     np.savetxt('by-actors.csv', Z, delimiter=',', fmt=['%s', '%d'], header='X,Y', comments='')
 

### 2021-03-29 scripts/make_by-classes.py

@@ -33,6 +33,8 @@ if __name__ == '__main__':
     print('Retrieved data')
     data = [ val for val in metadata.get().items() ]
     hist = reduce(histogram_by_class, data, {})
+    del hist['NONE']
+    del hist['test']
     print(hist)
     dtype = [ ('X', object), ('Y', np.uint32) ]
     Z = np.array([ *hist.items() ], dtype=dtype)

### 2021-03-29 scripts/make_by-duration.py

@@ -32,7 +32,7 @@ if __name__ == '__main__':
     data = [ val for val in metadata.get().items() ]
     hist = reduce(histogram_by_duration, data, [])
     print(hist)
-    hist, bins = np.histogram(hist, bins=10)
+    hist, bins = np.histogram(hist, bins=10, range=(65, 1500))
     """
     if float('inf') in hist:
         hist['Unknown'] = hist[float('inf')]

### 2021-03-30 paper.tex
Added pr curve caption
sort class histogram by desc freq; grouped stationary/non-vehicular objects into "other"; various wording/grammar/conciseness improvements

@@
 An important facet of automobile data aggregation is in eliminating biases and protecting the identities of depicted individuals.
-Consequently, our pipeline contains a post-processing stage in which we apply blurring masks to anonymize any personally identifiable information.
+Consequently, our pipeline contains a post-processing stage in which we anonymize personally identifiable information.
 Specifically, we provide the executor \texttt{FaceBlurrer}, which blurs faces.
-This executor first uses a MobileNet Single Shot MultiBox Detector \cite{yixuan_h_y_hu_2021_4642275} trained on the WIDERFACE dataset \cite{yang2016wider} to obtain the bounding boxes of all visibly identifiable individuals' faces at each frame of a given video and then applies a blurring mask over each bounding box.
+This executor first uses a MobileNet Single Shot MultiBox Detector \cite{yixuan_h_y_hu_2021_4642275} trained on the WIDERFACE dataset \cite{yang2016wider} to obtain the bounding boxes of all visibly identifiable individuals' faces at each frame of a given video, and then applies a blurring mask over each bounding box.
 We have chosen to use a MobileNet SSD for this task because it achieves a good balance between accuracy and performance, while requiring relatively little memory \cite{yixuan_h_y_hu_2021_4642275}.
@@
 		\includegraphics[width=0.4\textwidth]{prcurve.png}
-		\caption{\todo{Write caption, fix label (I don't think the term AUC is correct here since this value is actually the average precision from the training code)}}
+		\caption{Pre-trained DSARNN Precision-Recall curve on prototype dataset}
 		\label{fig:pr_curve}
@@
     \end{tikzpicture}
-		\caption{Object by classes in our database}
+		\caption{Objects grouped by class}
 		\label{fig:obj-by-class}
@@
     \end{tikzpicture}
-		\caption{Videos by number of participants}
+		\caption{Videos grouped by number of participants}
 		\label{fig:vids-by-participant}
@@
     \end{tikzpicture}
-		\caption{Videos by number of agents}
+		\caption{Videos grouped by number of agents}
 		\label{fig:vids-by-agents}
@@
     \end{tikzpicture}
-		\caption{Videos by duration}
+		\caption{Videos grouped by duration}
 		\label{fig:vids-by-duration}
@@
 
+\todo{Explain the "other" category in the class histogram. These are stationary/non-vehicular objects.}
+\todo{Add a paragraph explaining the key characteristics of Figures 5-10.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Automated labelling and custom interpolation would speed up the process of labelling and minimize the cases of misplaced bounding boxes.
-Labelling would be much faster if we had a (semi-)automated process of detecting objects and tracking them over frames.
+Labelling would be much faster if we had a semi-automated process of detecting objects and tracking them over frames.
 There are models for object detection that behave reasonably well which we could use, but they would still need to be augmented by a review process.

### 2021-03-30 scripts/make_by-classes.py

@@ -5,6 +5,9 @@ from firebase_admin.db import Reference
 from functools import reduce
 
 FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
+RELEVANT_CLASSES = ['car', 'bus', 'truck', 'van', 'motorcycle', 'train', 'streetcar', 'pedestrian', 'bicycle', 'animal']
+NOOP_CLASSES = ['NONE', 'test']
+OTHER_CLASS = 'other'
 
 def histogram_by_class(hist, data):
     (key, data) = data
@@ -16,7 +19,11 @@ def histogram_by_class(hist, data):
     for obj in data['bb_fields'].get('objects', []):
         if obj['id'] not in viewed_ids:
             viewed_ids.add(obj['id'])
-            hist[obj['class']] = hist.get(obj['class'], 0) + 1
+            obj_class = obj['class']
+            if obj_class in RELEVANT_CLASSES + NOOP_CLASSES:
+                hist[obj_class] = hist.get(obj_class, 0) + 1
+            else:
+                hist[OTHER_CLASS] = hist.get(OTHER_CLASS, 0) + 1 
     return hist
 
 if __name__ == '__main__':
@@ -35,8 +42,13 @@ if __name__ == '__main__':
     hist = reduce(histogram_by_class, data, {})
     del hist['NONE']
     del hist['test']
-    print(hist)
+    other = hist[OTHER_CLASS]
+    del hist[OTHER_CLASS]
+    items = [ *hist.items() ]
+    items.sort(key=lambda x:x[1], reverse=True)
+    items.append((OTHER_CLASS, other))
+    print(items)
     dtype = [ ('X', object), ('Y', np.uint32) ]
-    Z = np.array([ *hist.items() ], dtype=dtype)
+    Z = np.array(items, dtype=dtype)
     np.savetxt('by-classes.csv', Z, delimiter=',', fmt=['%s', '%d'], header='X,Y', comments='')
 

### 2021-03-30 paper.tex
add important TODOs

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo{Overall TODO: fix awkward sentences, grammatical issues }
 \begin{abstract}
@@
 We aim to generate datasets that are not constrained to any regions or countries but rather provide location-agnostic data that is representative of general, global road and vehicle conditions.
+\todo{Backup this claim with the location histogram, perhaps in the experiment section.
+If we put it there, we should reference it from here.}
 These datasets will also be collision-oriented as the majority of these videos contain collisions for people's viewing.
@@
 This is the data we hope to capture by taking advantage of existing videos of non-artificial collisions.
+\todo{Add sentence explaining we don't care about video resolution as long as collisions and agents are clear in the video.
+Further support this by the fact that we aren't using the final dense classification layer in the VGG, which in turns allows us to use videos of any resolution.
+}
 
@@
 
-The software pipeline is built of multiple executors that each process or handle the data corresponding to a single video before piping the resulting data to the next executor.
+The software pipeline is built from several modular components called executors that each process or handle the data corresponding to a single video before piping the resulting data to the next executor.
 

### 2021-03-31 paper.tex
switched to document class and bib style templates required by ITSC conference

@@
-\documentclass[letterpaper, 10 pt, conference]{IEEEconf}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%2345678901234567890123456789012345678901234567890123456789012345678901234567890
+%        1         2         3         4         5         6         7         8
+
+\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
+\overrideIEEEmargins												% Needed to meet printer requirements.
 \usepackage[utf8]{inputenc}
 \usepackage[T1]{fontenc}
-\usepackage[style=ieee]{biblatex}
 \usepackage{tikz}
@@
 
-\bibliography{sources}
 \begin{document}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo{Overall TODO: fix awkward sentences, grammatical issues }
+\todo{Overall TODO: fix awkward sentences, grammatical issues. }
 \begin{abstract}
@@
 The software pipeline is built from several modular components called executors that each process or handle the data corresponding to a single video before piping the resulting data to the next executor.
+Figure \ref{fig:pr_curve} illustrates the organization of the pipeline in its default configuration.
 
@@
             },
-        module/.default=2cm,
+        module/.default=1cm,
         >=LaTeX
@@
     \end{tikzpicture}
-		\caption{Architecture of the default pipeline}
-		\label{fig:obj-by-class}
+		\caption{Architecture of the pipeline in its default configuration. Each node in the diagram represents a stage of the pipeline, consisting of a single executor or series of executors.}
+		\label{fig:pipeline-architecture}
 \end{figure}
@@
   %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
-  \item "\texttt{description}": Description of the video as scraped from the video hosting website
+  \item "\texttt{}": Description of the video as scraped from the video hosting website
   \item "\texttt{state}": String that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
@@
 \begin{figure}
-  \begin{lstlisting}[language=json]
+  \begin{lstlisting}[language=json,xleftmargin=5mm]
 {
@@
   \end{lstlisting}
-    \caption{Example Metadata Produced by the Pipeline}
+    \caption{Example metadata produced by the pipeline}
     \label{metadata_example}
@@
     \end{tikzpicture}
-		\caption{Objects grouped by class}
+		\caption{Videos in dataset grouped by object class}
 		\label{fig:obj-by-class}
@@
     \end{tikzpicture}
-		\caption{Videos grouped by number of participants}
+		\caption{Videos in dataset grouped by number of participants}
 		\label{fig:vids-by-participant}
@@
     \end{tikzpicture}
-		\caption{Videos grouped by number of agents}
+		\caption{Videos in dataset grouped by number of agents}
 		\label{fig:vids-by-agents}
@@
     \end{tikzpicture}
-		\caption{Videos grouped by duration}
+		\caption{Videos in dataset grouped by duration}
 		\label{fig:vids-by-duration}
@@
     \includegraphics[width=3in]{by-collision.png}
-		\caption{Videos by collision}
+		\caption{All videos in database grouped by collision type}
 		\label{fig:vids-by-collision}
@@
     \includegraphics[width=3in]{by-camera.png}
-		\caption{Videos by camera}
+		\caption{All videos in database grouped by camera type}
 		\label{fig:vids-by-camera}
@@
 
+\todo{Organize figures better, crop out excess whitespace, resize them and place them within the column of the page.}
 \todo{Explain the "other" category in the class histogram. These are stationary/non-vehicular objects.}
-\todo{Add a paragraph explaining the key characteristics of Figures 5-10.}
+\todo{Explain the distinctions between the different types of collisions in the collision chart.}
+\todo{Add chart showing videos by source (Figure 11).}
+\todo{Move Figures 5-11 to Methodology - Video Collection.}
+\todo{Reduce caption size for each figure.}
+\todo{Add a paragraph explaining the key characteristics of Figures 5-11.}
 
@@
 \nocite{*}
-\printbibliography
+\bibliographystyle{IEEEtran}
+\bibliography{sources}
 

### 2021-03-31 scripts/make_by-camera.py

@@ -6,6 +6,9 @@ from functools import reduce
 from matplotlib import pyplot as plt
 
 FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
+STATIONARY_CAMERA_LABEL= "Stationary Camera"
+MANHELD_CAMERA_LABEL= "Manheld Camera"
+DASHCAM_LABEL= "Dashcam"
 
 def pie_by_camera(hist, data):
     (key, data) = data
@@ -13,11 +16,11 @@ def pie_by_camera(hist, data):
         return hist
     enum_tags = data['enum_tags']
     if 'StationaryCamera' in enum_tags:
-        hist.update({ 'StationaryCamera': hist.get('StationaryCamera', 0) + 1 })
+        hist.update({ STATIONARY_CAMERA_LABEL: hist.get(STATIONARY_CAMERA_LABEL, 0) + 1 })
     elif 'ManHeldCamera' in enum_tags:
-        hist.update({ 'ManHeldCamera': hist.get('ManHeldCamera', 0) + 1 })
+        hist.update({ MANHELD_CAMERA_LABEL: hist.get(MANHELD_CAMERA_LABEL, 0) + 1 })
     else:
-        hist.update({ 'DashCamera': hist.get('DashCamera', 0) + 1 })
+        hist.update({ DASHCAM_LABEL: hist.get(DASHCAM_LABEL, 0) + 1 })
 
     return hist
 
@@ -37,4 +40,5 @@ if __name__ == '__main__':
     pie = reduce(pie_by_camera, data, {})
     fig, ax = plt.subplots()
     ax.pie(pie.values(), labels=pie.keys(), autopct='%1.1f%%')
+    fig.tight_layout()
     fig.savefig('by-camera.png')

### 2021-03-31 scripts/make_by-collision.py

@@ -6,6 +6,9 @@ from functools import reduce
 from matplotlib import pyplot as plt
 
 FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
+NO_COLLISION_LABEL = "No Collision"
+MULTI_COLLISION_LABEL = "Multi Collision"
+SIMPLE_COLLISION_LABEL = "Simple Collision"
 
 def pie_by_collision(hist, data):
     (key, data) = data
@@ -13,11 +16,11 @@ def pie_by_collision(hist, data):
         return hist
     enum_tags = data['enum_tags']
     if 'MultiCollision' in enum_tags:
-        hist.update({ 'MultiCollision': hist.get('MultiCollision', 0) + 1 })
+        hist.update({ MULTI_COLLISION_LABEL: hist.get(MULTI_COLLISION_LABEL, 0) + 1 })
     elif 'NoCollision' in enum_tags:
-        hist.update({ 'NoCollision': hist.get('NoCollision', 0) + 1 })
+        hist.update({ NO_COLLISION_LABEL: hist.get(NO_COLLISION_LABEL, 0) + 1 })
     else:
-        hist.update({ 'SimpleCollision': hist.get('SimpleCollision', 0) + 1 })
+        hist.update({ SIMPLE_COLLISION_LABEL : hist.get(SIMPLE_COLLISION_LABEL, 0) + 1 })
 
     return hist
 
@@ -37,4 +40,5 @@ if __name__ == '__main__':
     pie = reduce(pie_by_collision, data, {})
     fig, ax = plt.subplots()
     ax.pie(pie.values(), labels=pie.keys(), autopct='%1.1f%%')
+    fig.tight_layout()
     fig.savefig('by-collision.png')

### 2021-03-31 paper.tex
utilize IEEEAbrv as recommended by IEEE style guide
adjust header

@@
          Nicholas Geofroy, Chengzhong Meng, Vincent-Olivier Roch\\
-         University of Waterloo\\
          \\
+         Faculties of Mathematics and Engineering, University of Waterloo\\
          \tt\small ben.upenieks@uwaterloo.ca, cvarier@uwaterloo.ca,
@@
 \bibliographystyle{IEEEtran}
-\bibliography{sources}
+\bibliography{IEEEabrv,sources}
 

### 2021-03-31 paper.tex
node spacing in architecture diagram

@@
     \tikzset{
+    	node distance = 6m and 0cm,
         module/.style={%
@@
       \node[module, below=of labeller] (uploader) {Data-Uploader};
-      \draw[->] (crawler)--(downloader);
-      \draw[->] (downloader)--(splitter);
-      \draw[->] (splitter)--(labeller);
-      \draw[->] (labeller)--(uploader);
+      \draw[->] (crawler) -- (downloader);
+      \draw[->] (downloader) -- (splitter);
+      \draw[->] (splitter) -- (labeller);
+      \draw[->] (labeller) -- (uploader);
 

### 2021-03-31 paper.tex
cropped and styled pie charts

@@
 \usetikzlibrary{positioning,fit,arrows.meta,backgrounds}
+\usepackage{graphicx}
 \usepackage{amsmath, amssymb, xcolor, tikz, pgfplots, pgfplotstable}
@@
     \tikzset{
-    	node distance = 6m and 0cm,
+    	node distance = 6mm and 0cm,
         module/.style={%
@@
 		\centering
-    \includegraphics[width=3in]{by-collision.png}
+    \includegraphics[width=3in,trim={0 1cm 0 1cm},clip]{by-collision.png}
 		\caption{All videos in database grouped by collision type}
@@
 		\centering
-    \includegraphics[width=3in]{by-camera.png}
+    \includegraphics[width=3in,trim={0 1cm 0 1cm},clip]{by-camera.png}
 		\caption{All videos in database grouped by camera type}

### 2021-03-31 scripts/make_by-camera.py

@@ -6,8 +6,8 @@ from functools import reduce
 from matplotlib import pyplot as plt
 
 FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
-STATIONARY_CAMERA_LABEL= "Stationary Camera"
-MANHELD_CAMERA_LABEL= "Manheld Camera"
+STATIONARY_CAMERA_LABEL= "Stationary\ Camera"
+MANHELD_CAMERA_LABEL= "Manheld\ Camera"
 DASHCAM_LABEL= "Dashcam"
 
 def pie_by_camera(hist, data):
@@ -39,6 +39,12 @@ if __name__ == '__main__':
     data = [ val for val in metadata.get().items() ]
     pie = reduce(pie_by_camera, data, {})
     fig, ax = plt.subplots()
-    ax.pie(pie.values(), labels=pie.keys(), autopct='%1.1f%%')
+    plt.rcParams['font.size'] = 12.0
+    plt.rcParams['text.usetex'] = True
+    values = list(pie.values())
+    keys = list(pie.keys())
+    for i in range(len(keys)):
+        keys[i] = r'$\mathrm{{{0}}}$'.format(keys[i])
+    ax.pie(values, labels=keys, autopct=r'$%.1f\%%$')
     fig.tight_layout()
-    fig.savefig('by-camera.png')
+    fig.savefig('by-camera.png', bbox_inches='tight', pad_inches=0)

### 2021-03-31 scripts/make_by-collision.py

@@ -6,9 +6,9 @@ from functools import reduce
 from matplotlib import pyplot as plt
 
 FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
-NO_COLLISION_LABEL = "No Collision"
-MULTI_COLLISION_LABEL = "Multi Collision"
-SIMPLE_COLLISION_LABEL = "Simple Collision"
+NO_COLLISION_LABEL = "No\ Collision"
+MULTI_COLLISION_LABEL = "Multi\ Collision"
+SIMPLE_COLLISION_LABEL = "Simple\ Collision"
 
 def pie_by_collision(hist, data):
     (key, data) = data
@@ -39,6 +39,12 @@ if __name__ == '__main__':
     data = [ val for val in metadata.get().items() ]
     pie = reduce(pie_by_collision, data, {})
     fig, ax = plt.subplots()
-    ax.pie(pie.values(), labels=pie.keys(), autopct='%1.1f%%')
+    plt.rcParams['font.size'] = 12.0
+    plt.rcParams['text.usetex'] = True
+    values = list(pie.values())
+    keys = list(pie.keys())
+    for i in range(len(keys)):
+        keys[i] = r'$\mathrm{{{0}}}$'.format(keys[i])
+    ax.pie(values, labels=keys, autopct=r'$%.1f\%%$')
     fig.tight_layout()
-    fig.savefig('by-collision.png')
+    fig.savefig('by-collision.png', bbox_inches='tight', pad_inches=0)

### 2021-04-01 paper.tex
Updated some metadata field descriptions to be more accurate

@@
   %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
-  \item "\texttt{}": Description of the video as scraped from the video hosting website
-  \item "\texttt{state}": String that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
+  \item "\texttt{description}": Description of the video as scraped from the video hosting website
+  \item "\texttt{state}": String that describes the current labelling state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
   \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
   \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site specific
-  \item "\texttt{title}": String that represents the type of the video
+  \item "\texttt{title}": The title of the video from the video hosting website
   \item "\texttt{url}": Url that the video was fetched from
-  \item "\texttt{is\_split\_url}": Boolean that is true if all of the frames of the video are covered in this metadata item and false if no
+  \item "\texttt{is\_split\_url}": Boolean that is true if the video has been segmented into multiple \texttt{MetaDataItem} objects during labelling
   \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
-  \item "\texttt{start\_i}": The start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
-  \item "\texttt{end\_i}": The end frame of the video the bounding boxes are created for (if is\_split\_url is true)
+  \item "\texttt{start\_i}": The start frame of the video segment that the bounding boxes are created for (if is\_split\_url is true)
+  \item "\texttt{end\_i}": The end frame of the video segment the bounding boxes are created for (if is\_split\_url is true)
   \item "\texttt{bb\_fields}": All bounding-box specific data

### 2021-04-01 paper.tex
Small update for missing word
adjusted + fixed chart label positions, distances and angles

@@
   \item "\texttt{start\_i}": The start frame of the video segment that the bounding boxes are created for (if is\_split\_url is true)
-  \item "\texttt{end\_i}": The end frame of the video segment the bounding boxes are created for (if is\_split\_url is true)
+  \item "\texttt{end\_i}": The end frame of the video segment that the bounding boxes are created for (if is\_split\_url is true)
   \item "\texttt{bb\_fields}": All bounding-box specific data
@@
       ylabel={Frequency (\# of objects)},
+      ymin=-50,
+      ymax=1800,
       xtick=data,
       xticklabels from table={\byclass}{X},
-      xticklabel style={rotate=90}
+      xticklabel style={rotate=50,anchor=east,yshift=-2mm}
     ]
@@
       ylabel={Frequency (\# of videos)},
+      ymin=-5,
+      ymax=175,
       xtick=data,
-      xticklabels from table={\byactors}{X},
-      xticklabel style={rotate=90}
+      xticklabels from table={\byactors}{X}
     ]
@@
       ylabel={Frequency (\# of videos)},
+      ymin=-10,
+      ymax=270,
       xtick=data,
@@
       xtick=data,
+      ymin=-5,
+      ymax=130,
       xticklabels from table={\byduration}{X},
-      xticklabel style={rotate=90}
+      xticklabel style = {rotate=45,anchor=east,yshift=-2mm}
     ]
@@
 		\centering
-    \includegraphics[width=3in,trim={0 1cm 0 1cm},clip]{by-collision.png}
+    \includegraphics[width=3in,trim={0 1cm 0 0.5cm},clip]{by-collision.png}
 		\caption{All videos in database grouped by collision type}

### 2021-04-01 scripts/make_by-camera.py

@@ -39,12 +39,28 @@ if __name__ == '__main__':
     data = [ val for val in metadata.get().items() ]
     pie = reduce(pie_by_camera, data, {})
     fig, ax = plt.subplots()
-    plt.rcParams['font.size'] = 12.0
+    plt.rcParams['font.size'] = 16.0
     plt.rcParams['text.usetex'] = True
     values = list(pie.values())
     keys = list(pie.keys())
+    # Format the labels and values with LaTeX typeface
     for i in range(len(keys)):
         keys[i] = r'$\mathrm{{{0}}}$'.format(keys[i])
-    ax.pie(values, labels=keys, autopct=r'$%.1f\%%$')
+    patches, texts, wedgepcts = ax.pie(values, labels=keys, autopct=r'$%.1f\%%$')
+    
+    # Set the radial positions of the wedge pcts
+    for pct, label in zip(wedgepcts, list(pie.keys())):
+        d = 0.8 
+        if label == MANHELD_CAMERA_LABEL:
+            d = 1.44
+        elif label == STATIONARY_CAMERA_LABEL:
+            d = 1.25
+        xi,yi = pct.get_position()
+        ri = np.sqrt(xi**2+yi**2)
+        phi = np.arctan2(yi,xi)
+        x = d*ri*np.cos(phi)
+        y = d*ri*np.sin(phi)
+        pct.set_position((x,y))
+    
     fig.tight_layout()
-    fig.savefig('by-camera.png', bbox_inches='tight', pad_inches=0)
+    fig.savefig('by-camera.png', dpi=300, bbox_inches='tight', pad_inches=0)

### 2021-04-01 scripts/make_by-collision.py

@@ -39,12 +39,13 @@ if __name__ == '__main__':
     data = [ val for val in metadata.get().items() ]
     pie = reduce(pie_by_collision, data, {})
     fig, ax = plt.subplots()
-    plt.rcParams['font.size'] = 12.0
+    plt.rcParams['font.size'] = 14.0
     plt.rcParams['text.usetex'] = True
     values = list(pie.values())
     keys = list(pie.keys())
+    # Format the labels and values with LaTeX typeface
     for i in range(len(keys)):
         keys[i] = r'$\mathrm{{{0}}}$'.format(keys[i])
     ax.pie(values, labels=keys, autopct=r'$%.1f\%%$')
     fig.tight_layout()
-    fig.savefig('by-collision.png', bbox_inches='tight', pad_inches=0)
+    fig.savefig('by-collision.png', dpi=300, bbox_inches='tight', pad_inches=0)

### 2021-04-01 paper.tex
adjusted figure widths
added distributions for videos by location and region

@@
 We provide a pipeline to assemble datasets of real vehicle collision events that have been published online to various video repositories.
-We specifically focus on collecting collisions recorded from front-mounted dashcam video cameras and demonstrate the importance of learning from complex road scenes and conditions globally rather than in one region.
+We specifically focus on collecting footage of collisions recorded from front-mounted dashcam video cameras and demonstrate the importance of learning from complex road scenes and conditions globally rather than in one region.
 Further, we present a small prototype dataset that we have produced using our pipeline which includes egocentric dashcam vehicle footage from all over the world, subject to varying visibilities, varying weather conditions, and varying settings.
@@
 
-\begin{figure}[htpb]
+\begin{figure}[htbp]
 	\centering
@@
 
-\begin{figure}[htpb]
+\begin{figure}[htbp]
 		\centering
-    \includegraphics[width=0.5\textwidth]{example_gui_tool.png}
+    \includegraphics[width=0.46\textwidth]{example_gui_tool.png}
 		\caption{GUI tool to facilitate annotation}
@@
 
-\begin{figure}[htpb]
+\begin{figure}[htbp]
 		\centering
-		\includegraphics[width=0.4\textwidth]{prcurve.png}
+		\includegraphics[width=0.5\textwidth]{prcurve.png}
 		\caption{Pre-trained DSARNN Precision-Recall curve on prototype dataset}
@@
 
-\begin{figure}[htpb]
+\begin{figure}[htbp]
 		\centering
@@
     \end{tikzpicture}
-		\caption{Videos in dataset grouped by object class}
+		\caption{Distribution of videos in dataset by object class}
 		\label{fig:obj-by-class}
@@
     \end{tikzpicture}
-		\caption{Videos in dataset grouped by number of participants}
+		\caption{Distribution of videos in dataset by number of participants}
 		\label{fig:vids-by-participant}
@@
     \end{tikzpicture}
-		\caption{Videos in dataset grouped by number of agents}
+		\caption{Distribution of videos in dataset by number of agents}
 		\label{fig:vids-by-agents}
@@
     \end{tikzpicture}
-		\caption{Videos in dataset grouped by duration}
+		\caption{Distribution of videos in dataset by duration}
 		\label{fig:vids-by-duration}
@@
 
-\begin{figure}[htpb]
+\begin{figure}[htbp]
 		\centering
-    \includegraphics[width=3in,trim={0 1cm 0 0.5cm},clip]{by-collision.png}
-		\caption{All videos in database grouped by collision type}
+    \includegraphics[width=0.46\textwidth,trim={0 1cm 0 0.5cm},clip]{by-collision.png}
+		\caption{Distribution of videos in database by collision type}
 		\label{fig:vids-by-collision}
@@
 
-\begin{figure}[htpb]
+\begin{figure}[htbp]
 		\centering
-    \includegraphics[width=3in,trim={0 1cm 0 1cm},clip]{by-camera.png}
-		\caption{All videos in database grouped by camera type}
+    \includegraphics[width=0.46\textwidth,trim={0 1cm 0 1cm},clip]{by-camera.png}
+		\caption{Distribution of videos in database by camera type}
 		\label{fig:vids-by-camera}
 \end{figure}
+
+\begin{table}[htbp]
+	\caption{Distribution of videos in database by download source}
+	\label{vids-by-source}
+	\begin{center}
+		\begin{tabular}{|c|c|}
+			\hline
+			Download source & Percentage of videos \\
+			\hline
+			youtube.com & 98.40\% \\
+			\hline
+			imgur.com & 0.85\% \\
+			\hline
+			gfycat.com & 0.47\% \\
+			\hline
+			streamable.com & 0.28\% \\
+			\hline
+		\end{tabular}
+	\end{center}
+\end{table}
+
+\begin{table}[htbp]
+	\caption{Distribution of videos in dataset by geographical region}
+	\label{vids-by-region}
+	\begin{center}
+		\begin{tabular}{|c|c|}
+			\hline
+			Region & Percentage of videos \\
+			\hline
+			North America & 48.13\% \\
+			\hline
+			Europe & 24.30\% \\
+			\hline
+			Russia & 19.16\% \\
+			\hline
+			Asia & 4.67\% \\
+			\hline
+			Australia & 3.74\% \\
+			\hline
+		\end{tabular}
+	\end{center}
+\end{table}
 
@@
 \todo{Explain the distinctions between the different types of collisions in the collision chart.}
-\todo{Add chart showing videos by source (Figure 11).}
+\todo{Add Figure 11 (table) showing videos by source (98.4\% YouTube, 0.47\% gfycat.com, 0.85\% imgur.com, 0.28\% streamable.com)}
 \todo{Move Figures 5-11 to Methodology - Video Collection.}

### 2021-04-01 scripts/make_by-source.py

@@ -1,0 +1,63 @@
+import numpy as np
+import firebase_admin as fb
+from firebase_admin import credentials, db
+from firebase_admin.db import Reference
+from functools import reduce
+from matplotlib import pyplot as plt
+
+FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
+YOUTUBE_LABEL = "YouTube"
+REDDIT_LABEL = "Reddit"
+IMGUR_LABEL = "imgur.com"
+GFYCAT_LABEL = "gfycat.com"
+STREAMABLE_LABEL = "streamable.com"
+
+def pie_by_source(hist, data):
+    (key, data) = data
+    if not data.get('download_src'):
+        return hist
+    src = data['download_src']
+    if src == YOUTUBE_LABEL or src == 'youtube.com':
+        hist.update({ YOUTUBE_LABEL: hist.get(YOUTUBE_LABEL, 0) + 1 })
+    elif src == REDDIT_LABEL:
+        hist.update({ REDDIT_LABEL: hist.get(REDDIT_LABEL, 0) + 1 })
+    elif src == GFYCAT_LABEL:
+        hist.update({ GFYCAT_LABEL: hist.get(GFYCAT_LABEL, 0) + 1 })
+    elif src == STREAMABLE_LABEL:
+        hist.update({ STREAMABLE_LABEL: hist.get(STREAMABLE_LABEL, 0) + 1 })
+    elif src == IMGUR_LABEL:
+        hist.update({ IMGUR_LABEL: hist.get(IMGUR_LABEL, 0) + 1 })       
+    else:
+        print(src)
+
+    return hist
+
+if __name__ == '__main__':
+    cred = credentials.Certificate(FIREBASE_CRED_FILENAME)
+    print('Created credentials')
+    fb_app = fb.initialize_app(cred, {
+            'databaseURL': 'https://autodash-9dccb.firebaseio.com/',
+            'databaseAuthVariableOverride': {
+                'uid': 'pipeline-worker'
+            }
+        })
+    print('Created app')
+    metadata = db.reference('metadata')
+    print('Retrieved data')
+    data = [ val for val in metadata.get().items() ]
+    pie = reduce(pie_by_source, data, {})
+    fig, ax = plt.subplots()
+    plt.rcParams['font.size'] = 16.0
+    plt.rcParams['text.usetex'] = True
+    values = list(pie.values())
+    keys = list(pie.keys())
[…]

### 2021-04-01 paper.tex
fix by-collision chart to operate on our pre-processed dataset. V1 of paper for ITSC submission complete.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo{Overall TODO: fix awkward sentences, grammatical issues. }
 \begin{abstract}
@@
 We aim to generate datasets that are not constrained to any regions or countries but rather provide location-agnostic data that is representative of general, global road and vehicle conditions.
-\todo{Backup this claim with the location histogram, perhaps in the experiment section.
-If we put it there, we should reference it from here.}
 These datasets will also be collision-oriented as the majority of these videos contain collisions for people's viewing.
 Current autonomous vehicle data collection techniques typically require astronomically expensive hardware and equipment and, consequently, are rarely involved in collisions and intentionally not put in high risk environments that may lead to a collision.
-This is the data we hope to capture by taking advantage of existing videos of non-artificial collisions.
-\todo{Add sentence explaining we don't care about video resolution as long as collisions and agents are clear in the video.
-Further support this by the fact that we aren't using the final dense classification layer in the VGG, which in turns allows us to use videos of any resolution.
-}
+Thus, our goal is to capture this data by taking advantage of existing videos of real-world collisions.
 
 The pipeline uses web-scraping techniques to fetch the video data from these websites, along with a set of video metadata, describing the video's contents.
-We use this data, in combination with the manually annotated data in order to create the collision dataset.
+We use this data, in combination with the manually annotated data in order to create a prototype collision dataset of dashcam video samples.
 This combination allows us to take advantage of the wide variety of videos available on the internet, while still having reliable data that has been curated manually.
@@
 Participants are objects that are involved in a collision identified in the metadata, while bystanders are uninvolved objects.
+
+It is worthwhile to note that in collecting samples for our prototype dataset, we do not impose a minimum video resolution threshold.
+We mitigate this by only collecting samples which contain clearly identifiable agents.
+This allows us to maximize the amount of data that we can feasibly include in our dataset.
 
@@
 In addition to collection and preprocessing, a core component of our pipeline is a GUI tool that facilitates the manual annotation of the dashcam videos, and quick manual filtering of non-dashcam and irrelevant videos.
-Following Chan et al.\cite{chan2016anticipating}, if a collision occurs we provide tools to annotate the frame the collision occurs, and bounding boxes to localize, identify and track agents in the video segment.
+Following Chan et al.\cite{chan2016anticipating}, if a collision occurs, we provide tools to annotate the frame where the collision occurs and bounding boxes to localize, identify and track agents in the video segment.
 Object tracking bounding boxes can be linearly interpolated from manual start and end points to improve ease of labelling.
-We also save the video resolution at which the video was annotated to ensure bounding box annotations can always be scaled to fit any variable download resolutions.
+We also save the video resolution at which the video was annotated to ensure bounding box annotations can always be scaled to fit variable download resolutions.
 For long-form videos that may contain multiple collision events or irrelevant video segments, such as compilation videos or videos with substantial editing and transitions, we provide a video clipping feature to demarcate the collision events from which we extract and generate distinct data points.
-Each video segment will eventually become a metadata item.
+Each video segment will eventually become a metadata item. Figure \ref{fig:example_gui_tool-png} shows an example of the GUI tool in usage.
 
@@
 
-\begin{figure}
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.46\textwidth]{example_gui_tool.png}
+	\caption{GUI tool to facilitate annotation}
+	\label{fig:example_gui_tool-png}
+\end{figure}
+
+\begin{figure}[htbp]
   \begin{lstlisting}[language=json,xleftmargin=5mm]
@@
 
-\begin{figure}[htbp]
-		\centering
-    \includegraphics[width=0.46\textwidth]{example_gui_tool.png}
-		\caption{GUI tool to facilitate annotation}
-		\label{fig:example_gui_tool-png}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In order to evaluate the importance of acquiring data from multiple geographical locations and under varying driving conditions around the world, we have manually collected a dataset of 223 video clips on which we will test the existing collision anticipation model, DSARNN.
+\subsection{Prototype Dataset}
+\label{section-prototype-dataset}
+In order to evaluate the importance of acquiring data from multiple geographical locations and under varying driving conditions around the world, we have built a prototype dataset of 223 video clips using our pipeline on which we will test the existing collision anticipation model, DSARNN.
 This dataset is comprised of 97 positive and 126 negative videos.
@@
 
-In our first experiment we merge our dataset with the dataset provided by Chan et.
-al.
-We augment their training set with 77 positives and 106 negatives, and their testing set with 20 positives and 20 negatives.
-We use the same training procedure as Chan et.
-al, namely we train for 40 epochs with a learning rate of $10^{-4}$ and a batch size of 10.
-Although our data contribution here is relatively small, we observe a mean time-to-collision of 2.198s at 80\% recall which is very similar to the existing results from Chan et.
-al.
-However, we observe an average precision of 66.22\% which is appreciably lower than the 73.53\% average precision reported by Chan et.
-al.
-\cite{chan2016anticipating}
-
-In our second experiment we use the provided pre-trained DSARNN model and test the performance on our entire dataset of 223 videos.
-We see very poor prediction performance at an average precision of 34.29\%, and in Figure \ref{fig:pr_curve} we observe poor precision at all recall values.
-
-\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=0.5\textwidth]{prcurve.png}
-		\caption{Pre-trained DSARNN Precision-Recall curve on prototype dataset}
-		\label{fig:pr_curve}
-\end{figure}
-
-These experiments seem to support the notion that in order for a collision prediction model to be generally effective in practice, it must be trained on collisions and complex roads scenes from varying regions and road conditions around the world, which is what we hope to achieve with this data collection pipeline.
-
 \pgfplotstableread[col sep=comma]{by-classes.csv}\byclass
@@
 
-We have aggregated some statistics about our dataset to help clients understand various distributions in the data.
+We have aggregated some statistics about our database and dataset to help clients understand the pertinent distributions in the data.
 While these distributions may be representative of online collision footage, they are not necessarily representative of real world collisions.
+Note that the total number of videos represented by the histograms is a superset of the number of videos in the final prototype dataset as it includes videos that were ultimately unsuitable for our collision prediction experiments.
+Thus we denote this superset as the \textit{pre-processed prototype dataset}.
 
-\begin{figure}[htbp]
-		\centering
-    \begin{tikzpicture}
-    \begin{axis}[
-      title={Objects by class},
-      ylabel={Frequency (\# of objects)},
-      ymin=-50,
-      ymax=1800,
-      xtick=data,
-      xticklabels from table={\byclass}{X},
-      xticklabel style={rotate=50,anchor=east,yshift=-2mm}
-    ]
-    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
-    \end{axis}
-    \end{tikzpicture}
-		\caption{Distribution of videos in dataset by object class}
-		\label{fig:obj-by-class}
-\end{figure}
-
-\begin{figure}[htbp]
-		\centering
-    \begin{tikzpicture}
-    \begin{axis}[
-      title={Videos by participant},
-      xlabel={Number of participants},
-      ylabel={Frequency (\# of videos)},
-      ymin=-5,
-      ymax=175,
-      xtick=data,
-      xticklabels from table={\byactors}{X}
-    ]
-    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
-    \end{axis}
-    \end{tikzpicture}
-		\caption{Distribution of videos in dataset by number of participants}
-		\label{fig:vids-by-participant}
-\end{figure}
-
-\begin{figure}[htbp]
-		\centering
-    \begin{tikzpicture}
-    \begin{axis}[
-      title={Videos by agents},
-      xlabel={Number of agents},
-      ylabel={Frequency (\# of videos)},
-      ymin=-10,
-      ymax=270,
-      xtick=data,
-      xticklabels from table={\byagents}{X}
-    ]
-    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byagents;
-    \end{axis}
-    \end{tikzpicture}
-		\caption{Distribution of videos in dataset by number of agents}
-		\label{fig:vids-by-agents}
-\end{figure}
-
-\begin{figure}[htbp]
-		\centering
-    \begin{tikzpicture}
-    \begin{axis}[
-      title={Videos by duration},
-      xlabel={Duration (in frames)},
-      ylabel={Frequency (\# of videos)},
-      xtick=data,
-      ymin=-5,
-      ymax=130,
-      xticklabels from table={\byduration}{X},
-      xticklabel style = {rotate=45,anchor=east,yshift=-2mm}
-    ]
-    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byduration;
-    \end{axis}
-    \end{tikzpicture}
-		\caption{Distribution of videos in dataset by duration}
-		\label{fig:vids-by-duration}
-\end{figure}
-
-\begin{figure}[htbp]
-		\centering
-    \includegraphics[width=0.46\textwidth,trim={0 1cm 0 0.5cm},clip]{by-collision.png}
-		\caption{Distribution of videos in database by collision type}
-		\label{fig:vids-by-collision}
-\end{figure}
-
-\begin{figure}[htbp]
-		\centering
-    \includegraphics[width=0.46\textwidth,trim={0 1cm 0 1cm},clip]{by-camera.png}
-		\caption{Distribution of videos in database by camera type}
-		\label{fig:vids-by-camera}
-\end{figure}
-
-\begin{table}[htbp]
+\begin{table}[!h]
 	\caption{Distribution of videos in database by download source}
@@
 			\hline
-			youtube.com & 98.40\% \\
+			youtube.com & \textbf{98.40\%} \\
 			\hline
@@
 
-\begin{table}[htbp]
-	\caption{Distribution of videos in dataset by geographical region}
+\begin{table}[!h]
+	\caption{Distribution of videos in pre-processed prototype dataset by geographical region}
 	\label{vids-by-region}
@@
 
-\todo{Organize figures better, crop out excess whitespace, resize them and place them within the column of the page.}
-\todo{Explain the "other" category in the class histogram. These are stationary/non-vehicular objects.}
-\todo{Explain the distinctions between the different types of collisions in the collision chart.}
-\todo{Add Figure 11 (table) showing videos by source (98.4\% YouTube, 0.47\% gfycat.com, 0.85\% imgur.com, 0.28\% streamable.com)}
-\todo{Move Figures 5-11 to Methodology - Video Collection.}
-\todo{Reduce caption size for each figure.}
-\todo{Add a paragraph explaining the key characteristics of Figures 5-11.}
+From Table \ref{vids-by-source}, it is clear that the vast majority of videos that have been processed through our pipeline and cataloged in our database were obtained from YouTube.
+It can also be seen that the YouTube and Reddit downloaders are capable of scraping various other online repositories such as Imgur, Gfycat and Streamable.
+
+From Table \ref{vids-by-region}, we can see that our prototype dataset consists of dashcam footage from a reasonably well-balanced distribution of geographical regions.
+This also implies a diverse representation in driving conditions due to the various differences in climate and infrastructure amongst these regions.
+
+\begin{figure}[!h]
+	\centering
+	\begin{tikzpicture}
+	\begin{axis}[
+	title={Objects by class},
+	ylabel={Frequency (\# of objects)},
+	ymin=-50,
+	ymax=1800,
+	xtick=data,
+	xticklabels from table={\byclass}{X},
+	xticklabel style={rotate=50,anchor=east,yshift=-2mm}
+	]
+	\addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
+	\end{axis}
+	\end{tikzpicture}
+	\caption{Distribution of videos in pre-processed prototype dataset by object class}
+	\label{fig:obj-by-class}
+\end{figure}
+
+\begin{figure}[!h]
+	\centering
+	\begin{tikzpicture}
+	\begin{axis}[
+	title={Videos by participant},
+	xlabel={Number of participants},
+	ylabel={Frequency (\# of videos)},
+    ymin=-5,
+	ymax=175,
+	xtick=data,
+	xticklabels from table={\byactors}{X}
+	]
+	\addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
+	\end{axis}
+	\end{tikzpicture}
+	\caption{Distribution of videos in pre-processed prototype dataset by number of participants}
+	\label{fig:vids-by-participant}
+\end{figure}
+
+In Figure \ref{fig:obj-by-class}, we see that there are several types of objects which have been identified as agents in our prototype dataset.
+Among these, the most common are motorized vehicles and pedestrians as one would intuitively expect.
+A number of stationary, inanimate objects such as industrial machinery and poles were noteworthy as they were involved in collisions.
+These have been aggregated into the "other" category.
+
+In Figure \ref{fig:vids-by-participant}, it can be seen that there is a wide range in the distribution of the number of participants in each sample of our dataset.
+We also observe that it is more common for no collisions to occur than any particular non-zero number of participants to be present in a sample.
+
+In Figure \ref{fig:vids-by-agents}, we observe that it is most common for samples to contain either 2 agents or no agents at all.
+This is implied by the fact that videos with only 1 agent cannot contain a collision.
+These are less likely to be interesting and in turn, scraped by our pipeline.
+
+\begin{figure}[!h]
+	\centering
+	\begin{tikzpicture}
+	\begin{axis}[
+	title={Videos by agents},
+	xlabel={Number of agents},
+	ylabel={Frequency (\# of videos)},
+    ymin=-10,
+	ymax=270,
+	xtick=data,
+	xticklabels from table={\byagents}{X}
+	]
+	\addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byagents;
+	\end{axis}
+	\end{tikzpicture}
+	\caption{Distribution of videos in prototype dataset by number of agents}
+	\label{fig:vids-by-agents}
+\end{figure}
+
+In Figure \ref{fig:vids-by-duration}, we can clearly see that there is a roughly standard normal distribution in the number of videos by duration, with a mean, median and mode at around 352 frames.
+This suggests that the pipeline favors videos which tend to be shorter on average.
+At an average video framerate of 30 FPS, this equates to a mean duration of just over 11 seconds.
+In section \ref{section-prototype-dataset}, it was mentioned that clips were cropped to 5 seconds in the prototype dataset, therefore this is a favorable characteristic as it helps reduce the amount of necessary processing.
+
+\begin{figure}[!h]
+	\centering
+	\begin{tikzpicture}
+	\begin{axis}[
+	title={Videos by duration},
+	xlabel={Duration (in frames)},
+	ylabel={Frequency (\# of videos)},
+	xtick=data,
+    ymin=-5,
+	ymax=130,
+	xticklabels from table={\byduration}{X},
+	xticklabel style = {rotate=45,anchor=east,yshift=-2mm}
+	]
+	\addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byduration;
+	\end{axis}
+	\end{tikzpicture}
+	\caption{Distribution of videos in prototype dataset by duration}
+	\label{fig:vids-by-duration}
+\end{figure}
+
+Figures \ref{fig:vids-by-collision} and \ref{fig:vids-by-camera} outline key characteristics about our database at large.
+Figure \ref{fig:vids-by-collision} shows that from the video repositories we targeted, we were able to obtain a relatively well-balanced distribution of collision types in our data.
+Here, the distinction between 'Simple Collision' and 'Multi Collision' is that the former involves 2 participants and the latter involves more than 2 participants.
+Figure \ref{fig:vids-by-camera} shows that the majority of the videos the pipeline scraped were indeed dashcam videos.
+This suggests that the pipeline is quite effective in identifying suitable candidates for a dashcam collision dataset.
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.46\textwidth,trim={0 1cm 0 0},clip]{by-collision.png}
+	\caption{Distribution of videos in database by collision type}
+	\label{fig:vids-by-collision}
+\end{figure}
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.46\textwidth,trim={0 1cm 0 1cm},clip]{by-camera.png}
+	\caption{Distribution of videos in database by camera type}
+	\label{fig:vids-by-camera}
+\end{figure}
+
+\subsection{Collision Prediction Model Training and Analysis}
+\label{section-collision-prediction}
+In our first experiment we merge our dataset with the dataset provided by Chan et.
+al.
+We augment their training set with 77 positives and 106 negatives, and their testing set with 20 positives and 20 negatives.
+We use the same training procedure as Chan et.
+al, namely we train for 40 epochs with a learning rate of $10^{-4}$ and a batch size of 10.
+Although our data contribution here is relatively small, we observe a mean time-to-collision of \textbf{2.198s} at \textbf{80\%} recall which is very similar to the existing results from Chan et.
+al.
+However, we observe an average precision of 66.22\% which is appreciably lower than the 73.53\% average precision reported by Chan et.
+al.
+\cite{chan2016anticipating}
+
+In our second experiment we use the provided pre-trained DSARNN model and test the performance on our entire dataset of 223 videos.
+We see very poor prediction performance at an average precision of 34.29\%, and in Figure \ref{fig:pr_curve} we observe poor precision at all recall values.
+
+\begin{figure}[!htbp]
+		\centering
+		\includegraphics[width=0.5\textwidth]{prcurve.png}
+		\caption{Pre-trained DSARNN Precision-Recall curve on prototype dataset}
+		\label{fig:pr_curve}
+\end{figure}
+
+These experiments support the notion that in order for a collision prediction model to be generally effective in practice, it must be trained on collisions and complex roads scenes from varying regions and road conditions around the world, which is what we hope to achieve with this data collection pipeline.
 
@@
 \begin{enumerate}
-\item Labelling precision improvements: The current video-labelling process in the pipeline, manual bounding box drawing with linear interpolation between input frames, is prone to inserting mistaken bounding boxes that don't exactly match to the location of an object on certain frames.
+\item \textbf{Labelling precision improvements:} The current video-labelling process in the pipeline, manual bounding box drawing with linear interpolation between input frames, is prone to inserting mistaken bounding boxes that don't exactly match to the location of an object on certain frames.
 Automated labelling and custom interpolation would speed up the process of labelling and minimize the cases of misplaced bounding boxes.
@@
 
-\item Complete Location-Varied Dataset: Our next step is to enlarge our existing dataset of car collisions from regions all over the world, which would then use solely to form a training set and testing set for our next experiment.
+\item \textbf{Complete Location-Varied Dataset:} Our next step is to enlarge our existing dataset of car collisions from regions all over the world, which would then use solely to form a training set and testing set for our next experiment.
 We could then compare the results of this experiment with location-varied data to the results from the dataset collected in Taiwan by Chan et.

### 2021-04-01 scripts/make_by-collision.py

@@ -12,7 +12,7 @@ SIMPLE_COLLISION_LABEL = "Simple\ Collision"
 
 def pie_by_collision(hist, data):
     (key, data) = data
-    if not data.get('enum_tags'):
+    if data.get('is_cancelled', True) or not data.get('enum_tags'):
         return hist
     enum_tags = data['enum_tags']
     if 'MultiCollision' in enum_tags:

### 2021-04-01 paper.tex
minor grammatical fixes; updated V1

@@
 At an average video framerate of 30 FPS, this equates to a mean duration of just over 11 seconds.
-In section \ref{section-prototype-dataset}, it was mentioned that clips were cropped to 5 seconds in the prototype dataset, therefore this is a favorable characteristic as it helps reduce the amount of necessary processing.
+In section \ref{section-prototype-dataset}, it was mentioned that clips were cropped to 5 seconds in the prototype dataset.
+Therefore, this is a favorable characteristic as it helps reduce the amount of necessary processing.
 
@@
 \label{section-collision-prediction}
-In our first experiment we merge our dataset with the dataset provided by Chan et.
+In our first experiment, we merge our prototype dataset with the dataset provided by Chan et.
 al.
@@
 We use the same training procedure as Chan et.
-al, namely we train for 40 epochs with a learning rate of $10^{-4}$ and a batch size of 10.
+al.
+Namely, we train for 40 epochs with a learning rate of $10^{-4}$ and a batch size of 10.
 Although our data contribution here is relatively small, we observe a mean time-to-collision of \textbf{2.198s} at \textbf{80\%} recall which is very similar to the existing results from Chan et.
@@
 
-In our second experiment we use the provided pre-trained DSARNN model and test the performance on our entire dataset of 223 videos.
+In our second experiment, we use the provided pre-trained DSARNN model and test the performance on our entire dataset of 223 videos.
 We see very poor prediction performance at an average precision of 34.29\%, and in Figure \ref{fig:pr_curve} we observe poor precision at all recall values.
@@
 
-These experiments support the notion that in order for a collision prediction model to be generally effective in practice, it must be trained on collisions and complex roads scenes from varying regions and road conditions around the world, which is what we hope to achieve with this data collection pipeline.
+These experiments support the notion that in order for a collision prediction model to be generally effective in practice, it must be trained on collisions and complex roads scenes from varying regions and road conditions around the world.
+This is what we hope to achieve with our data collection pipeline.
 
@@
 
-There are many ways that we could improve our system, such as the following:
+There are many ways in which we could improve our system, namely the following:
 \begin{enumerate}
-\item \textbf{Labelling precision improvements:} The current video-labelling process in the pipeline, manual bounding box drawing with linear interpolation between input frames, is prone to inserting mistaken bounding boxes that don't exactly match to the location of an object on certain frames.
+\item \textbf{Labelling precision improvements:} The current video-labelling process in the pipeline, manual bounding box drawing with linear interpolation between input frames, is prone to inserting mistaken bounding boxes that do not exactly match up with the location of an object on certain frames.
 Automated labelling and custom interpolation would speed up the process of labelling and minimize the cases of misplaced bounding boxes.
 Labelling would be much faster if we had a semi-automated process of detecting objects and tracking them over frames.
-There are models for object detection that behave reasonably well which we could use, but they would still need to be augmented by a review process.
-For object tracking, there are simple heuristic algorithms that could be used.
+There are models for object detection that behave reasonably well for our purposes, but they would still need to be augmented by a review process.
+We could easily solve the problem of object tracking by implementing simple heuristic algorithms.
 Being able to modify the method of interpolation between frames beyond the default linear interpolation would allow for more bounding box precision between large input frame windows.
-Moreover, given a type of interpolation is stored in the metadata, we probably shouldn't store all interpolated frames, rather than just the ones the user has entered.
-While linear interpolation works great for entering a frame every 10 frames, supporting more interpolations could be great for faster data entry, or even for supporting affine transformations on more complex bounds.
+Moreover, if we store the interpolation type in the metadata, we would likely gain a significant improvement in performance and memory usage by not storing all the interpolated frames rather than just the ones the user has entered.
+While linear interpolation works well for entering a frame every 10 frames, supporting additional types of interpolation would facilitate quicker data entry and enable the possibility of supporting affine transformations on more complex bounds.
 
-\item \textbf{Complete Location-Varied Dataset:} Our next step is to enlarge our existing dataset of car collisions from regions all over the world, which would then use solely to form a training set and testing set for our next experiment.
-We could then compare the results of this experiment with location-varied data to the results from the dataset collected in Taiwan by Chan et.
+\item \textbf{Complete Location-Varied Dataset:} Our next step is to expand our existing dataset of automobile collisions to include samples from additional regions across the globe.
+We would then use this to form a training and testing set for our next experiment.
+Finally, we would compare the results of this experiment with location-varied data to the results from the dataset collected in Taiwan by Chan et.
 al.

### 2021-04-02 paper.tex
fixed typos + more grammatical fixes, updated V1

@@
 \title{\LARGE \bf
-A Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets
+A Semi-Automated Software Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets
 }
@@
 Currently, this type of data is often created through computer generated scenarios \cite{Kim_Lee_Hwang_Suh_2019} due to the dangerous and costly nature of road collisions and data collection equipment.
-We provide a pipeline to assemble datasets of real vehicle collision events that have been published online to various video repositories.
+We provide a semi-automated software pipeline to assemble datasets of real vehicle collision events that have been published online to various video repositories.
 We specifically focus on collecting footage of collisions recorded from front-mounted dashcam video cameras and demonstrate the importance of learning from complex road scenes and conditions globally rather than in one region.
@@
 However, we can collect collision data naturally in real driving scenarios through dashcams -- cheap video cameras that can be mounted to a car's dashboard.
-Typically used for insurance purposes, dashcams have the added benefit of recording a wide variety of real collisions that might not be effectively simulated. 
+Typically used for insurance purposes, dashcams have the added benefit of recording a wide variety of real collisions that are difficult to simulate effectively. 
 This has led to the creation of many online communities to share videos of these rare situations on websites such as Reddit, YouTube, and Imgur.
@@
 These datasets will also be collision-oriented as the majority of these videos contain collisions for people's viewing.
-Current autonomous vehicle data collection techniques typically require astronomically expensive hardware and equipment and, consequently, are rarely involved in collisions and intentionally not put in high risk environments that may lead to a collision.
+Current autonomous vehicle data collection techniques typically require astronomically expensive hardware and equipment.
+Consequently, they are rarely involved in collisions and intentionally not put in high risk environments that may lead to a collision.
 Thus, our goal is to capture this data by taking advantage of existing videos of real-world collisions.
@@
 We use this data, in combination with the manually annotated data in order to create a prototype collision dataset of dashcam video samples.
-This combination allows us to take advantage of the wide variety of videos available on the internet, while still having reliable data that has been curated manually.
-As part of this data, we identify participants and bystanders, both known as agents.
+This combination allows us to take advantage of the wide variety of videos available on the Internet while still having reliable data that has been curated manually.
+As part of this data, we identify \textit{participants} and \textit{bystanders}, both known as \textit{agents}.
 Participants are objects that are involved in a collision identified in the metadata, while bystanders are uninvolved objects.
@@
 They propose a novel Dynamic-Spatial-Attention Recurrent Neural Network (DSARNN) that distributes attention to localized and detected vehicles within the video and models temporal dependencies to predict the earliest frame of a potential impending collision.
-Released with their paper is a dataset of 678 dashcam videos capturing areas in Taiwan.
+Along with their paper, they have released a dataset of 678 dashcam videos capturing areas in Taiwan.
 Each video is annotated with vehicle tracking bounding boxes, the vehicles that were involved in the collision and the frame of the collision.
@@
 
-The software pipeline is built from several modular components called executors that each process or handle the data corresponding to a single video before piping the resulting data to the next executor.
+Our pipeline is built from several modular components called executors that each process or handle the data corresponding to a single video before piping the resulting data to the next executor.
 Figure \ref{fig:pr_curve} illustrates the organization of the pipeline in its default configuration.
@@
 This new executor should be added as an entry point in a new YAML configuration and should generate and return a \texttt{MetaDataItem} with video source information to be used by a subsequent and corresponding downloader.
-\texttt{MetaDataItem} objects are fed into the \texttt{UniversalDownloader} which aggregates \texttt{iDownloader} implementations and distributes \texttt{MetaDataItem} objects to their corresponding downloader via regular expressions matching of source URL's.
+\texttt{MetaDataItem} objects are fed into the \texttt{UniversalDownloader} which aggregates \texttt{iDownloader} implementations.
+The \texttt{UniversalDownloader} then distributes \texttt{MetaDataItem} objects to their corresponding downloader by matching source URLs through regular expressions.
 New downloaders should be registered with the \texttt{UniversalDownloader} via a YAML pipeline configuration along with a regular expression string for URL matching.
@@
 Specifically, we provide the executor \texttt{FaceBlurrer}, which blurs faces.
-This executor first uses a MobileNet Single Shot MultiBox Detector \cite{yixuan_h_y_hu_2021_4642275} trained on the WIDERFACE dataset \cite{yang2016wider} to obtain the bounding boxes of all visibly identifiable individuals' faces at each frame of a given video, and then applies a blurring mask over each bounding box.
+This executor first uses a MobileNet Single Shot MultiBox Detector \cite{yixuan_h_y_hu_2021_4642275} trained on the WIDERFACE dataset \cite{yang2016wider} to obtain the bounding boxes of all visibly identifiable individuals' faces at each frame of a given video.
+The executor then applies a blurring mask over each bounding box and writes the modified frame back to the video stream.
 We have chosen to use a MobileNet SSD for this task because it achieves a good balance between accuracy and performance, while requiring relatively little memory \cite{yixuan_h_y_hu_2021_4642275}.
 
-This software module is encapsulated as a library and can be reused by importing our \texttt{anonymization} package.
-The accuracy, amount and type of blurring applied can be tweaked using the API exposed by the \texttt{anonymization} package.
+This software module is encapsulated as a library and can be reused in other projects by importing our \texttt{anonymization} package.
+The accuracy, amount and type of blurring applied can be tweaked using the exposed API.
 
@@
   \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
-  \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site specific
+  \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site- specific
   \item "\texttt{title}": The title of the video from the video hosting website
-  \item "\texttt{url}": Url that the video was fetched from
-  \item "\texttt{is\_split\_url}": Boolean that is true if the video has been segmented into multiple \texttt{MetaDataItem} objects during labelling
+  \item "\texttt{url}": URL that the video was fetched from
+  \item "\texttt{is\_split\_url}": Boolean that is true if the video has been segmented into multiple \texttt{MetaDataItem} objects during labelling, false otherwise
   \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
-  \item "\texttt{start\_i}": The start frame of the video segment that the bounding boxes are created for (if is\_split\_url is true)
-  \item "\texttt{end\_i}": The end frame of the video segment that the bounding boxes are created for (if is\_split\_url is true)
+  \item "\texttt{start\_i}": The start frame of the video segment that the bounding boxes are created for (if \texttt{is\_split\_url} is true)
+  \item "\texttt{end\_i}": The end frame of the video segment that the bounding boxes are created for (if \texttt{is\_split\_url} is true)
   \item "\texttt{bb\_fields}": All bounding-box specific data
@@
     \item "\texttt{collision\_locations}": List of frame numbers indicating the collision start frames
-    \item "\texttt{resolution}": List with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
-    \item "\texttt{objects}": List of all of the bounding boxes for each object in the video.
-An object being either a vehicle or pedestrian.
-Within each object, there is metadata specific to that object.
+    \item "\texttt{resolution}": List with 2 elements (width, height) representing the resolution in pixels of the video the bounding boxes were created for
+    \item "\texttt{objects}": List of all of the relevant metadata pertaining to each agent in the video (either participant or bystander). Each item in this list includes the following:
     \begin{itemize}
       \item "\texttt{id}": Unique numerical identifier that represents this object
-      \item "\texttt{bboxes}": List of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
-      \item "\texttt{class}": The class of the object, such as "car", "pedestrian"
+      \item "\texttt{bboxes}": List of bounding boxes for this specific object.
+Each bounding box is represented as a $1\times5$ array with elements in the following order: frame number, x1, y1, x2, y2
+      \item "\texttt{class}": The class of the object (eg. "car", "pedestrian")
       \item "\texttt{has\_collision}": Boolean that is true if the object is in a collision, false otherwise
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{EXPERIMENT}
+\section{EXPERIMENTS}
 
@@
 This trimming and sampling functionality is provided within the pipeline configuration \texttt{smallcorgi\_exporter.yml}.
-In our experiments we train the DSARNN model on features produced by running a pre-trained VGG on each full frame and the cropped objects within the frame \cite{DBLP:journals/corr/SimonyanZ14a}.
+In our experiments, we train the DSARNN model on features produced by running a pre-trained VGG on each full frame and the cropped objects within the frame \cite{DBLP:journals/corr/SimonyanZ14a}.
 This is denoted VGG+RNN+F+D-con.
@@
 While these distributions may be representative of online collision footage, they are not necessarily representative of real world collisions.
-Note that the total number of videos represented by the histograms is a superset of the number of videos in the final prototype dataset as it includes videos that were ultimately unsuitable for our collision prediction experiments.
-Thus we denote this superset as the \textit{pre-processed prototype dataset}.
+The total number of videos represented by the following tables and histograms is a superset of the number of videos in the final prototype dataset as it includes videos that were ultimately unsuitable for our collision prediction experiments.
+Thus, we denote this superset as the \textit{pre-processed prototype dataset}.
 
@@
 			Download source & Percentage of videos \\
-			\hline
 			youtube.com & \textbf{98.40\%} \\
-			\hline
 			imgur.com & 0.85\% \\
-			\hline
 			gfycat.com & 0.47\% \\
-			\hline
 			streamable.com & 0.28\% \\
@@
 			Region & Percentage of videos \\
-			\hline
 			North America & 48.13\% \\
-			\hline
 			Europe & 24.30\% \\
-			\hline
 			Russia & 19.16\% \\
-			\hline
 			Asia & 4.67\% \\
-			\hline
 			Australia & 3.74\% \\
@@
 
-From Table \ref{vids-by-region}, we can see that our prototype dataset consists of dashcam footage from a reasonably well-balanced distribution of geographical regions.
+From Table \ref{vids-by-region}, we can see that our pre-processed prototype dataset consists of dashcam footage from a reasonably well-balanced distribution of geographical regions.
+The dataset mostly consists of samples from North America, Europe and Russia, which complements the dataset presented by Chan.
+et.
+al.
+\cite{chan2016anticipating} well.
 This also implies a diverse representation in driving conditions due to the various differences in climate and infrastructure amongst these regions.
@@
 
-In Figure \ref{fig:obj-by-class}, we see that there are several types of objects which have been identified as agents in our prototype dataset.
+From Figure \ref{fig:obj-by-class}, we see that there are several types of objects which have been identified as agents in our pre-processed prototype dataset.
 Among these, the most common are motorized vehicles and pedestrians as one would intuitively expect.
-A number of stationary, inanimate objects such as industrial machinery and poles were noteworthy as they were involved in collisions.
+A number of stationary, inanimate objects such as industrial machinery were worth noting as they were involved in collisions.
 These have been aggregated into the "other" category.
 
-In Figure \ref{fig:vids-by-participant}, it can be seen that there is a wide range in the distribution of the number of participants in each sample of our dataset.
+From Figure \ref{fig:vids-by-participant}, it can be seen that there is a wide range in the distribution of the number of participants in each sample of our dataset.
 We also observe that it is more common for no collisions to occur than any particular non-zero number of participants to be present in a sample.
 
-In Figure \ref{fig:vids-by-agents}, we observe that it is most common for samples to contain either 2 agents or no agents at all.
+From Figure \ref{fig:vids-by-agents}, we observe that it is most common for samples to contain either exactly 2 agents or no agents at all.
 This is implied by the fact that videos with only 1 agent cannot contain a collision.
@@
 	\end{tikzpicture}
-	\caption{Distribution of videos in prototype dataset by number of agents}
+	\caption{Distribution of videos in pre-processed prototype dataset by number of agents}
 	\label{fig:vids-by-agents}
@@
 
-In Figure \ref{fig:vids-by-duration}, we can clearly see that there is a roughly standard normal distribution in the number of videos by duration, with a mean, median and mode at around 352 frames.
+From Figure \ref{fig:vids-by-duration}, we can clearly see that there is a roughly standard normal distribution in the number of videos by duration, with a mean, median and mode at around 352 frames.
 This suggests that the pipeline favors videos which tend to be shorter on average.
-At an average video framerate of 30 FPS, this equates to a mean duration of just over 11 seconds.
-In section \ref{section-prototype-dataset}, it was mentioned that clips were cropped to 5 seconds in the prototype dataset.
+At an average video framerate of 30 FPS, this equates to a mean sample duration of just over 11 seconds.
+In section \ref{section-prototype-dataset}, it was mentioned that the samples were cropped to 5 seconds in the final prototype dataset.
 Therefore, this is a favorable characteristic as it helps reduce the amount of necessary processing.
@@
 	\end{tikzpicture}
-	\caption{Distribution of videos in prototype dataset by duration}
+	\caption{Distribution of videos in pre-processed prototype dataset by duration}
 	\label{fig:vids-by-duration}
@@
 Figure \ref{fig:vids-by-collision} shows that from the video repositories we targeted, we were able to obtain a relatively well-balanced distribution of collision types in our data.
-Here, the distinction between 'Simple Collision' and 'Multi Collision' is that the former involves 2 participants and the latter involves more than 2 participants.
+Here, the distinction between \textit{Simple Collision} and \textit{Multi Collision} is that the former involves exactly 2 participants and the latter involves more than 2 participants.
 Figure \ref{fig:vids-by-camera} shows that the majority of the videos the pipeline scraped were indeed dashcam videos.
-This suggests that the pipeline is quite effective in identifying suitable candidates for a dashcam collision dataset.
+This suggests that the pipeline is quite effective in identifying suitable candidates for a  dataset consisting solely of dashcam collision footage.
 
@@
 These experiments support the notion that in order for a collision prediction model to be generally effective in practice, it must be trained on collisions and complex roads scenes from varying regions and road conditions around the world.
-This is what we hope to achieve with our data collection pipeline.
 
@@
 \begin{enumerate}
-\item \textbf{Labelling precision improvements:} The current video-labelling process in the pipeline, manual bounding box drawing with linear interpolation between input frames, is prone to inserting mistaken bounding boxes that do not exactly match up with the location of an object on certain frames.
+\item \textbf{Labelling precision improvements:} The current video labelling process in the pipeline involves manual bounding box drawing with linear interpolation between input frames.
+This is prone to inserting mistaken bounding boxes that do not exactly match up with the location of an object on certain frames.
 Automated labelling and custom interpolation would speed up the process of labelling and minimize the cases of misplaced bounding boxes.
@@
 Moreover, if we store the interpolation type in the metadata, we would likely gain a significant improvement in performance and memory usage by not storing all the interpolated frames rather than just the ones the user has entered.
-While linear interpolation works well for entering a frame every 10 frames, supporting additional types of interpolation would facilitate quicker data entry and enable the possibility of supporting affine transformations on more complex bounds.
+While linear interpolation works well for entering one frame for every 10 frames in a video clip, supporting additional types of interpolation would facilitate quicker data entry and enable the possibility of supporting affine transformations on more complex bounds.
 

### 2021-04-03 paper.tex
added ranges in participants and duration histograms (in scripts)

@@
 	xtick=data,
-	xticklabels from table={\byactors}{X}
+	xticklabels from table={\byactors}{X},
+	xticklabel style = {rotate=45,anchor=east,yshift=-2mm}
 	]

### 2021-04-03 scripts/make_by-actors.py

@@ -6,7 +6,7 @@ from functools import reduce
 
 FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
 
-def histogram_by_duration(hist, data):
+def histogram_by_actors(hist, data):
     (key, data) = data
     if data.get('is_cancelled', True):
         return hist
@@ -29,9 +29,10 @@ if __name__ == '__main__':
     metadata = db.reference('metadata')
     print('Retrieved data')
     data = [ val for val in metadata.get().items() ]
-    hist = reduce(histogram_by_duration, data, {})
+    hist = reduce(histogram_by_actors, data, {})
     hist, bins = np.histogram([ *hist.keys() ], weights=[ *hist.values() ])
-    dtype = [ ('X', np.uint32), ('Y', np.uint32) ]
-    Z = np.array([ *zip(bins, hist) ], dtype=dtype)
+    bin_intervals = [str(int(x))+ "-" + str(int(y)) for x,y in zip(bins[:-1], bins[1:])]
+    dtype = [ ('X', object), ('Y', np.uint32) ]
+    Z = np.array([ *zip(bin_intervals, hist) ], dtype=dtype)
     np.savetxt('by-actors.csv', Z, delimiter=',', fmt=['%s', '%d'], header='X,Y', comments='')
 

### 2021-04-03 scripts/make_by-agents.py

@@ -6,7 +6,7 @@ from functools import reduce
 
 FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
 
-def histogram_by_duration(hist, data):
+def histogram_by_agents(hist, data):
     (key, data) = data
     if data.get('is_cancelled', True):
         return hist
@@ -36,7 +36,7 @@ if __name__ == '__main__':
     metadata = db.reference('metadata')
     print('Retrieved data')
     data = [ val for val in metadata.get().items() ]
-    hist = reduce(histogram_by_duration, data, {})
+    hist = reduce(histogram_by_agents, data, {})
     print(hist)
     dtype = [ ('X', object), ('Y', np.uint32) ]
     Z = np.array([ *hist.items() ], dtype=dtype)

### 2021-04-03 scripts/make_by-duration.py

@@ -38,7 +38,9 @@ if __name__ == '__main__':
         hist['Unknown'] = hist[float('inf')]
         del hist[float('inf')]
     """
-    dtype = [ ('X', np.uint32), ('Y', np.uint32) ]
-    Z = np.array([ *zip(bins, hist) ], dtype=dtype)
+    bins = np.insert(bins, 0, 0, axis=0)
+    bin_intervals = [str(int(x))+ "-" + str(int(y)) for x,y in zip(bins[:-1], bins[1:])]
+    dtype = [ ('X', object), ('Y', np.uint32) ]
+    Z = np.array([ *zip(bin_intervals, hist) ], dtype=dtype)
     np.savetxt('by-duration.csv', Z, delimiter=',', fmt=['%s', '%d'], header='X,Y', comments='')
 

### 2021-04-03 scripts/make_by-actors.py
fixed last endpoint for each histogram interval

@@ -31,7 +31,11 @@ if __name__ == '__main__':
     data = [ val for val in metadata.get().items() ]
     hist = reduce(histogram_by_actors, data, {})
     hist, bins = np.histogram([ *hist.keys() ], weights=[ *hist.values() ])
-    bin_intervals = [str(int(x))+ "-" + str(int(y)) for x,y in zip(bins[:-1], bins[1:])]
+    print(bins)
+    print(hist)
+    bin_intervals = [str(int(x))+ "-" + str(int(y) - 1) for x,y in zip(bins[:-2], bins[1:-1])]
+    bin_intervals.append(str(int(bins[-2]))+ "-" + str(int(bins[-1])))
+    print(bin_intervals)
     dtype = [ ('X', object), ('Y', np.uint32) ]
     Z = np.array([ *zip(bin_intervals, hist) ], dtype=dtype)
     np.savetxt('by-actors.csv', Z, delimiter=',', fmt=['%s', '%d'], header='X,Y', comments='')

### 2021-04-03 scripts/make_by-duration.py

@@ -31,15 +31,17 @@ if __name__ == '__main__':
     print('Retrieved data')
     data = [ val for val in metadata.get().items() ]
     hist = reduce(histogram_by_duration, data, [])
-    print(hist)
     hist, bins = np.histogram(hist, bins=10, range=(65, 1500))
     """
     if float('inf') in hist:
         hist['Unknown'] = hist[float('inf')]
         del hist[float('inf')]
     """
-    bins = np.insert(bins, 0, 0, axis=0)
-    bin_intervals = [str(int(x))+ "-" + str(int(y)) for x,y in zip(bins[:-1], bins[1:])]
+    print(bins)
+    print(hist)
+    bin_intervals = [str(int(x))+ "-" + str(int(y) - 1) for x,y in zip(bins[:-2], bins[1:-1])]
+    bin_intervals.append(str(int(bins[-2]))+ "-" + str(int(bins[-1])))
+    print(bin_intervals)
     dtype = [ ('X', object), ('Y', np.uint32) ]
     Z = np.array([ *zip(bin_intervals, hist) ], dtype=dtype)
     np.savetxt('by-duration.csv', Z, delimiter=',', fmt=['%s', '%d'], header='X,Y', comments='')

### 2021-04-10 paper.tex
rewrite methodology section to align with chen's comments

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{METHODOLOGY}
+\section{AUTODASH 2021}
+We aim to provide a dataset that contains a diverse set of egocentric vehicle collision videos with different locations and collision scenarios.
+In order to source these videos, we built a data pipeline that collects user-submitted videos from YouTube and Imgur.
+Using our pipeline, we collected and labelled 250 video clips of collision and near-collision scenarios from various locations in Europe, Asia, and North America.
+We have a variety of scene types such as city streets, highways, and rural areas from these locations.
+All video clips are annotated with bounding boxes for the vehicles and pedestrians present, as well as frame indices and object IDs for the participants in the collision.
 
-Our pipeline is built from several modular components called executors that each process or handle the data corresponding to a single video before piping the resulting data to the next executor.
-Figure \ref{fig:pr_curve} illustrates the organization of the pipeline in its default configuration.
+\subsection{Video Collection Pipeline}
+In order to facilitate collection of videos, we built a video discovery and annotation pipeline that can be customized for many labelling tasks.
+Our pipeline is built from several modular components called executors that each process or handle the data corresponding to a single video before piping the resulting data to the next executor using a pipe and filter architecture.
+The pipeline fetches and stores video metadata as JSON in a NoSQL cloud database and enables concurrent labelling of videos.
+
+We collect a wide range of metadata on each video such as the set of bounding boxes for actors in the video, the object type of all the actors, the start frame of any collision in the video, and the location of the video.
+
+The most basic pipeline configuration starts off with a set of web scrapers that each target and scrape a specific website or video repository based on a user-defined set of key-terms, and a \textit{database source executor} that pulls unlabelled videos from the  database.
+Videos that are pulled by the scrapers are immediately added to the database in order to ensure only one person is labeling a video at a time.
+
+After a video has been downloaded to the user's machine, it is passed to the \textit{Splitter Executor}, which is used to split an input video into multiple sub-videos.
+We use the splitter for long-form videos that may contain multiple independent collision events or irrelevant video segments, such as compilation videos or videos with substantial editing and transitions.
+The \textit{Splitter} outputs a different metadata item for each distinct sub-video extracted from its input video.
+
+After collection and preprocessing, a core component of our pipeline is a GUI tool (Figure \ref{fig:example_gui_tool-png}) that facilitates the manual annotation of the dashcam videos, and quick manual filtering of non-dashcam and irrelevant videos.
+We provide tools to annotate the video bounding boxes to localize, identify and track agents in the video segment, as well as ways to label the type of each agent and the location of the video.
+In order to assist with the manual labelling of bounding boxes, we provide ways to linearly interpolate between two user-drawn bounding boxes, so the user does not need to label every frame.
 
@@
   \centering
-    \tikzset{
-    	node distance = 6mm and 0cm,
-        module/.style={%
-            draw, rounded corners,
-            minimum width=#1,
-            minimum height=7mm,
-            font=\sffamily
-            },
-        module/.default=1cm,
-        >=LaTeX
-    }
-    \begin{tikzpicture}[
-      % This will show the frame around the figure
-      show background rectangle]
-
-      % Place first 6 items
-      \node[module] (crawler) {Web-Scrapers};
-      \node[module, below=of crawler] (downloader) {Downloaders};
-      \node[module, below=of downloader] (splitter) {Video-Splitter};
-      \node[module, below=of splitter] (labeller) {Video-Labelling Tool};
-      \node[module, below=of labeller] (uploader) {Data-Uploader};
-      \draw[->] (crawler) -- (downloader);
-      \draw[->] (downloader) -- (splitter);
-      \draw[->] (splitter) -- (labeller);
-      \draw[->] (labeller) -- (uploader);
-
-    \end{tikzpicture}
-		\caption{Architecture of the pipeline in its default configuration. Each node in the diagram represents a stage of the pipeline, consisting of a single executor or series of executors.}
-		\label{fig:pipeline-architecture}
+  \includegraphics[width=0.46\textwidth]{example_gui_tool.png}
+  \caption{GUI tool to facilitate annotation}
+  \label{fig:example_gui_tool-png}
 \end{figure}
 
-\subsection{Video Collection}
+\subsection{Object Detection}
+Every video in the dataset contians bounding boxes for all of the actors present in the video.
+Each actor is given a numerical ID, a list of bounding boxes that contain that actor for every frame they are present, as well as a classificaiton of the actor.
+There are 9 different classifications with the majority of objects being classified as one of "car", "truck", "van", or "motorcycle"
 
-The entry into our pipeline is a set of web scraper executors that each target and scrape a specific website or video repository based on a user-defined set of key-terms, and a \textit{database source executor} that pulls unlabelled videos from the user's database.
-Videos that are pulled by the scrapers are immediately added to the database with relevant metadata and marked as unlabelled.
-Subsequently, they are loaded into memory and sequentially fed into the pipeline.
-If the pipeline terminates before labelling a video, it remains flagged as unlabelled in the database and the video will be pulled in a subsequent run by the \textit{database source executor}.
-Crawler state is maintained via database lookup of specified key-value pairs to ensure duplicate data is not pulled.
-No video preprocessing such as resizing, trimming or cropping is automatically performed.
+\subsection{Collision Detection}
+Assisting in collision detection algorithms is the main purpose of this dataset, and as such we collect multiple pieces of data about the collision.
+We label and define a \textit{collision location} as the index of the first frame in the video for which at least one actor makes unintentional contact with another actor or stationary object.
+A given video may have multiple collision locations, especially in the case of highway scenes, and therefore each metadata contains a list of frame numbers for such events.
 
-Users may define their own search terms to be used when querying the video repository.
+In addition to \textit{collision location} we classify every actor $a_i$ in the video with a \textit{has\_collision} flag that specifies if $a_i$ takes part in a collision at any point in the video.
+
+% REMOVED IN REVISION
+% Figure \ref{fig:pr_curve} illustrates the organization of the pipeline in its default configuration.
+
+% \begin{figure}[htbp]
+%     \centering
+%     \tikzset{
+%         node distance = 6mm and 0cm,
+%         module/.style={%
+%             draw, rounded corners,
+%             minimum width=#1,
+%             minimum height=7mm,
+%             font=\sffamily
+%             },
+%         module/.default=1cm,
+%         >=LaTeX
+%     }
+%     \begin{tikzpicture}[
+%       % This will show the frame around the figure
+%       show background rectangle]
+
+%       % Place first 6 items
+%       \node[module] (crawler) {Web-Scrapers};
+%       \node[module, below=of crawler] (downloader) {Downloaders};
+%       \node[module, below=of downloader] (splitter) {Video-Splitter};
+%       \node[module, below=of splitter] (labeller) {Video-Labelling Tool};
+%       \node[module, below=of labeller] (uploader) {Data-Uploader};
+%       \draw[->] (crawler) -- (downloader);
+%       \draw[->] (downloader) -- (splitter);
+%       \draw[->] (splitter) -- (labeller);
+%       \draw[->] (labeller) -- (uploader);
+
+%     \end{tikzpicture}
+%         \caption{Architecture of the pipeline in its default configuration. Each node in the diagram represents a stage of the pipeline, consisting of a single executor or series of executors.}
+%         \label{fig:pipeline-architecture}
+% \end{figure}
+
+% Users may define their own search terms to be used when querying the video repository.
 This value can be set in a YAML pipeline configuration file.
@@
 
-In addition to collection and preprocessing, a core component of our pipeline is a GUI tool that facilitates the manual annotation of the dashcam videos, and quick manual filtering of non-dashcam and irrelevant videos.
+% In addition to collection and preprocessing, a core component of our pipeline is a GUI tool that facilitates the manual annotation of the dashcam videos, and quick manual filtering of non-dashcam and irrelevant videos.
 Following Chan et al.\cite{chan2016anticipating}, if a collision occurs, we provide tools to annotate the frame where the collision occurs and bounding boxes to localize, identify and track agents in the video segment.
@@
 We also save the video resolution at which the video was annotated to ensure bounding box annotations can always be scaled to fit variable download resolutions.
-For long-form videos that may contain multiple collision events or irrelevant video segments, such as compilation videos or videos with substantial editing and transitions, we provide a video clipping feature to demarcate the collision events from which we extract and generate distinct data points.
-Each video segment will eventually become a metadata item. Figure \ref{fig:example_gui_tool-png} shows an example of the GUI tool in usage.
+% Each video segment will eventually become a metadata item. Figure \ref{fig:example_gui_tool-png} shows an example of the GUI tool in usage.
 
-\subsection{Metadata}
-After all of the previous steps have been completed, the pipeline is able to produce a complete metadata object.
-There are many fields in the metadata object (as can be seen in Figure \ref{metadata_example}):
+% \subsection{Metadata}
+% After all of the previous steps have been completed, the pipeline is able to produce a complete metadata object.
+% There are many fields in the metadata object (as can be seen in Figure \ref{metadata_example}):
 
-\begin{itemize}
-  %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
-  \item "\texttt{description}": Description of the video as scraped from the video hosting website
-  \item "\texttt{state}": String that describes the current labelling state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
-  \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
-  \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site- specific
-  \item "\texttt{title}": The title of the video from the video hosting website
-  \item "\texttt{url}": URL that the video was fetched from
-  \item "\texttt{is\_split\_url}": Boolean that is true if the video has been segmented into multiple \texttt{MetaDataItem} objects during labelling, false otherwise
-  \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
-  \item "\texttt{start\_i}": The start frame of the video segment that the bounding boxes are created for (if \texttt{is\_split\_url} is true)
-  \item "\texttt{end\_i}": The end frame of the video segment that the bounding boxes are created for (if \texttt{is\_split\_url} is true)
-  \item "\texttt{bb\_fields}": All bounding-box specific data
-  \begin{itemize}
-    \item "\texttt{collision\_locations}": List of frame numbers indicating the collision start frames
-    \item "\texttt{resolution}": List with 2 elements (width, height) representing the resolution in pixels of the video the bounding boxes were created for
-    \item "\texttt{objects}": List of all of the relevant metadata pertaining to each agent in the video (either participant or bystander). Each item in this list includes the following:
-    \begin{itemize}
-      \item "\texttt{id}": Unique numerical identifier that represents this object
-      \item "\texttt{bboxes}": List of bounding boxes for this specific object.
+% \begin{itemize}
+%   %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
+%   \item "\texttt{description}": Description of the video as scraped from the video hosting website
+%   \item "\texttt{state}": String that describes the current labelling state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
+%   \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
+%   \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site- specific
+%   \item "\texttt{title}": The title of the video from the video hosting website
+%   \item "\texttt{url}": URL that the video was fetched from
+%   \item "\texttt{is\_split\_url}": Boolean that is true if the video has been segmented into multiple \texttt{MetaDataItem} objects during labelling, false otherwise
+%   \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
+%   \item "\texttt{start\_i}": The start frame of the video segment that the bounding boxes are created for (if \texttt{is\_split\_url} is true)
+%   \item "\texttt{end\_i}": The end frame of the video segment that the bounding boxes are created for (if \texttt{is\_split\_url} is true)
+%   \item "\texttt{bb\_fields}": All bounding-box specific data
+%   \begin{itemize}
+%     \item "\texttt{collision\_locations}": List of frame numbers indicating the collision start frames
+%     \item "\texttt{resolution}": List with 2 elements (width, height) representing the resolution in pixels of the video the bounding boxes were created for
+%     \item "\texttt{objects}": List of all of the relevant metadata pertaining to each agent in the video (either participant or bystander). Each item in this list includes the following:
+%     \begin{itemize}
+%       \item "\texttt{id}": Unique numerical identifier that represents this object
+%       \item "\texttt{bboxes}": List of bounding boxes for this specific object.
 Each bounding box is represented as a $1\times5$ array with elements in the following order: frame number, x1, y1, x2, y2
-      \item "\texttt{class}": The class of the object (eg. "car", "pedestrian")
-      \item "\texttt{has\_collision}": Boolean that is true if the object is in a collision, false otherwise
-    \end{itemize}
-  \end{itemize}
-\end{itemize}
+%       \item "\texttt{class}": The class of the object (eg. "car", "pedestrian")
+%       \item "\texttt{has\_collision}": Boolean that is true if the object is in a collision, false otherwise
+%     \end{itemize}
+%   \end{itemize}
+% \end{itemize}
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.46\textwidth]{example_gui_tool.png}
-	\caption{GUI tool to facilitate annotation}
-	\label{fig:example_gui_tool-png}
-\end{figure}
-
-\begin{figure}[htbp]
-  \begin{lstlisting}[language=json,xleftmargin=5mm]
-{
-  "description":"",
-  "download_src":"YouTube",
-  "tags": {
-    "reddit_post_info":{
-      "id":"<post_id>"
-      "title":"title"
-    }
-  },
-  "title":"Title of the Video",
-  "url":"http://www.myvideo.com",
-  "is_split_url": false,
-  "enum_tags": ["NoCollision"],
-  "start_i": 0,
-  "end_i": 60,
-  "bb_fields": {
-    "collision_locations": [],
-    "objects": [
-      {
-        "bboxes": [
-          [0, 1096, 377, 1279, 634]
-        ],
-        "class": "car",
-        "has_collision": false,
-        "id": "1"
-      }
-    ],
-    "resolution": [1280, 720]
-  }
-}
-  \end{lstlisting}
-    \caption{Example metadata produced by the pipeline}
-    \label{metadata_example}
-\end{figure}
+% \begin{figure}[htbp]
+%   \begin{lstlisting}[language=json,xleftmargin=5mm]
+% {
+%   "description":"",
+%   "download_src":"YouTube",
+%   "tags": {
+%     "reddit_post_info":{
+%       "id":"<post_id>"
+%       "title":"title"
+%     }
+%   },
+%   "title":"Title of the Video",
+%   "url":"http://www.myvideo.com",
+%   "is_split_url": false,
+%   "enum_tags": ["NoCollision"],
+%   "start_i": 0,
+%   "end_i": 60,
+%   "bb_fields": {
+%     "collision_locations": [],
+%     "objects": [
+%       {
+%         "bboxes": [
+%           [0, 1096, 377, 1279, 634]
+%         ],
+%         "class": "car",
+%         "has_collision": false,
+%         "id": "1"
+%       }
+%     ],
+%     "resolution": [1280, 720]
+%   }
+% }
+%   \end{lstlisting}
+%     \caption{Example metadata produced by the pipeline}
+%     \label{metadata_example}
+% \end{figure}
 

### 2021-04-16 scripts/count_bbs.py
Fixing Duplication bug in count_bbs.py

@@ -9,27 +9,23 @@ FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
 
 def count_bbs(count, data):
     (key, data) = data
+    count['all_urls'].add(data.get('url'))
     if data.get('is_cancelled', True):
         return count
+    if (data.get('url'), data.get('start_i')) in count.get('seen', set()):
+        count['duplicated'].add((data.get('url'), data.get('start_i')))
     if 'bb_fields' in data and len(data['bb_fields']) > 0:
-        count.update({ 'total': count.get('total', 0) + 1 })
+        if (data.get('url'), data.get('start_i')) not in count.get('seen', set()):
+            count.update({ 'total': count.get('total', 0) + 1 })
         if 'collision_locations' in data['bb_fields'] and len(data['bb_fields']['collision_locations']) > 0:
             count.update({ 'collision': count.get('collision', 0) + 1 })
-            if (data.get('url'), data.get('start_i')) in count.get('seen', set()):
-                count['duplicated'].add((data.get('url'), data.get('start_i')))
-            count['seen'].add((data['url'], data.get('start_i')))
         if 'accident_locations' in data['bb_fields'] and len(data['bb_fields']['accident_locations']) > 0:
             count.update({ 'nested_accident': count.get('nested_accident', 0) + 1 })
-            if (data.get('url'), data.get('start_i')) in count.get('seen', set()):
-                count['duplicated'].add((data.get('url'), data.get('start_i')))
-            count['seen'].add((data.get('url'), data.get('start_i')))
     if 'accident_locations' in data and len(data['accident_locations']) > 0:
         count.update({ 'accident': count.get('accident', 0) + 1 })
-        if (data.get('url'), data.get('start_i')) in count.get('seen', set()):
-            count['duplicated'].add((data.get('url'), data.get('start_i')))
-        count['seen'].add((data['url'], data.get('start_i')))
     if not data.get('url'):
         count.update({ 'no_url': count.get('no_url', set()) + data.id })
+    count['seen'].add((data['url'], data.get('start_i')))
     return count
 
 if __name__ == '__main__':
@@ -45,7 +41,12 @@ if __name__ == '__main__':
     metadata = db.reference('metadata')
     print('Retrieved data')
     data = [ val for val in metadata.get().items() ]
-    count = reduce(count_bbs, data, { 'seen':set(), 'duplicated': set() })
[…]

### 2021-04-16 paper.tex
remove commented out sections because we can always revert with git
fixed histograms to not count duplicate videos

@@
 
-% REMOVED IN REVISION
-% Figure \ref{fig:pr_curve} illustrates the organization of the pipeline in its default configuration.
-
-% \begin{figure}[htbp]
-%     \centering
-%     \tikzset{
-%         node distance = 6mm and 0cm,
-%         module/.style={%
-%             draw, rounded corners,
-%             minimum width=#1,
-%             minimum height=7mm,
-%             font=\sffamily
-%             },
-%         module/.default=1cm,
-%         >=LaTeX
-%     }
-%     \begin{tikzpicture}[
-%       % This will show the frame around the figure
-%       show background rectangle]
-
-%       % Place first 6 items
-%       \node[module] (crawler) {Web-Scrapers};
-%       \node[module, below=of crawler] (downloader) {Downloaders};
-%       \node[module, below=of downloader] (splitter) {Video-Splitter};
-%       \node[module, below=of splitter] (labeller) {Video-Labelling Tool};
-%       \node[module, below=of labeller] (uploader) {Data-Uploader};
-%       \draw[->] (crawler) -- (downloader);
-%       \draw[->] (downloader) -- (splitter);
-%       \draw[->] (splitter) -- (labeller);
-%       \draw[->] (labeller) -- (uploader);
-
-%     \end{tikzpicture}
-%         \caption{Architecture of the pipeline in its default configuration. Each node in the diagram represents a stage of the pipeline, consisting of a single executor or series of executors.}
-%         \label{fig:pipeline-architecture}
-% \end{figure}
-
-% Users may define their own search terms to be used when querying the video repository.
-This value can be set in a YAML pipeline configuration file.
-By default, our scrapers query using the keywords: \texttt{Car crash dashcam}.
-Currently we support crawling Reddit and YouTube to locate videos that are of interest, and downloading videos hosted on YouTube and Imgur.
-Users that want to pull from a video repository that is not currently implemented should create a custom executor and implement the \texttt{iCrawler} interface.
-This new executor should be added as an entry point in a new YAML configuration and should generate and return a \texttt{MetaDataItem} with video source information to be used by a subsequent and corresponding downloader.
-\texttt{MetaDataItem} objects are fed into the \texttt{UniversalDownloader} which aggregates \texttt{iDownloader} implementations.
-The \texttt{UniversalDownloader} then distributes \texttt{MetaDataItem} objects to their corresponding downloader by matching source URLs through regular expressions.
-New downloaders should be registered with the \texttt{UniversalDownloader} via a YAML pipeline configuration along with a regular expression string for URL matching.
-
-%HAS BEEN REMOVED BECAUSE NOT FUNCTIONAL
-%\subsection{Video Preprocessing}
-%\subsection{Automatic Annotation}
-%\subsection{Object Detection \& Tracking}
-%\todo{Automated object detection not used right now?}
 \subsection{Anonymization}
@@
 The accuracy, amount and type of blurring applied can be tweaked using the exposed API.
-
-\subsection{Annotation}
-
-% In addition to collection and preprocessing, a core component of our pipeline is a GUI tool that facilitates the manual annotation of the dashcam videos, and quick manual filtering of non-dashcam and irrelevant videos.
-Following Chan et al.\cite{chan2016anticipating}, if a collision occurs, we provide tools to annotate the frame where the collision occurs and bounding boxes to localize, identify and track agents in the video segment.
-Object tracking bounding boxes can be linearly interpolated from manual start and end points to improve ease of labelling.
-We also save the video resolution at which the video was annotated to ensure bounding box annotations can always be scaled to fit variable download resolutions.
-% Each video segment will eventually become a metadata item. Figure \ref{fig:example_gui_tool-png} shows an example of the GUI tool in usage.
-
-% \subsection{Metadata}
-% After all of the previous steps have been completed, the pipeline is able to produce a complete metadata object.
-% There are many fields in the metadata object (as can be seen in Figure \ref{metadata_example}):
-
-% \begin{itemize}
-%   %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
-%   \item "\texttt{description}": Description of the video as scraped from the video hosting website
-%   \item "\texttt{state}": String that describes the current labelling state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
-%   \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
-%   \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site- specific
-%   \item "\texttt{title}": The title of the video from the video hosting website
-%   \item "\texttt{url}": URL that the video was fetched from
-%   \item "\texttt{is\_split\_url}": Boolean that is true if the video has been segmented into multiple \texttt{MetaDataItem} objects during labelling, false otherwise
-%   \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
-%   \item "\texttt{start\_i}": The start frame of the video segment that the bounding boxes are created for (if \texttt{is\_split\_url} is true)
-%   \item "\texttt{end\_i}": The end frame of the video segment that the bounding boxes are created for (if \texttt{is\_split\_url} is true)
-%   \item "\texttt{bb\_fields}": All bounding-box specific data
-%   \begin{itemize}
-%     \item "\texttt{collision\_locations}": List of frame numbers indicating the collision start frames
-%     \item "\texttt{resolution}": List with 2 elements (width, height) representing the resolution in pixels of the video the bounding boxes were created for
-%     \item "\texttt{objects}": List of all of the relevant metadata pertaining to each agent in the video (either participant or bystander). Each item in this list includes the following:
-%     \begin{itemize}
-%       \item "\texttt{id}": Unique numerical identifier that represents this object
-%       \item "\texttt{bboxes}": List of bounding boxes for this specific object.
-Each bounding box is represented as a $1\times5$ array with elements in the following order: frame number, x1, y1, x2, y2
-%       \item "\texttt{class}": The class of the object (eg. "car", "pedestrian")
-%       \item "\texttt{has\_collision}": Boolean that is true if the object is in a collision, false otherwise
-%     \end{itemize}
-%   \end{itemize}
-% \end{itemize}
-
-% \begin{figure}[htbp]
-%   \begin{lstlisting}[language=json,xleftmargin=5mm]
-% {
-%   "description":"",
-%   "download_src":"YouTube",
-%   "tags": {
-%     "reddit_post_info":{
-%       "id":"<post_id>"
-%       "title":"title"
-%     }
-%   },
-%   "title":"Title of the Video",
-%   "url":"http://www.myvideo.com",
-%   "is_split_url": false,
-%   "enum_tags": ["NoCollision"],
-%   "start_i": 0,
-%   "end_i": 60,
-%   "bb_fields": {
-%     "collision_locations": [],
-%     "objects": [
-%       {
-%         "bboxes": [
-%           [0, 1096, 377, 1279, 634]
-%         ],
-%         "class": "car",
-%         "has_collision": false,
-%         "id": "1"
-%       }
-%     ],
-%     "resolution": [1280, 720]
-%   }
-% }
-%   \end{lstlisting}
-%     \caption{Example metadata produced by the pipeline}
-%     \label{metadata_example}
-% \end{figure}
 
@@
     ylabel={Frequency (\# of objects)},
-    ymin=-50,
-    ymax=1800,
+    ymin=-25,
+    ymax=800,
     xtick=data,
@@
     ymin=-5,
-    ymax=175,
+    ymax=130,
     xtick=data,
@@
     ylabel={Frequency (\# of videos)},
-    ymin=-10,
-    ymax=270,
+    ymin=-5,
+    ymax=112,
     xtick=data,
@@
     xtick=data,
-    ymin=-5,
-    ymax=130,
+    ymin=-2,
+    ymax=70,
     xticklabels from table={\byduration}{X},

### 2021-04-16 scripts/make_by-actors.py

@@ -2,16 +2,15 @@ import numpy as np
 import firebase_admin as fb
 from firebase_admin import credentials, db
 from firebase_admin.db import Reference
-from functools import reduce
+from functools import reduce, partial
 
 FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
 
-def histogram_by_actors(hist, data):
+def histogram_by_actors(hist, data, seen):
     (key, data) = data
-    if data.get('is_cancelled', True):
+    if data.get('is_cancelled', True) or 'bb_fields' not in data or (data.get('url'), data.get('start_i')) in seen:
         return hist
-    if 'bb_fields' not in data:
-       return hist
+    seen.add((data.get('url'), data.get('start_i')))
     num_actors = len(set([ obj.get('id') for obj in data['bb_fields'].get('objects', []) ]))
     hist[num_actors] = hist.get(num_actors, 0) + 1
     return hist
@@ -29,7 +28,7 @@ if __name__ == '__main__':
     metadata = db.reference('metadata')
     print('Retrieved data')
     data = [ val for val in metadata.get().items() ]
-    hist = reduce(histogram_by_actors, data, {})
+    hist = reduce(partial(histogram_by_actors, seen = set()), data, {})
     hist, bins = np.histogram([ *hist.keys() ], weights=[ *hist.values() ])
     print(bins)
     print(hist)

### 2021-04-16 scripts/make_by-agents.py

@@ -2,16 +2,15 @@ import numpy as np
 import firebase_admin as fb
 from firebase_admin import credentials, db
 from firebase_admin.db import Reference
-from functools import reduce
+from functools import reduce, partial
 
 FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
 
-def histogram_by_agents(hist, data):
+def histogram_by_agents(hist, data, seen):
     (key, data) = data
-    if data.get('is_cancelled', True):
+    if data.get('is_cancelled', True) or 'bb_fields' not in data or (data.get('url'), data.get('start_i')) in seen:
         return hist
-    if 'bb_fields' not in data:
-       return hist
+    seen.add((data.get('url'), data.get('start_i')))
     num_agents = 0
     viewed_ids = set()
     for obj in data['bb_fields'].get('objects', []):
@@ -36,7 +35,7 @@ if __name__ == '__main__':
     metadata = db.reference('metadata')
     print('Retrieved data')
     data = [ val for val in metadata.get().items() ]
-    hist = reduce(histogram_by_agents, data, {})
+    hist = reduce(partial(histogram_by_agents, seen = set()), data, {})
     print(hist)
     dtype = [ ('X', object), ('Y', np.uint32) ]
     Z = np.array([ *hist.items() ], dtype=dtype)

### 2021-04-16 scripts/make_by-classes.py

@@ -2,19 +2,18 @@ import numpy as np
 import firebase_admin as fb
 from firebase_admin import credentials, db
 from firebase_admin.db import Reference
-from functools import reduce
+from functools import reduce, partial
 
 FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
 RELEVANT_CLASSES = ['car', 'bus', 'truck', 'van', 'motorcycle', 'train', 'streetcar', 'pedestrian', 'bicycle', 'animal']
 NOOP_CLASSES = ['NONE', 'test']
 OTHER_CLASS = 'other'
 
-def histogram_by_class(hist, data):
+def histogram_by_class(hist, data, seen):
     (key, data) = data
-    if data.get('is_cancelled', True):
+    if data.get('is_cancelled', True) or 'bb_fields' not in data or (data.get('url'), data.get('start_i')) in seen:
         return hist
-    if 'bb_fields' not in data:
-        return hist
+    seen.add((data.get('url'), data.get('start_i')))
     viewed_ids = set()
     for obj in data['bb_fields'].get('objects', []):
         if obj['id'] not in viewed_ids:
@@ -39,7 +38,7 @@ if __name__ == '__main__':
     metadata = db.reference('metadata')
     print('Retrieved data')
     data = [ val for val in metadata.get().items() ]
-    hist = reduce(histogram_by_class, data, {})
+    hist = reduce(partial(histogram_by_class, seen = set()), data, {})
     del hist['NONE']
     del hist['test']
     other = hist[OTHER_CLASS]

### 2021-04-16 scripts/make_by-duration.py

@@ -2,18 +2,17 @@ import numpy as np
 import firebase_admin as fb
 from firebase_admin import credentials, db
 from firebase_admin.db import Reference
-from functools import reduce
+from functools import reduce, partial
 
 FIREBASE_CRED_FILENAME = "autodash-9dccb-add3cdae62ea.json"
 
-def histogram_by_duration(hist, data):
+def histogram_by_duration(hist, data, seen):
     (key, data) = data
-    if data.get('is_cancelled', True):
-        return hist
-    if 'bb_fields' not in data:
-        return hist
     if 'end_i' not in data or 'start_i' not in data:
         return hist
+    if data.get('is_cancelled', True) or 'bb_fields' not in data or (data.get('url'), data.get('start_i')) in seen:
+        return hist
+    seen.add((data.get('url'), data.get('start_i')))
     hist.append(data.get('end_i', float('inf')) - data.get('start_i', float('-inf')))
     return hist
 
@@ -30,7 +29,7 @@ if __name__ == '__main__':
     metadata = db.reference('metadata')
     print('Retrieved data')
     data = [ val for val in metadata.get().items() ]
-    hist = reduce(histogram_by_duration, data, [])
+    hist = reduce(partial(histogram_by_duration, seen = set()), data, [])
     hist, bins = np.histogram(hist, bins=10, range=(65, 1500))
     """
     if float('inf') in hist:
